### 2018-03-04 assets/src/week3/paper/main.tex

\documentclass{acmart}
\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{sidebyside}
\usepackage{cleveref}
\usepackage{placeins}
\usepackage{colortbl}

\title{An inquiry into the influence of parallelism and the choice of random
engines on the runtime and results of Stride}

\author{Niels Aerens}
\author{Thomas Avé}
\author{Tobia De Koninck}
\author{Robin Jadoul}

% \date{March 2018}

\begin{abstract}
    In this article, we investigate a few properties of the Stride project. In particular, we look at the influence of the amount of parallelization with respect to the running time of a simulation and the difference in simulation outcomes when varying the used random number generator.
\end{abstract}

\begin{document}

\maketitle

\section{Introduction}
Stride \cite{KUYLEN20172438} is an individual-based Simulator for the Transmission of Infectious Diseases with focus on model flexibility and
performance. The performance of such a simulator is important for the researcher to have fast feedback in order to
build a reasonable model of the disease. The Stride program currently has scenario tests to prevent regressions in the
simulation output. To provide fast feedback to the developers working on Stride the test should run sufficiently quickly.
The running time of the tests are a good indication of the running time of the simulator itself. Hence we perform a
performance analysis of the running time of tests and the influence of parallelism.

The scenario tests are using the Attack Rate as parameter to assert the simulator outcome. Since Stride is a stochastic
system and thus relies on randomness, the output of its tests are variable. Therefore the tests use an acceptability range
for the test outcome. We determined these ranges by running the tested simulations multiple times (100+). We noticed
using a QQ-Plot and hypothesis tests that the Attack Rate can be considered to follow a normal distribution.
For the accepted ranges, we decided to allow a distance of 2 standard deviations from the observed mean.

The second topic of this paper is to analyze the influence of the random number generator engine on the Attack Rate.
Stride uses the Trng library \cite{bauke2015tina} as random number generator. The inspected engines are \texttt{lgc64}, \texttt{lgc64\_shift}, \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2} and \texttt{yarn3}.

\pagebreak

\section{Methods}

\subsection{Influence of multi-threading}

The analysis described in this section was performed on a 32 core AMD machine. Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at time of writing. By using a Bash-script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/597e9d14356a40f10c52dbd789ce495f0891720e/assets/src/week3/bench.sh}} % TODO update links to website
the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.

\subsection{Influence of random engine}

Using a Python3 script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/b8b67f7083ba8a523bdb16f0c6fd0fdfeea7dacf/assets/src/week3/random_engines.py}} % TODO update links to website
the simulation was run using the different random engines, at the same time the running time
was measured.

\section{Results}

\subsection{Influence of multi-threading}
The running time in function of the number of threads are shown in \cref{fig:threads}. The difference between the first and third
quartile is only 0.45 seconds. This difference is negligible compared to the 27 seconds running time. We can conclude
that the parallelisation of the code doesn’t have a great influence on the performance.
Note that for each number of threads, the values are obtained by running the Influenza A simulation 15 times and taking the average running time.

\sidebyside[!hbt][fig:threads:scatter][fig:threads:boxplot]
    {Connected scatter plot}
    {images/performance_scatter.png}
    {Boxplot}
    {images/boxplot_performance.png}
    {Running time in function of number of threads}
    {fig:threads}
\subsection{Influence of random engine}
The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine needs the most time. The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 6 seconds. Thus there isn’t a big difference. A complete comparison of running times can be found in \cref{fig:engine:running}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{images/engine_performance_bar.png}
    \caption{Running time of the different rng engines for the influenza A test case.}
    \label{fig:engine:running}
\end{figure}

The first test case of Stride (Influenza A\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L82}})
performs a simulation of influenza in Flanders, with an $R_0$ value\footnote{Basic reproduction number, a measure for the infectiousness of a disease: the amount of people will 1 infected person infect directly in a completely
susceptible population.} of 3.0. For this test case the range of allowed attack rates doesn't change much. 
% TODO insert text about hypothesis tests
The second test case (Influenza B\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L86}}) uses a seeding rate of 0, which results in a constant attack rate of 0. As expected the RNG engine doesn't have influence on this outcome.
The same holds for the third test case (Influenza C\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L91}}) which uses very low seeding rate and a large immunity factor. The attack vector for every engine is 5.
The Measles 16\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L97}} testcase is more interesting for the analysis of the RNG engines. The disease simulated is not influeanza but the measles. The $R_0$ value is set to 16, which results in a very large part of the population becoming infected.

% TODO insert text about hypothesis tests
The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the whole population, so the attack rate is for all the engines the same.

\subsection{Normality of the output}
\label{par:normality}
To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilkes test.

% Influenza A
Looking at the Influenza A testcase, we find the resulting P-values for Shapiro-Wilkes test in \cref{tab:influenza_a:shapiro}. Here, all random engines result in an (at least approximately) normal distribution for the attack rate.
\begin{table}[!hbt]
    \begin{tabular}{c c c c c c}
       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
        0.2530 & 0.8561 & 0.2717 & 0.3722 & 0.4837 & 0.6319
    \end{tabular}
    \caption{P-values of the Influenza A test case for the Shapiro-Wilkes normality test}
    \label{tab:influenza_a:shapiro}
\end{table}

% Measles 16
For the Measles 16 testcase, resulting P-values for the Shapiro-Wilkes test can be found in \cref{tab:measles_16:shapiro}.
We can observe that only the \texttt{lgc64} engine fails the test at $p = 0.05$. % TODO: reference plots

\begin{table}[!hbt]
    \begin{tabular}{c c c c c c}
       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
        $1.039\times10^{-7}$ & 0.5460 & 0.1423 & 0.7592 & 0.2702 & 0.1516
    \end{tabular}
    \caption{P-values of the Measles 16 test case for the Shapiro-Wilkes normality test}
    \label{tab:measles_16:shapiro}
\end{table}

\subsection{Equality of acceptable ranges for the test cases}

In this section the equality of the different value ranges which are accepted by the tests for each random engine is verified. Only the Influenza A and Measles 16 test cases are studied since they provide have a variable range. The tests are done using t-test for the standard deviations and z-test for the means, since it's known that the data is normally distributed.

The hypotheses for the t-test:
\[
\begin{aligned}
 H_0 &: \sigma = \sigma_2\\
 H_1 &: \sigma \ne \sigma_2\
\end{aligned}
\]

and for the z-test:
\[
\begin{aligned}
 H_0 &: \mu_1 = \mu_2  \\
 H_1 &: \mu_1 \ne \mu_2.
\end{aligned}
\]

The p-values for these tests are listed in \cref{tab:measles_16:p_values} and clearly indicates that the \(H_0\) holds for both tests. % TOD update

\begin{table}[!hbt]
    \centering
    \bgroup
    \def\arraystretch{2}
    \begin{tabular}{c|c|c|c|c|c}
                                & \textbf{Influenza A}  & \textbf{Measles 16} \\ \hline
        \texttt{lgc64}          & \([1855,2279]\)       & \([588591,591128]\) \\
        \texttt{lgc64\_shift}   & \([1954,2226]\)       & \([588899,591513]\) \\
        \texttt{mrg2}           & \([1859,2415]\)       & \([589230,591369]\) \\
        \texttt{mrg3}           & \([1985,2329]\)       & \([589401,591198]\) \\
        \texttt{yarn2}          & \([1876,2331]\)       & \([588739,591488]\) \\
        \texttt{yarn3}          & \([1955,2300]\)       & \([589066,590965]\) \\
    \end{tabular}
    \egroup
    \caption{The acceptable attack rates for the Influenza A en Measles 16 test case for every random number engine}
    \label{tab:ranges_engines}
\end{table}

\begin{table}[!hbt]
    \begin{tabular}{c|c|c|c|c|c|c}
        & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
        \textbf{mrg2}      
            & \(p_{\mu} = 0.2337 \quad p_{\sigma} = 0.2217 \) 
            & \cellcolor{gray}
            & \cellcolor{gray}
            & \cellcolor{gray} \\
        \textbf{mrg3}          
            & \(p_{\mu} = 0.01715 \quad p_{\sigma} = 0.0234 \)
            & \(p_{\mu} = 0.6365 \quad p_{\sigma} = 0.703 \) 
            & \cellcolor{gray} 
            & \cellcolor{gray} \\
        \textbf{yarn2}        
            & \(p_{\mu} = 0.6767 \quad p_{\sigma} = 0.6782 \)  
            & \(p_{\mu} = 0.4729 \quad p_{\sigma} = 0.4849 \)  
            & \(p_{\mu} = 0.1485 \quad p_{\sigma} = 0.1613  \)  
            & \cellcolor{gray} \\
        \textbf{yarn3}          
            & \(p_{\mu} = 0.1798 \quad p_{\sigma} = 0.3083 \)  
            & \(p_{\mu} = 0.8226 \quad p_{\sigma} = 0.5178  \) 
            & \(p_{\mu} = 0.3502 \quad p_{\sigma} = 0.4936  \)
            & \(p_{\mu} = 0.5187 \quad p_{\sigma} = 0.5178  \) \\
    \end{tabular}
    \caption{P-values of the Influenza A test case}
    \label{tab:measles_16:p_values}
\end{table}

\begin{table}[!hbt]
    \begin{tabular}{c|c|c|c|c|c|c}
        & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
        \textbf{mrg2}      
            & \(p_{\mu} = 0.6677 \quad p_{\sigma} = 0.7113 \) 
            & \cellcolor{gray}
            & \cellcolor{gray}
            & \cellcolor{gray} \\
        \textbf{mrg3}          
            & \(p_{\mu} = 0.6488 \quad p_{\sigma} = 0.6813 \)
            & \(p_{\mu} = 0.9985 \quad p_{\sigma} = 0.9983 \) 
            & \cellcolor{gray} 
            & \cellcolor{gray} \\
        \textbf{yarn2}        
            & \(p_{\mu} = 0.7061 \quad p_{\sigma} = 0.7513 \)  
            & \(p_{\mu} = 0.4081 \quad p_{\sigma} = 0.3292 \)  
            & \(p_{\mu} = 0.3812  \quad p_{\sigma} = 0.3917  \)  
            & \cellcolor{gray} \\
        \textbf{yarn3}          
            & \(p_{\mu} = 0.3615 \quad p_{\sigma} = 0.3908  \)  
            & \(p_{\mu} = 0.124 \quad p_{\sigma} = 0.1112  \) 
            & \(p_{\mu} = 0.0929 \quad p_{\sigma} = 0.1258  \)
            & \(p_{\mu} = 0.6495 \quad p_{\sigma} = 0.65  \) \\
    \end{tabular}
    \caption{P-values of the Measles 16 test case}
    \label{tab:measles_16:p_values}
\end{table}

\clearpage

\begin{figure}%
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64\_shift}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64_shift.png}}%
   		}%
   	}\\
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{mrg2}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg2.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{mrg3}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg3.png}}%
   		}%
   	}\\
   	\makebox[\textwidth][c]{%
   		\centering%
   		\subfloat[Boxplot of Influenza A run with \texttt{yarn2}]{%
   			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn2.png}}%
   		}%
   		\qquad%
   		\subfloat[Boxplot of Influenza A run with \texttt{yarn3}]{%
  			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn3.png}}%
   		}%
   	}%
   	\caption{Running time in function of number of threads}

\end{figure}

% TODO: investigate influence of threading on attack rate (hopefully minimal)

\clearpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{references.bib}

\end{document}

### 2018-03-10 assets/src/week4/random_engines_stats.py
Data processing script paper week4

@@ -1,0 +1,50 @@
+from __future__ import print_function
+import sys
+import matplotlib.pyplot as plt
+import scipy.stats
+
+data = {}
+for line in open(sys.argv[1]):
+    line = line.strip()
+    engine, mean, sigma, pts = line.split(" ", 3)
+    data[engine] = (float(mean), float(sigma), map(float, pts[1:-1].split(", ")))
+
+name_base = sys.argv[2]
+
+for engine in sorted(data):
+    filename = "{}_boxplot_{}.png".format(name_base, engine)
+    plt.figure()
+    plt.title("Boxplot")
+    plt.xlabel('Amount of people infected at the end')
+    plt.ylabel('Amount of occurences')
+    plt.boxplot(data[engine][2], 0, 'rs', 0, 0.75)
+    plt.savefig(filename)
+
+    filename = "{}_qq_{}.png".format(name_base, engine)
+    plt.figure()
+    scipy.stats.probplot(data[engine][2], dist="norm", plot=plt)
+    plt.savefig(filename)
+
+    filename = "{}_histo_{}.png".format(name_base, engine)
+    plt.figure()
+    plt.xlabel("Infected count")
+    plt.ylabel("Number of occurrences")
+    plt.hist(data[engine][2])
+    plt.savefig(filename)
+
+    p = scipy.stats.shapiro(data[engine][2])[1]
+    mean = data[engine][0]
+    sigma = data[engine][1]
+    print("Acceptable range for {}, engine {}: [{:d}, {:d}]".format(name_base, engine, int(round(mean - 2*sigma)), int(round(mean + 2*sigma))))
+    print("Normality of {}, engine {}: p = {:0.4f}".format(name_base, engine, p))
+    print()
+
+for engine in sorted(data):
+    for e2 in sorted(data):
+        if e2 <= engine: continue
+        p = scipy.stats.ttest_rel(data[engine][2], data[e2][2])[1]
+        print("Comparison of {} and {}: equal mean with p = {:0.4f}".format(engine, e2, p))
+        p = scipy.stats.levene(data[engine][2], data[e2][2])[1]
+        print("Comparison of {} and {}: equal sigma with p = {:0.4f}".format(engine, e2, p))
+        print()
+

### 2018-03-10 assets/src/week4/paper/main.tex
Updated paper for week4, should only need plots added and review

--- 2018-03-04 assets/src/week3/paper/main.tex
@@
 \usepackage{colortbl}
+\usepackage{bm}
 
@@
 The running time in function of the number of threads are shown in \cref{fig:threads}. The difference between the first and third
-quartile is only 0.45 seconds. This difference is negligible compared to the 27 seconds running time. We can conclude
-that the parallelisation of the code doesn’t have a great influence on the performance.
+quartile is only 0.45 seconds. This difference is negligible compared to the 27 seconds running time. Even the furthest outliers are less than 2 seconds apart. We can safely conclude
+that the parallelisation of the code doesn’t have a great influence on the performance. There should hopefully be some room for improvement here for the performance of Stride.
 Note that for each number of threads, the values are obtained by running the Influenza A simulation 15 times and taking the average running time.
@@
 A complete comparison of running times can be found in \cref{fig:engine:running}.
+The distribution analysis of the results with different random engines was done with 100 data points for each random engine.
+While this is still a relatively sample size, much larger sample sizes were not feasible due to the time requirements to run them all.
 
@@
 susceptible population.} of 3.0. For this test case the range of allowed attack rates doesn't change much. 
-% TODO insert text about hypothesis tests
 The second test case (Influenza B\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L86}}) uses a seeding rate of 0, which results in a constant attack rate of 0.
@@
 The $R_0$ value is set to 16, which results in a very large part of the population becoming infected.
-
-% TODO insert text about hypothesis tests
 The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the whole population, so the attack rate is for all the engines the same.
@@
 \label{par:normality}
-To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilkes test.
+To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots and histograms of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilkes test.
 
@@
        \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
-        0.2530 & 0.8561 & 0.2717 & 0.3722 & 0.4837 & 0.6319
+        0.8719 & 0.4609 & 0.9385 & 0.6556 & 0.7254 & 0.7089
     \end{tabular}
@@
 For the Measles 16 testcase, resulting P-values for the Shapiro-Wilkes test can be found in \cref{tab:measles_16:shapiro}.
-We can observe that only the \texttt{lgc64} engine fails the test at $p = 0.05$. % TODO: reference plots
 
@@
        \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
-        $1.039\times10^{-7}$ & 0.5460 & 0.1423 & 0.7592 & 0.2702 & 0.1516
+        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.0.4431
     \end{tabular}
@@
 
+We can consider the attack rate to be normally distributed in all presented cases.
+
 \subsection{Equality of acceptable ranges for the test cases}
@@
 Only the Influenza A and Measles 16 test cases are studied since they provide have a variable range.
-The tests are done using t-test for the standard deviations and z-test for the means, since it's known that the data is normally distributed.
+The tests are done using a Levene test for the standard deviations and a t-test for related samples for the means.
 
-The hypotheses for the t-test:
+The hypotheses for the Levene test:
 \[
 \begin{aligned}
- H_0 &: \sigma = \sigma_2\\
- H_1 &: \sigma \ne \sigma_2\
+ H_0 &: \sigma_1 = \sigma_2\\
+ H_1 &: \sigma_1 \ne \sigma_2\
 \end{aligned}
@@
 
-and for the z-test:
+and for the t-test:
 \[
@@
 
-The p-values for these tests are listed in \cref{tab:measles_16:p_values} and clearly indicates that the \(H_0\) holds for both tests. % TOD update
+The p-values for these tests are listed in \cref{tab:influenza:p_values} and \cref{tab:measles_16:p_values}.
+They clearly indicates that the \(H_0\) should not be rejected for both tests on a confidence level of $\alpha = 0.05$.
+Consequently, we can fairly confidently conclude that the distribution of the attack rate does not differ significantly when using a different random engine.
 
@@
                                 & \textbf{Influenza A}  & \textbf{Measles 16} \\ \hline
-        \texttt{lgc64}          & \([1855,2279]\)       & \([588591,591128]\) \\
-        \texttt{lgc64\_shift}   & \([1954,2226]\)       & \([588899,591513]\) \\
-        \texttt{mrg2}           & \([1859,2415]\)       & \([589230,591369]\) \\
-        \texttt{mrg3}           & \([1985,2329]\)       & \([589401,591198]\) \\
-        \texttt{yarn2}          & \([1876,2331]\)       & \([588739,591488]\) \\
-        \texttt{yarn3}          & \([1955,2300]\)       & \([589066,590965]\) \\
+        \texttt{lgc64}          & \([1896, 2364]\)       & \([588959, 591317]\) \\
+        \texttt{lgc64\_shift}   & \([1893, 2372]\)       & \([588992, 591360]\) \\
+        \texttt{mrg2}           & \([1899, 2334]\)       & \([588967, 591307]\) \\
+        \texttt{mrg3}           & \([1891, 2345]\)       & \([589012, 591268]\) \\
+        \texttt{yarn2}          & \([1879, 2331]\)       & \([588836, 591615]\) \\
+        \texttt{yarn3}          & \([1902, 2331]\)       & \([588751, 591443]\) \\
     \end{tabular}
@@
 \begin{table}[!hbt]
-    \begin{tabular}{c|c|c|c|c|c|c}
-        & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+    \centerline{\begin{tabular}{c|c|c|c|c|c|}
+        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
+        \textbf{lgc64\_shift}
+            & \( 0.8819 \quad 0.7593 \)
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
         \textbf{mrg2}      
-            & \(p_{\mu} = 0.2337 \quad p_{\sigma} = 0.2217 \) 
+            & \( 0.2797 \quad 0.3763 \) 
+            & \( 0.3359 \quad 0.2392 \) 
             & \cellcolor{gray}
@@
         \textbf{mrg3}          
-            & \(p_{\mu} = 0.01715 \quad p_{\sigma} = 0.0234 \)
-            & \(p_{\mu} = 0.6365 \quad p_{\sigma} = 0.703 \) 
+            & \( 0.3942 \quad 0.7113 \)
+            & \( 0.3958 \quad 0.5026 \) 
+            & \( 0.8842 \quad 0.6079 \) 
             & \cellcolor{gray}
@@
         \textbf{yarn2}        
-            & \(p_{\mu} = 0.6767 \quad p_{\sigma} = 0.6782 \)  
-            & \(p_{\mu} = 0.4729 \quad p_{\sigma} = 0.4849 \)  
-            & \(p_{\mu} = 0.1485 \quad p_{\sigma} = 0.1613  \)  
+            & \( 0.1507 \quad  0.5990 \)  
+            & \( 0.1432 \quad 0.4116 \)  
+            & \( 0.4590 \quad 0.7271 \) 
+            & \( 0.4339 \quad 0.8737 \)  
             & \cellcolor{gray} \\
         \textbf{yarn3}          
-            & \(p_{\mu} = 0.1798 \quad p_{\sigma} = 0.3083 \)  
-            & \(p_{\mu} = 0.8226 \quad p_{\sigma} = 0.5178  \) 
-            & \(p_{\mu} = 0.3502 \quad p_{\sigma} = 0.4936  \)
-            & \(p_{\mu} = 0.5187 \quad p_{\sigma} = 0.5178  \) \\
-    \end{tabular}
+            & \( 0.3578 \quad 0.4295 \)  
+            & \( 0.3351 \quad 0.2750  \) 
+            & \( 0.9843 \quad 0.9042  \)
+            & \( 0.9017 \quad 0.6833 \) 
+            & \( 0.4517 \quad 0.8102  \) \\
+    \end{tabular}}
     \caption{P-values of the Influenza A test case}
-    \label{tab:measles_16:p_values}
+    \label{tab:influenza:p_values}
 \end{table}
@@
     \begin{tabular}{c|c|c|c|c|c|c}
-        & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
+        \textbf{lgc64\_shift}
+            & \( 0.2164 \quad 0.8855 \)
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
         \textbf{mrg2}      
-            & \(p_{\mu} = 0.6677 \quad p_{\sigma} = 0.7113 \) 
+            & \( 0.9754 \quad 0.8673 \) 
+            & \( 0.2264 \quad 0.9838 \) 
             & \cellcolor{gray}
@@
         \textbf{mrg3}          
-            & \(p_{\mu} = 0.6488 \quad p_{\sigma} = 0.6813 \)
-            & \(p_{\mu} = 0.9985 \quad p_{\sigma} = 0.9983 \) 
+            & \( 0.9630 \quad 0.9900 \)
+            & \( 0.2671 \quad 0.8882 \) 
+            & \( 0.9373 \quad 0.8687 \) 
             & \cellcolor{gray}
@@
         \textbf{yarn2}        
-            & \(p_{\mu} = 0.7061 \quad p_{\sigma} = 0.7513 \)  
-            & \(p_{\mu} = 0.4081 \quad p_{\sigma} = 0.3292 \)  
-            & \(p_{\mu} = 0.3812  \quad p_{\sigma} = 0.3917  \)  
+            & \( 0.3326 \quad 0.2670 \)  
+            & \( 0.5949 \quad 0.2232 \)  
+            & \( 0.3163 \quad 0.2107 \) 
+            & \( 0.3081 \quad 0.2400 \)  
             & \cellcolor{gray} \\
         \textbf{yarn3}          
-            & \(p_{\mu} = 0.3615 \quad p_{\sigma} = 0.3908  \)  
-            & \(p_{\mu} = 0.124 \quad p_{\sigma} = 0.1112  \) 
-            & \(p_{\mu} = 0.0929 \quad p_{\sigma} = 0.1258  \)
-            & \(p_{\mu} = 0.6495 \quad p_{\sigma} = 0.65  \) \\
+            & \( 0.6517 \quad 0.5366 \)  
+            & \( 0.3611 \quad 0.4624 \) 
+            & \( 0.6508 \quad 0.4457 \)
+            & \( 0.6282 \quad 0.5097 \) 
+            & \( 0.2195 \quad 0.6542 \) \\
     \end{tabular}
@@
 
-% TODO: investigate influence of threading on attack rate (hopefully minimal)
+\section{Future work}
+
+With respect to the analysis performed in this paper, it would be interesting to see an investigation of the influence of threading on the attack rate, or another representative metric of the output of the Stride simulator.
+It is clear that we hope and expect this effect to be minimal to nonexistent, but it is a good sanity check of the Stride codebase that this would be verified.
+
+\section{Postscriptum}
+
+This analysis was done using commit \texttt{5563ebd337ae75ed35b739307afe03bdb5219325} of the \href{https://github.com/LEDfan/Bachelorproef}{LEDfan/Bachelorproef} repository, corresponding to the \texttt{fde6c507e8596bde6d632f6759c9e65f4b878a68} commit in the upstream \href{https://github.com/broeckho/stride}{broeckho/stride} repository.
 

### 2018-03-10 assets/src/week4/paper/main.tex
Update plots for paper week 4

@@
        \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
-        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.0.4431
+        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.4431
     \end{tabular}
@@
 We can consider the attack rate to be normally distributed in all presented cases.
+
+A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at \url{TODO TODO TODO}.
+% TODO: update url once published to gh-pages
+
+\begin{figure}%
+   	\makebox[\textwidth][c]{%
+   		\centering%
+   		\subfloat[QQ plot of Influenza A results with \texttt{lgc64}]{%
+   			{\includegraphics[width=0.5\textwidth]{images/influenza_qq_lgc64.png}}%
+   		}%
+   		\qquad%
+   		\subfloat[Histogram of Influenza A results with \texttt{lgc64}]{%
+  			{\includegraphics[width=0.5\textwidth]{images/influenza_histo_lgc64.png}}%
+   		}%
+   	}\\
+   	\makebox[\textwidth][c]{%
+   		\centering%
+   		\subfloat[QQ plot of Measles 16 results with \texttt{mrg2}]{%
+   			{\includegraphics[width=0.5\textwidth]{images/measles_qq_mrg2.png}}%
+   		}%
+   		\qquad%
+   		\subfloat[Histogram of Measles 16 results with \texttt{mrg2}]{%
+  			{\includegraphics[width=0.5\textwidth]{images/measles_histo_mrg2.png}}%
+   		}%
+   	}%
+   	\label{fig:normality}
+   	\caption{Visually evaluating the normality of the attack rate}
+\end{figure}
 
@@
 
-\clearpage
-
-\begin{figure}%
-   	\makebox[\textwidth][c]{%
-   		\centering%
-   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64}]{%
-   			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64.png}}%
-   		}%
-   		\qquad%
-   		\subfloat[Boxplot of Influenza A run with \texttt{lgc64\_shift}]{%
-  			{\includegraphics[width=0.5\textwidth]{images/boxplot_lgc64_shift.png}}%
-   		}%
-   	}\\
-   	\makebox[\textwidth][c]{%
-   		\centering%
-   		\subfloat[Boxplot of Influenza A run with \texttt{mrg2}]{%
-   			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg2.png}}%
-   		}%
-   		\qquad%
-   		\subfloat[Boxplot of Influenza A run with \texttt{mrg3}]{%
-  			{\includegraphics[width=0.5\textwidth]{images/boxplot_mrg3.png}}%
-   		}%
-   	}\\
-   	\makebox[\textwidth][c]{%
-   		\centering%
-   		\subfloat[Boxplot of Influenza A run with \texttt{yarn2}]{%
-   			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn2.png}}%
-   		}%
-   		\qquad%
-   		\subfloat[Boxplot of Influenza A run with \texttt{yarn3}]{%
-  			{\includegraphics[width=0.5\textwidth]{images/boxplot_yarn3.png}}%
-   		}%
-   	}%
-   	\caption{Running time in function of number of threads}
-
-\end{figure}
-
 \section{Future work}

### 2018-03-10 assets/src/week4/paper/main.tex
Small adjustements after peer-revie

@@
 for the test outcome. We determined these ranges by running the tested simulations multiple times (100+). We noticed
-using a QQ-Plot and hypothesis tests that the Attack Rate can be considered to follow a normal distribution.
+by using a QQ-Plot and hypothesis tests that the Attack Rate can be considered to follow a normal distribution.
 For the accepted ranges, we decided to allow a distance of 2 standard deviations from the observed mean.
@@
 The analysis described in this section was performed on a 32 core AMD machine.
-Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at time of writing.
+Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing.
 By using a Bash-script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/597e9d14356a40f10c52dbd789ce495f0891720e/assets/src/week3/bench.sh}} % TODO update links to website
@@
 Using a Python3 script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/b8b67f7083ba8a523bdb16f0c6fd0fdfeea7dacf/assets/src/week3/random_engines.py}} % TODO update links to website
-the simulation was run using the different random engines, at the same time the running time
-was measured.
+the simulation was run using the different random engines, at the same time measuring the running time.
 
@@
 \subsection{Influence of random engine}
-The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine needs the most time.
+The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine requires the most amount of time.
 The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 6 seconds.
@@
 The distribution analysis of the results with different random engines was done with 100 data points for each random engine.
-While this is still a relatively sample size, much larger sample sizes were not feasible due to the time requirements to run them all.
+While this is still a relatively small sample size, much larger sample sizes were not feasible due to the time requirements to run them all.
 
@@
 As expected the RNG engine doesn't have influence on this outcome.
-The same holds for the third test case (Influenza C\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L91}}) which uses very low seeding rate and a large immunity factor.
+The same holds for the third test case (Influenza C\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L91}}) which uses a very low seeding rate and a large immunity factor.
 The attack vector for every engine is 5.
 The Measles 16\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L97}} testcase is more interesting for the analysis of the RNG engines.
-The disease simulated is not influeanza but the measles.
+The disease simulated is not influenza but the measles.
 The $R_0$ value is set to 16, which results in a very large part of the population becoming infected.
@@
 In this section the equality of the different value ranges which are accepted by the tests for each random engine is verified.
-Only the Influenza A and Measles 16 test cases are studied since they provide have a variable range.
+Only the Influenza A and Measles 16 test cases are studied since they provide a variable range.
 The tests are done using a Levene test for the standard deviations and a t-test for related samples for the means.
@@
 The p-values for these tests are listed in \cref{tab:influenza:p_values} and \cref{tab:measles_16:p_values}.
-They clearly indicates that the \(H_0\) should not be rejected for both tests on a confidence level of $\alpha = 0.05$.
+They clearly indicate that the \(H_0\) should not be rejected for both tests on a confidence level of $\alpha = 0.05$.
 Consequently, we can fairly confidently conclude that the distribution of the attack rate does not differ significantly when using a different random engine.

### 2018-03-10 assets/src/week4/paper/main.tex
4->6
Add more script from past week + update URL's in Paper

@@
 Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing.
-By using a Bash-script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/597e9d14356a40f10c52dbd789ce495f0891720e/assets/src/week3/bench.sh}} % TODO update links to website
+By using a Bash-script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/bench.sh}} % TODO update links to website
 the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.
@@
 
-Using a Python3 script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/b8b67f7083ba8a523bdb16f0c6fd0fdfeea7dacf/assets/src/week3/random_engines.py}} % TODO update links to website
+Using a Python3 script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines.py}} 
 the simulation was run using the different random engines, at the same time measuring the running time.
@@
 The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine requires the most amount of time.
-The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 6 seconds.
+The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 4 seconds.
 Thus there isn’t a big difference.
@@
 
-A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at \url{TODO TODO TODO}.
-% TODO: update url once published to gh-pages
+A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website \footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
 

### 2018-03-10 assets/src/week4/paper/main.tex
Remove space before footnote

@@
 
-A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website \footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
+A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
 

### 2018-03-10 assets/src/week4/paper/main.tex

@@
 The second topic of this paper is to analyze the influence of the random number generator engine on the Attack Rate.
-Stride uses the Trng library \cite{bauke2015tina} as random number generator.
+Stride uses the TRNG library \cite{bauke2015tina} as random number generator.
 The inspected engines are \texttt{lgc64}, \texttt{lgc64\_shift}, \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2} and \texttt{yarn3}.
@@
 Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing.
-By using a Bash-script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/bench.sh}} % TODO update links to website
+By using a Bash-script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/bench.sh}}
 the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.
@@
 Using a Python3 script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines.py}} 
-the simulation was run using the different random engines, at the same time measuring the running time.
+the simulation was run using the different random engines, while also measuring the running time.
 
@@
 The $R_0$ value is set to 16, which results in a very large part of the population becoming infected.
-The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the whole population, so the attack rate is for all the engines the same.
+The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the whole population, so the attack rate is the same for all engines.
 
@@
 \label{par:normality}
-To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots and histograms of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilkes test.
+To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots and histograms of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilk test.
 
 % Influenza A
-Looking at the Influenza A testcase, we find the resulting P-values for Shapiro-Wilkes test in \cref{tab:influenza_a:shapiro}.
+Looking at the Influenza A testcase, we find the resulting P-values for Shapiro-Wilk test in \cref{tab:influenza_a:shapiro}.
 Here, all random engines result in an (at least approximately) normal distribution for the attack rate.
@@
     \end{tabular}
-    \caption{P-values of the Influenza A test case for the Shapiro-Wilkes normality test}
+    \caption{P-values of the Influenza A test case for the Shapiro-Wilk normality test}
     \label{tab:influenza_a:shapiro}
@@
 % Measles 16
-For the Measles 16 testcase, resulting P-values for the Shapiro-Wilkes test can be found in \cref{tab:measles_16:shapiro}.
+For the Measles 16 testcase, resulting P-values for the Shapiro-Wilk test can be found in \cref{tab:measles_16:shapiro}.
 
@@
     \end{tabular}
-    \caption{P-values of the Measles 16 test case for the Shapiro-Wilkes normality test}
+    \caption{P-values of the Measles 16 test case for the Shapiro-Wilk normality test}
     \label{tab:measles_16:shapiro}
@@
    	}%
+   	\caption{Visually evaluating the normality of the attack rate}
    	\label{fig:normality}
-   	\caption{Visually evaluating the normality of the attack rate}
 \end{figure}

### 2018-04-21 assets/src/paper-stochastisch/main.tex
Add boilerplate paper + Makefile

--- 2018-03-10 assets/src/week4/paper/main.tex
@@
-\documentclass{acmart}
+\documentclass[natbib=true]{acmart}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{bm}
+
+\setcitestyle{numbers,sort&compress}
 
@@
 \begin{abstract}
-    In this article, we investigate a few properties of the Stride project.
-In particular, we look at the influence of the amount of parallelization with respect to the running time of a simulation and the difference in simulation outcomes when varying the used random number generator.
 \end{abstract}
@@
 \section{Introduction}
-Stride \cite{KUYLEN20172438} is an individual-based Simulator for the Transmission of Infectious Diseases with focus on model flexibility and
-performance. The performance of such a simulator is important for the researcher to have fast feedback in order to
-build a reasonable model of the disease. The Stride program currently has scenario tests to prevent regressions in the
-simulation output. To provide fast feedback to the developers working on Stride the test should run sufficiently quickly.
-The running time of the tests are a good indication of the running time of the simulator itself. Hence we perform a
-performance analysis of the running time of tests and the influence of parallelism.
-
-The scenario tests are using the Attack Rate as parameter to assert the simulator outcome. Since Stride is a stochastic
-system and thus relies on randomness, the output of its tests are variable. Therefore the tests use an acceptability range
-for the test outcome. We determined these ranges by running the tested simulations multiple times (100+). We noticed
-by using a QQ-Plot and hypothesis tests that the Attack Rate can be considered to follow a normal distribution.
-For the accepted ranges, we decided to allow a distance of 2 standard deviations from the observed mean.
-
-The second topic of this paper is to analyze the influence of the random number generator engine on the Attack Rate.
-Stride uses the TRNG library \cite{bauke2015tina} as random number generator.
-The inspected engines are \texttt{lgc64}, \texttt{lgc64\_shift}, \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2} and \texttt{yarn3}.
 
@@
 
-\subsection{Influence of multi-threading}
-
-The analysis described in this section was performed on a 32 core AMD machine.
-Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing.
-By using a Bash-script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/bench.sh}}
-the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.
-
-\subsection{Influence of random engine}
-
-Using a Python3 script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines.py}} 
-the simulation was run using the different random engines, while also measuring the running time.
-
 \section{Results}
-
-\subsection{Influence of multi-threading}
-The running time in function of the number of threads are shown in \cref{fig:threads}. The difference between the first and third
-quartile is only 0.45 seconds. This difference is negligible compared to the 27 seconds running time. Even the furthest outliers are less than 2 seconds apart. We can safely conclude
-that the parallelisation of the code doesn’t have a great influence on the performance. There should hopefully be some room for improvement here for the performance of Stride.
-Note that for each number of threads, the values are obtained by running the Influenza A simulation 15 times and taking the average running time.
-
-\sidebyside[!hbt][fig:threads:scatter][fig:threads:boxplot]
-    {Connected scatter plot}
-    {images/performance_scatter.png}
-    {Boxplot}
-    {images/boxplot_performance.png}
-    {Running time in function of number of threads}
-    {fig:threads}
-\subsection{Influence of random engine}
-The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine requires the most amount of time.
-The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 4 seconds.
-Thus there isn’t a big difference.
-A complete comparison of running times can be found in \cref{fig:engine:running}.
-The distribution analysis of the results with different random engines was done with 100 data points for each random engine.
-While this is still a relatively small sample size, much larger sample sizes were not feasible due to the time requirements to run them all.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{images/engine_performance_bar.png}
-    \caption{Running time of the different rng engines for the influenza A test case.}
-    \label{fig:engine:running}
-\end{figure}
-
-The first test case of Stride (Influenza A\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L82}})
-performs a simulation of influenza in Flanders, with an $R_0$ value\footnote{Basic reproduction number, a measure for the infectiousness of a disease: the amount of people will 1 infected person infect directly in a completely
-susceptible population.} of 3.0. For this test case the range of allowed attack rates doesn't change much. 
-The second test case (Influenza B\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L86}}) uses a seeding rate of 0, which results in a constant attack rate of 0.
-As expected the RNG engine doesn't have influence on this outcome.
-The same holds for the third test case (Influenza C\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L91}}) which uses a very low seeding rate and a large immunity factor.
-The attack vector for every engine is 5.
-The Measles 16\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/dd1ef48867238d62446813f47d6718908505b7f2/test/cpp/gtester/BatchRuns.cpp\#L97}} testcase is more interesting for the analysis of the RNG engines.
-The disease simulated is not influenza but the measles.
-The $R_0$ value is set to 16, which results in a very large part of the population becoming infected.
-The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the whole population, so the attack rate is the same for all engines.
-
-\subsection{Normality of the output}
-\label{par:normality}
-To validate our assumption that the distribution of the attack rate was normal for our tests, we both looked at QQ-plots and histograms of the outputs of different runs against a reference normal distribution with $\mu = \bar{X}, \sigma=S_X$, verified that histograms had a more or less normal look to them, and verified with the Shapiro-Wilk test.
-
-% Influenza A
-Looking at the Influenza A testcase, we find the resulting P-values for Shapiro-Wilk test in \cref{tab:influenza_a:shapiro}.
-Here, all random engines result in an (at least approximately) normal distribution for the attack rate.
-\begin{table}[!hbt]
-    \begin{tabular}{c c c c c c}
-       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
-        0.8719 & 0.4609 & 0.9385 & 0.6556 & 0.7254 & 0.7089
-    \end{tabular}
-    \caption{P-values of the Influenza A test case for the Shapiro-Wilk normality test}
-    \label{tab:influenza_a:shapiro}
-\end{table}
-
-% Measles 16
-For the Measles 16 testcase, resulting P-values for the Shapiro-Wilk test can be found in \cref{tab:measles_16:shapiro}.
-
-\begin{table}[!hbt]
-    \begin{tabular}{c c c c c c}
-       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
-        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.4431
-    \end{tabular}
-    \caption{P-values of the Measles 16 test case for the Shapiro-Wilk normality test}
-    \label{tab:measles_16:shapiro}
-\end{table}
-
-We can consider the attack rate to be normally distributed in all presented cases.
-
-A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
-
-\begin{figure}%
-   	\makebox[\textwidth][c]{%
-   		\centering%
-   		\subfloat[QQ plot of Influenza A results with \texttt{lgc64}]{%
-   			{\includegraphics[width=0.5\textwidth]{images/influenza_qq_lgc64.png}}%
-   		}%
-   		\qquad%
-   		\subfloat[Histogram of Influenza A results with \texttt{lgc64}]{%
-  			{\includegraphics[width=0.5\textwidth]{images/influenza_histo_lgc64.png}}%
-   		}%
-   	}\\
-   	\makebox[\textwidth][c]{%
-   		\centering%
-   		\subfloat[QQ plot of Measles 16 results with \texttt{mrg2}]{%
-   			{\includegraphics[width=0.5\textwidth]{images/measles_qq_mrg2.png}}%
-   		}%
-   		\qquad%
-   		\subfloat[Histogram of Measles 16 results with \texttt{mrg2}]{%
-  			{\includegraphics[width=0.5\textwidth]{images/measles_histo_mrg2.png}}%
-   		}%
-   	}%
-   	\caption{Visually evaluating the normality of the attack rate}
-   	\label{fig:normality}
-\end{figure}
-
-\subsection{Equality of acceptable ranges for the test cases}
-
-In this section the equality of the different value ranges which are accepted by the tests for each random engine is verified.
-Only the Influenza A and Measles 16 test cases are studied since they provide a variable range.
-The tests are done using a Levene test for the standard deviations and a t-test for related samples for the means.
-
-The hypotheses for the Levene test:
-\[
-\begin{aligned}
- H_0 &: \sigma_1 = \sigma_2\\
- H_1 &: \sigma_1 \ne \sigma_2\
-\end{aligned}
-\]
-
-and for the t-test:
-\[
-\begin{aligned}
- H_0 &: \mu_1 = \mu_2  \\
- H_1 &: \mu_1 \ne \mu_2.
-\end{aligned}
-\]
-
-The p-values for these tests are listed in \cref{tab:influenza:p_values} and \cref{tab:measles_16:p_values}.
-They clearly indicate that the \(H_0\) should not be rejected for both tests on a confidence level of $\alpha = 0.05$.
-Consequently, we can fairly confidently conclude that the distribution of the attack rate does not differ significantly when using a different random engine.
-
-\begin{table}[!hbt]
-    \centering
-    \bgroup
-    \def\arraystretch{2}
-    \begin{tabular}{c|c|c|c|c|c}
-                                & \textbf{Influenza A}  & \textbf{Measles 16} \\ \hline
-        \texttt{lgc64}          & \([1896, 2364]\)       & \([588959, 591317]\) \\
-        \texttt{lgc64\_shift}   & \([1893, 2372]\)       & \([588992, 591360]\) \\
-        \texttt{mrg2}           & \([1899, 2334]\)       & \([588967, 591307]\) \\
-        \texttt{mrg3}           & \([1891, 2345]\)       & \([589012, 591268]\) \\
-        \texttt{yarn2}          & \([1879, 2331]\)       & \([588836, 591615]\) \\
-        \texttt{yarn3}          & \([1902, 2331]\)       & \([588751, 591443]\) \\
-    \end{tabular}
-    \egroup
-    \caption{The acceptable attack rates for the Influenza A en Measles 16 test case for every random number engine}
-    \label{tab:ranges_engines}
-\end{table}
-
-\begin{table}[!hbt]
-    \centerline{\begin{tabular}{c|c|c|c|c|c|}
-        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
-        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
-        \textbf{lgc64\_shift}
-            & \( 0.8819 \quad 0.7593 \)
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{mrg2}      
-            & \( 0.2797 \quad 0.3763 \) 
-            & \( 0.3359 \quad 0.2392 \) 
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{mrg3}          
-            & \( 0.3942 \quad 0.7113 \)
-            & \( 0.3958 \quad 0.5026 \) 
-            & \( 0.8842 \quad 0.6079 \) 
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{yarn2}        
-            & \( 0.1507 \quad  0.5990 \)  
-            & \( 0.1432 \quad 0.4116 \)  
-            & \( 0.4590 \quad 0.7271 \) 
-            & \( 0.4339 \quad 0.8737 \)  
-            & \cellcolor{gray} \\
-        \textbf{yarn3}          
-            & \( 0.3578 \quad 0.4295 \)  
-            & \( 0.3351 \quad 0.2750  \) 
-            & \( 0.9843 \quad 0.9042  \)
-            & \( 0.9017 \quad 0.6833 \) 
-            & \( 0.4517 \quad 0.8102  \) \\
-    \end{tabular}}
-    \caption{P-values of the Influenza A test case}
-    \label{tab:influenza:p_values}
-\end{table}
-
-\begin{table}[!hbt]
-    \begin{tabular}{c|c|c|c|c|c|c}
-        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
-        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
-            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
-        \textbf{lgc64\_shift}
-            & \( 0.2164 \quad 0.8855 \)
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{mrg2}      
-            & \( 0.9754 \quad 0.8673 \) 
-            & \( 0.2264 \quad 0.9838 \) 
-            & \cellcolor{gray}
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{mrg3}          
-            & \( 0.9630 \quad 0.9900 \)
-            & \( 0.2671 \quad 0.8882 \) 
-            & \( 0.9373 \quad 0.8687 \) 
-            & \cellcolor{gray}
-            & \cellcolor{gray} \\
-        \textbf{yarn2}        
-            & \( 0.3326 \quad 0.2670 \)  
-            & \( 0.5949 \quad 0.2232 \)  
-            & \( 0.3163 \quad 0.2107 \) 
-            & \( 0.3081 \quad 0.2400 \)  
-            & \cellcolor{gray} \\
-        \textbf{yarn3}          
-            & \( 0.6517 \quad 0.5366 \)  
-            & \( 0.3611 \quad 0.4624 \) 
-            & \( 0.6508 \quad 0.4457 \)
-            & \( 0.6282 \quad 0.5097 \) 
-            & \( 0.2195 \quad 0.6542 \) \\
-    \end{tabular}
-    \caption{P-values of the Measles 16 test case}
-    \label{tab:measles_16:p_values}
-\end{table}
 
@@
 
-With respect to the analysis performed in this paper, it would be interesting to see an investigation of the influence of threading on the attack rate, or another representative metric of the output of the Stride simulator.
-It is clear that we hope and expect this effect to be minimal to nonexistent, but it is a good sanity check of the Stride codebase that this would be verified.
-
 \section{Postscriptum}
-
-This analysis was done using commit \texttt{5563ebd337ae75ed35b739307afe03bdb5219325} of the \href{https://github.com/LEDfan/Bachelorproef}{LEDfan/Bachelorproef} repository, corresponding to the \texttt{fde6c507e8596bde6d632f6759c9e65f4b878a68} commit in the upstream \href{https://github.com/broeckho/stride}{broeckho/stride} repository.
 

### 2018-04-22 assets/src/paper-stochastisch/main.tex

@@
 \usepackage[utf8]{inputenc}
+\usepackage[shortlabels]{enumitem}
 \usepackage{subfig}
 \usepackage{graphicx}
-\usepackage{sidebyside}
 \usepackage{cleveref}
@@
 
-\title{An inquiry into the influence of parallelism and the choice of random
-engines on the runtime and results of Stride}
+\title{Analysis of the stochastic spread of Stride simulation outcomes}
 
@@
 
-% \date{March 2018}
-
 \begin{abstract}
+In this article we investigate a few properties of the Stride project.
+In particular we look at how to quantify the stochastic margins on the end result of a simulation run.
+Thereafter we try to identify how this information can be used for detecting unintended model changes with scenario tests.
 \end{abstract}
@@
 \section{Introduction}
+Stride \cite{KUYLEN20172438} is an individual-based Simulator for the Transmission of Infectious Diseases with focus on model flexibility and
+performance. 
+Currently the Stride program has scenario tests to prevent regressions in the
+simulation output. 
+These tests use the Attack Rate as a parameter to assert the simulator outcome. Since Stride is a stochastic
+system and thus relies on randomness, the output of its tests are variable.
+The need for an acceptability range for the test outcome and the distribution of the test outcomes were examined.
 
@@
 
-\section{Methods}
+\section{Scenario tests}
 
-\section{Results}
+The first test case of Stride (Influenza A \ref{sup:influenza_a}) performs a simulation of influenza in Flanders, with an $R_0$ \footnote{Basic reproduction number, a measure for the infectiousness of a disease: the amount of people 1 infected person will infect directly in a completely susceptible population.} value of 3.0.
 
-\section{Future work}
+The second test case (Influenza B) uses a seeding rate of 0, which results in a constant attack rate of 0. As expected, the RNG engine does not have influence on this outcome. 
+The same holds for the third test case (Influenza C) which uses a very low seeding rate and a large immunity factor.
+The attack vector for every run is 5.
+The Measles 16 test case simulates the measles, the \(R_0\) value is set to 16, which results in a very large part of the population becoming infected. 
+The last testcase (Measles 60) sets the $R_0$ value to 60. It infects the
+whole population hence the attack rate is the same for all runs.
 
-\section{Postscriptum}
+\section{Distribution of test outcome}
 
-\clearpage
+Before determining useful margins for the test outcome the distribution of these values has to be found.
+The Stride program is using the TRNG library \citep{bauke2015tina} for generating random numbers.
+This libray is capable of using different RNG engines, therefore it is necessary to find the distribution of the attack rate for all these different random engines.
+It is expected that all these random engines have the same distribution and that the outcomes are equivalent. 
+The tested random number engines are \texttt{lgc64}, \texttt{lgc64\_shift}, \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2} and \texttt{yarn3}.
+
+In order to do a statistical analysis, sufficient test data has to be generated. This was done using a Python script provided at \ref{sup:random_engines.py}. 
+This script will execute stride 15 times for each random number engine, while choosing a seed for the number in the range \([0, 1000000000]\) using Python's \texttt{random.randint}\footnote{https://docs.python.org/3/library/random.html\#random.randint} method.
+Python is using the \texttt{Mersenne Twister} as the core generator and generates a seed based on the random source of the operating system (e.g.
+\texttt{/dev/urandom} on a UNIX-like system) or the current time as a fallback.
+Only the Influenza A and Measles 16 were tested since these are the only scenario tests without a constant Attack Rate. 
+The script was adapated to generate 100 datapoints for each test case. The results can be found at \ref{sup:data-points:a} and \ref{sup:data-points:16} for respectively Influenza A and Measles 16.
+
+A good starting point is testing whether it is normally distributed.
+To give an estimate of the normality QQ-plots were used (see \cref{img:qq-plot:influenza_a} for an example).
+All QQ-plots can be found at \ref{sup:qq-plots}, histograms of the data can be found at \ref{sup:histograms}.
+The QQ-plots already indicate rather normal distributed data.
+To formally confirm the normality the Shapiro-Wilk test was performed of which the p-values can be found in \cref{tab:influenza_a:shapiro} and \cref{tab:measles_16:shapiro}.
+All tests results in an (at least approximately) normal distribution for the attack rate.
+
+\begin{figure}[!hbt]
+    \centering
+    \includegraphics[width=0.7\textwidth]{images/influenza_a_qq_lgc64.png}
+    \caption{QQ-Plot of Influenza A with the \texttt{lgc64} RNG engine}
+    \label{img:qq-plot:influenza_a}
+\end{figure}
+
+\begin{table}[!hbt]
+    \begin{tabular}{c c c c c c}
+       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
+        0.8719 & 0.4609 & 0.9385 & 0.6556 & 0.7254 & 0.7089
+    \end{tabular}
+    \caption{P-values of the Influenza A test case for the Shapiro-Wilk normality test}
+    \label{tab:influenza_a:shapiro}
+\end{table}
+
+\begin{table}[!hbt]
+    \begin{tabular}{c c c c c c}
+       \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} & \textbf{yarn3}\\
+        0.8231 & 0.4216 & 0.9115 & 0.4199 & 0.1473 & 0.4431
+    \end{tabular}
+    \caption{P-values of the Measles 16 test case for the Shapiro-Wilk normality test}
+    \label{tab:measles_16:shapiro}
+\end{table}
+
+\FloatBarrier
+
+\section{Test Margins}
+
+The scenario tests of Stride are run both sequential and parallel. 
+OpenMP is used as library to facilitate the parallelization. 
+As noted before Stride is a stochastic program and is using the TRNG library. 
+The random number generation in stride is managed by the \texttt{RnManager} class, which ensures only one random number engine is constructed, because it is important not to generate the same random numbers (since only one seed is used during the simulator lifetime), which would be the behaviour when initialising RNG multiple times.
+
+The parallelization of the test cases may cause differences in test outcome, even when using the same seed and RNG engine. 
+Due to the unpredictable interleaving of the different threads, the random numbers generated will be drawn in a different order.
+
+In the sections that follow the different changes in the test environment and how they should be treated are discussed.
+
+\subsection{When changing the implementation without altering the theoretical model}
+
+The tests are using a constant seed, therefore one would expect that outcome of both the sequential and parallel tests do not change.
+
+It may be the case that when refactoring or rewriting source code, the execution order of some parts changes.
+As a result the usage of random numbers may change and therefore the test outcome changes although the theoretical and conceptual model have not changed.
+In other words, the implementation changed, but the underlying algorithms did not.
+
+Additionally the parallel tests will almost always vary in outcome for the reasons described earlier on.
+
+It is clear that for the parallel tests there is no other option than working with a margin on the allowed outcomes.
+
+There are a few options for the sequential tests. One of them is to have a constant outcome for this type of test.
+The advantage is that a developer will be notified by the Continuous Integration service even for the slightest change in outcome.
+The developer can then validate this failure and check whether it is within the allowable margins and will re-calibrate or if the developer made a mistake in the code.
+
+A second option is to have a margin for the sequential tests just like for the parallel tests. The developer will have less false-positive notifications of test failures.
+On the other hand the chance that the developer has made a mistake that remains unnoticed is bigger. It may be preferred to use a smaller margin in this case.
+
+A compromise could be to let the tests check if the outcome is the exact expected value. If this is the case the tests pass.
+If not it checks if the outcome falls within the allowable margins. When this is the case only a warning is emitted but the tests pass. In all other cases the test fails.
+This results in less false-positives, but the developer can't blindly trust the pass of a test. They have to check for warnings, which will be tough when using a CI system. % TODO: regular
+This violates the principle of binary outcomes of software tests. 
+Using a CI system with three states could solve this, but this may convert itself into a binary system again with only warning and failure.
+
+Since it is known that the Attack Rate is normally distributed the standard deviation can be used to define a allowable margin.
+It turns out that 2 times the standard deviation is a good fit since 95\% of the possible attack rates will fit between that range.
+
+\subsection{When changing the theoretical model}
+
+This is the most challenging case.
+A change in the theoretical model should definitely be caught by the sequential tests (since these work without a margin), and ideally should be caught by the parallel tests too.
+However since these do work with a margin it is possible that the change is too small to be out of the range.
+
+When such a change is performed by the developer, a calibration tool should be used to calculate new values for both the sequential and parallel tests.
+The developer of the change should be very cautious to blindly trust the calibration tool, and manually verify the new output of the tests.
+In other words they should check if the change in outcome is what they expected when adapting the code.
+
+\subsection{When changing the RNG engine}
+
+Changing the RNG engine should not result in a ''big'' difference when using another engine. This difference can again be correctly qualified by using two times the standard deviation.
+
+Earlier on it was proven that independent of the choice of RNG engine the test outcome is normally distributed.
+The same data and scripts were used to conclude that the different random number engines generate the same range of test outcomes.
+Again only the Influenza A and Measles 16 were studied. The Levene test was used to test the equality of the standard deviation, a t-test for related samples was used for the means.
+
+The hypotheses for the Levene test:
+\[
+\begin{aligned}
+ H_0 &: \sigma_1 = \sigma_2\\
+ H_1 &: \sigma_1 \ne \sigma_2\
+\end{aligned}
+\]
+
+and for the t-test:
+\[
+\begin{aligned}
+ H_0 &: \mu_1 = \mu_2  \\
+ H_1 &: \mu_1 \ne \mu_2.
+\end{aligned}
+\]
+
+The p-values for these tests are listed in \cref{tab:influenza:p_values} and \cref{tab:measles_16:p_values}.
+They clearly indicate that the \(H_0\) should not be rejected for both tests on a confidence level of $\alpha = 0.05$.
+Consequently, we can confidently conclude that the distribution of the attack rate does not differ significantly when using a different random engine.
+
+\begin{table}[!hbt]
+    \centering
+    \bgroup
+    \def\arraystretch{2}
+    \begin{tabular}{c|c|c|c|c|c}
+                                & \textbf{Influenza A}  & \textbf{Measles 16} \\ \hline
+        \texttt{lgc64}          & \([1896, 2364]\)       & \([588959, 591317]\) \\
+        \texttt{lgc64\_shift}   & \([1893, 2372]\)       & \([588992, 591360]\) \\
+        \texttt{mrg2}           & \([1899, 2334]\)       & \([588967, 591307]\) \\
+        \texttt{mrg3}           & \([1891, 2345]\)       & \([589012, 591268]\) \\
+        \texttt{yarn2}          & \([1879, 2331]\)       & \([588836, 591615]\) \\
+        \texttt{yarn3}          & \([1902, 2331]\)       & \([588751, 591443]\) \\
+    \end{tabular}
+    \egroup
+    \caption{The acceptable attack rates for the Influenza A en Measles 16 test case for every random number engine}
+    \label{tab:ranges_engines}
+\end{table}
+
+\begin{table}[!hbt]
+    \centerline{\begin{tabular}{c|c|c|c|c|c|}
+        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
+        \textbf{lgc64\_shift}
+            & \( 0.8819 \quad 0.7593 \)
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{mrg2}      
+            & \( 0.2797 \quad 0.3763 \) 
+            & \( 0.3359 \quad 0.2392 \) 
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{mrg3}          
+            & \( 0.3942 \quad 0.7113 \)
+            & \( 0.3958 \quad 0.5026 \) 
+            & \( 0.8842 \quad 0.6079 \) 
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{yarn2}        
+            & \( 0.1507 \quad  0.5990 \)  
+            & \( 0.1432 \quad 0.4116 \)  
+            & \( 0.4590 \quad 0.7271 \) 
+            & \( 0.4339 \quad 0.8737 \)  
+            & \cellcolor{gray} \\
+        \textbf{yarn3}          
+            & \( 0.3578 \quad 0.4295 \)  
+            & \( 0.3351 \quad 0.2750  \) 
+            & \( 0.9843 \quad 0.9042  \)
+            & \( 0.9017 \quad 0.6833 \) 
+            & \( 0.4517 \quad 0.8102  \) \\
+    \end{tabular}}
+    \caption{P-values of the Influenza A test case}
+    \label{tab:influenza:p_values}
+\end{table}
+
+\begin{table}[!hbt]
+    \begin{tabular}{c|c|c|c|c|c|c}
+        & \textbf{lgc64} & \textbf{lgc64\_shift} & \textbf{mrg2} & \textbf{mrg3} & \textbf{yarn2} \\
+        &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \)
+            &  \( \bm{p_\mu} \quad \bm{p_\sigma} \) \\
+        \textbf{lgc64\_shift}
+            & \( 0.2164 \quad 0.8855 \)
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{mrg2}      
+            & \( 0.9754 \quad 0.8673 \) 
+            & \( 0.2264 \quad 0.9838 \) 
+            & \cellcolor{gray}
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{mrg3}          
+            & \( 0.9630 \quad 0.9900 \)
+            & \( 0.2671 \quad 0.8882 \) 
+            & \( 0.9373 \quad 0.8687 \) 
+            & \cellcolor{gray}
+            & \cellcolor{gray} \\
+        \textbf{yarn2}        
+            & \( 0.3326 \quad 0.2670 \)  
+            & \( 0.5949 \quad 0.2232 \)  
+            & \( 0.3163 \quad 0.2107 \) 
+            & \( 0.3081 \quad 0.2400 \)  
+            & \cellcolor{gray} \\
+        \textbf{yarn3}          
+            & \( 0.6517 \quad 0.5366 \)  
+            & \( 0.3611 \quad 0.4624 \) 
+            & \( 0.6508 \quad 0.4457 \)
+            & \( 0.6282 \quad 0.5097 \) 
+            & \( 0.2195 \quad 0.6542 \) \\
+    \end{tabular}
+    \caption{P-values of the Measles 16 test case}
+    \label{tab:measles_16:p_values}
+\end{table}
+
+\FloatBarrier
+
+\subsection{When changing the seed for the RNG}
+
+This is an extra test case added to the Stride test-suite to ensure that the seed provided by the random number engine doesn't change the test outcome.
+
+Since a non-constant seed is used the sequential-test will not have a constant outcome anymore.
+Instead it will have the same margin as the parallel tests before (i.e.
+two times the standard deviation).
+
+Again the same script was used to test for normality and thus the same output ranges was used as listed in \cref{tab:ranges_engines}.
+
+\section{Supplementary Materials}
+
+    \begin{enumerate}[label={[\arabic*]},ref={[sup~\arabic*]}]
+        \item Influenza A scenario test \\
+            \url{https://github.com/LEDfan/Bachelorproef/blob/master/test/cpp/gtester/ScenarioData.cpp\#L39}
+            \label{sup:influenza_a}
+
+        \item Python script to generate test data \\
+            \url{https://ledfan.github.io/Bachelorproef/assets/src/paper-stochastisch/supplemental/random_engines.py} 
+            \label{sup:random_engines.py}
+
+        \item Data for Influenza A \\
+            \url{https://ledfan.github.io/Bachelorproef/assets/src/paper-stochastisch/supplemental/engine_count_influenza.txt}
+            \label{sup:data-points:a}
+
+        \item Data for Measles 16 \\
+            \url{https://ledfan.github.io/Bachelorproef/assets/src/paper-stochastisch/supplemental/engine_count_measles.txt}
+            \label{sup:data-points:16}
+
+        \item QQ-plots for Influenza A and Measles 16 for the different RNG engines \\ 
+            \url{https://ledfan.github.io/Bachelorproef/assets/src/paper-stochastisch/supplemental/qq-plots.html} 
+            \label{sup:qq-plots}
+
+        \item Histograms for Influenza A and Measles 16 for the different RNG engines \\ 
+            \url{https://ledfan.github.io/Bachelorproef/assets/src/paper-stochastisch/supplemental/histograms.html} 
+            \label{sup:histograms}
+
+    \end{enumerate}
 

### 2018-06-19 doc/latex/02-Software.tex
Early version of an updated userManual

%%!TEX root = ./UserManual.tex
\chapter{Software}
\label{chap:software}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% System Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Requirements}
\label{section:system}

Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
To use the visualization tools Qt is needed (at least version 5.9), besides that the following tools needs to be installed:
\begin{compactitem}
    \item g++
    \item make
    \item CMake (>= v3.10)
    \item Boost
    \item Python (optional, for automatization)
    \item Doxygen (optional, for documentation)
    \item LaTeX (optional, for documentation)
\end{compactitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Installation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Installation}
\label{section:Installation}

To install the project, first obtain the source code by cloning the repository to a directory or download a zip file with all project
material from the GitHub website and de-compress the archive. 
The build system for Stride uses the CMake tool. This is used to build and install the software at a high level of abstraction and almost platform independent (see \url{http://www.cmake.org/}). 
The project includes the conventional make targets to ``build'', ``install'', ``test'' and ``clean'' the project. There is one additional target ``configure'' to set up the CMake/make structure that will actually do all the work.
For those users that do not have a working knowledge of CMake, a front end Makefile has been provided that invokes the appropriate CMake commands.
More details on building the software can be found in ``INSTALL.txt'' in the source folder.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Documentation}
\label{section:documentation}

The Application Programmer Interface (API) documentation is generated automatically 
using the Doxygen tool ((see \url{www.doxygen.org}) from documentation instructions 
embedded in the code .

The user manual distributed with the source code has been written in \LaTeX (see \url{www.latex-project.org}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Directory layout}

The project directory structure is very systematic.
Everything used to build the software is stored in the directory \texttt{./src}:
\begin{compactitem}
    \item \texttt{src/main}: Code related files (sources, third party libraries and headers, ...)
      	\begin{itemize}
        		\item \texttt{src/main/<language>}: source code, per coding language: cpp (for C++), python, R,   
        		\item \texttt{src/main/resources}: third party resources included in the project: 
        \end{itemize}
    \item \texttt{src/doc}: documentation files (API, manual, ...)
      	\begin{itemize}
        		\item \texttt{src/doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
        		\item \texttt{src/doc/latex\_man}: files needed to generate the user manual with Latex
        \end{itemize}
    \item \texttt{src/test}: test related files (scripts, regression files, ...)
\end{compactitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% File formats
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{File formats}
\label{section:FileFormats}

The Stride software supports different file formats: 
\begin{description}
	\item [CSV] \ \\
	Comma separated values, used for population input data and simulator output.
	\item [HDF5] \ \\
	Hierarchical Data Format 5, designed to store and organize large amounts of data.
	\item [JSON] \ \\
	JavaScript Object Notation, an open standard format that uses human-readable text to transmit objects consisting of attribute-value pairs. 	 \mbox{(see \url{www.json.org})}
	\item [TXT] \ \\
	Text files, for the logger. 
	\item [XML] \ \\
	Extensible Markup Language, a markup language (both human-readable and machine-readable) that defines a set of rules for encoding documents.
    \item [Proto] \ \\
    Protocol Buffers, used for exporting and importing the generated population and geographical grid.
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Testing}
Unit tests and install checks are added to Stride based on Google's ``gtest" framework and CMake's ``ctest" tool. 
In addition, the code base contains assertions to verify the simulator logic. 
They are activated when the application is built in debug mode and can be used to catch errors at run time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{section:Results}

The software can generates different output files:
\begin{description}
	\item [cases.csv] \ \\
	Cumulative number of cases per day.
	\item [summary.csv] \ \\
	Aggregated results on the number of cases, configuration details and timings.
	\item [person.csv] \ \\
	Individual details on infection characteristics.
	\item [logfile.txt] \ \\
	Details on transmission and/or social contacts events.
    \item [gengeopop.proto] \ \\
    Generated population and geographical grid.
    \item [map.png] \ \\
    Image of the map shown in the MapViewer component.
    \item [calibration\_data.json] \ \\
    Results of the calibration component.
\end{description}

### 2018-06-19 doc/latex/03-Simulator.tex
Early version of an updated userManual

%%!TEX root = ./UserManual.tex
\chapter{Simulator}
\label{chap:simulator}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Workspace
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Workspace}

By default, Stride is installed in \texttt{./target/installed/} inside de project directory though this can be modified using the CMakeLocalConfig.txt file (example is given in \texttt{./src/main/resources/make}). 
Compilation and installation of the software will create the following files and directories:

\begin{compactitem}
    \item Binaries 
    		in directory \texttt{<project\_dir>/bin}
      	\begin{itemize}
        		\item $stride$: executable.
        		\item $gtester$: regression tests for the sequential code.
                \item $gengeopop$: generates the population and geographical grid.
                \item $guilauncher$: tool to edit a simulation configuration and execute it
                \item $mapviewer$: tool to visualize the population and geographical grid, can be directly used from $stride$ and $guilauncher$.
                \item $calibration$: tool to run the simulator multiple times to generate statistical data. This can be used to calibrate test outcomes.
        		\item $wrapper\_sim.py$: Python simulation wrapper  		
        \end{itemize}
    \item Configuration files (xml and json)
      	in directory \texttt{<project\_dir>/config}
      	\begin{itemize}
		\item $run\_default.xml$: default configuration file for Stride to perform a Nassau simulation.
        \item $run\_generate\_default.xml$: default configuration file for Stride to first generate a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_import\_default.xml$: default configuration file for Stride to first import a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_default.xml$: default configuration file for Stride to first generate several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_import.xml$: default configuration file for Stride to first import several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_miami\_weekend.xml$: configuration file for Stride to perform Miami simulations with uniform social contact rates in the community clusters.
		\item $wrapper\_miami.json$: default configuration file for the wrapper\_sim binary to perform Miami simulations with different attack rates.
        \item \ldots
        \end{itemize}
    \item Data files (csv)
      	in directory \texttt{<project\_dir>/data}
      	\begin{itemize}
        \item $belgium\_commuting$: Belgian commuting data for the active populations. The fraction of residents from ``city\_depart'' that are employed in ``city\_arrival''. Details are provided for all cities and for 13 major cities.
		\item $belgium\_population$: Relative Belgian population per city. Details are provided for all cities and for 13 major cities.
		\item $contact\_matrix\_average$: Social contact rates, given the cluster type. Community clusters have average (week/weekend) rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Community clusters have week rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Primary Community cluster has weekend rates, Secondary Community has week rates.
		\item $disease\_xxx$: Disease characteristics (incubation and infectious period) for xxx.
		\item $holidays\_xxx$: Holiday characteristics for xxx.
		\item $pop\_xxx$: Synthetic population data extracted from the 2010 U.S. Synthetic Population Database (Version 1) from RTI International for xxx \cite{wheaton2014a,wheaton2014b}. 
		\item $ref\_2011$: Reference data from EUROSTAT on the Belgian population of 2011. Population ages and household sizes.
		\item $ref\_fl2010\_xxx$: Reference data on social contacts for Belgium, 2011.

        \item $DE\_cities.csv$: German cities, fetched from \footnote{\url{}}.
        \item $FR\_cities.csv$: French cities, fetched from \footnote{\url{}}.
        \item $NL\_cities.csv$: Dutch cities, fetched from \footnote{\url{}}.
        \item $wallonia\_cities.csv$: Wallonia cities, fetched from \footnote{\url{}}.
        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{}}.
        \end{itemize}
    \item Documentation files
      	in directory \texttt{./target/installed/doc}
      	\begin{itemize}
        		\item Reference manual
        		\item User manual
        \end{itemize}
\end{compactitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Run
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Run the simulator}

From the workspace directory, the simulator can be started with default configuration using the command \mbox{``\texttt{./bin/stride}''}. Settings can be passed to the simulator using one or more command line arguments:

\begin{compactitem}

\item \texttt{-c} or \texttt{{-}-config}: The configuration file.

\item \texttt{-r} or \texttt{{-}-r0}: To obtain the basic reproduction number, no tertiary infections.

\end{compactitem}

\section{Generating a population and geographical grid}

From the workspace directory, the generation of a population and geographical grid (sometimes called GeoGrid) can be started with the default configuration using the command \mbox{``\texttt{./bin/gengeopop}''}. The following configuration options are available:

\begin{description}
    \item[\texttt{--populationSize}] \ \\ 
        The size of the population to generate. By default a population of \texttt{6000000} is generated.
    \item[\texttt{--fracActive}] \ \\
        The fraction of people who are active, i.e. who are employed or students. By default \tetttt{0.75} is used.
    \item[\texttt{--fracStudentCommuting}] \ \\
        The fraction of students commuting. By default \texttt{0.5} is used.
    \item[\texttt{--fracActiveCommuting}] \ \\
        The fraction of active people who commutes. By default \textt{0.5} is used.
    \item[\texttt{--frac1826Students}] \ \\
        The fraction of 1826 years which are students. By default \textt{0.5} is used.
    \item[\texttt{--household}] \ \\
        The file to read the household profiles from.
    \item[\texttt{--commuting}] \ \\
        The file to read the commuting information from.
    \item[\texttt{--cities}] \ \\
        The file to read the cities from.
    \item[\texttt{--subMinicipalities}] \ \\
        The file to read the sub-municipalities from.
    \item[\texttt{--output}] \ \\
        The file to write the GeoGrid to. By default this is \texttt{gengeopop.proto}
    \item[\texttt{--state}] \ \\
        The state to be used for initializing the random engine. This can be used to continue with the same state when generating multiple regions.
    \item[\texttt{--rng\_type}] \ \\
        The type of random engine to use by default \texttt{mrg2} is used. Available options are: \texttt{mrg2}, \textt{mrg3}, \textt{yarn2}, \texttt{yarn3}, \texttt{lgc64} and \texttt{lgc64\_shift}.
    \item[\texttt{--seed}] \ \\
        The seed to be used for the random engine. The default is \texttt{0}.
    \item[\texttt{--loglevel}] \ \\ 
        The loglevel to use, by default this is \texttt{info}.
\end{description}

\section{Using the MapViewer}

The MapViewer component can be used to explore a generated GeoGrid.
From the workspace directory, the MapViewer can be started by using \mbox{``\texttt{./bin/mapviewer}''}. No additional command line options are available.
To open a GeoGrid use the menu options \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
The circular markers indicate a city or sub-municipality. The square markers indicate the ``parent'' city of sub-municipalities, they don't have a population.
By clicking on the square marker, all the sub-municipalities will be selected.
When one ore more cities is selected the details are shown in the right sidebar. For example the ContactCenters are listed, when a ContactCenter is clicked, the ContactPools of the clicked ContactCenter will be shown.

Multiple cities can be selected by holding the control key and left mouse button and selecting a rectangle.

The visible area of a map can be exported to an image file using \texttt{File -> Export to image}.

% TODO continue

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sim Wrapper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Python Wrapper}
A Python wrapper is provided to perform multiple runs with the C++ executable. 
The wrapper is designed to be used with .json configuration files and examples are provided with the source code. 
For example: \\ \\
\centerline{\texttt{./bin/wrapper\_sim --config ./config/wrapper\_default.json}} \\ \\
will start the simulator with each configuration in the file.
It is important to note the input notation: values given inside brackets can be extended (e.g., ``rng\_seeds''=[1,2,3]) but single values can only be replaced by one other value (e.g., ``days'': 100).

### 2018-06-19 doc/latex/03-Simulator.tex
Update userManual

@@
     \item[\texttt{--fracActive}] \ \\
-        The fraction of people who are active, i.e. who are employed or students. By default \tetttt{0.75} is used.
+        The fraction of people who are active, i.e. who are employed or students. By default \texttt{0.75} is used.
     \item[\texttt{--fracStudentCommuting}] \ \\
@@
     \item[\texttt{--fracActiveCommuting}] \ \\
-        The fraction of active people who commutes. By default \textt{0.5} is used.
+        The fraction of active people who commutes. By default \texttt{0.5} is used.
     \item[\texttt{--frac1826Students}] \ \\
-        The fraction of 1826 years which are students. By default \textt{0.5} is used.
+        The fraction of 1826 years which are students. By default \texttt{0.5} is used.
     \item[\texttt{--household}] \ \\
@@
     \item[\texttt{--rng\_type}] \ \\
-        The type of random engine to use by default \texttt{mrg2} is used. Available options are: \texttt{mrg2}, \textt{mrg3}, \textt{yarn2}, \texttt{yarn3}, \texttt{lgc64} and \texttt{lgc64\_shift}.
+        The type of random engine to use by default \texttt{mrg2} is used.
+Available options are: \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2}, \texttt{yarn3}, \texttt{lgc64} and \texttt{lgc64\_shift}.
     \item[\texttt{--seed}] \ \\
@@
 From the workspace directory, the MapViewer can be started by using \mbox{``\texttt{./bin/mapviewer}''}. No additional command line options are available.
-To open a GeoGrid use the menu options \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
+To open a GeoGrid use the menu option \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
 The circular markers indicate a city or sub-municipality. The square markers indicate the ``parent'' city of sub-municipalities, they don't have a population.
@@
 When one ore more cities is selected the details are shown in the right sidebar.
-For example the ContactCenters are listed, when a ContactCenter is clicked, the ContactPools of the clicked ContactCenter will be shown.
-
-Multiple cities can be selected by holding the control key and left mouse button and selecting a rectangle.
-
+For example a list of ContacCenters in the current selected Location.
+When a ContactCenter is clicked, the ContactPools of the clicked ContactCenter will be shown.
+When holding the Ctrl key and clicking multiple markers all clicked markers will be selected.
+Multiple cities in a rectangle can be selected by holding the control key and left mouse button while dragging.
+Clicking on the map will deselect all cities.
+Hold the Alt key while panning the map to prevent deselection.
+Ctrl+ A can be used to select all cities, while Ctrl + F can be used to fit the viewport of the map so all cities are visible.
+To show commutes of a city, first enable the \texttt{View -> Show Commutes} option and then select a city.
+While simulating a blue marker indicates that no one is infected at that location.
+As soon as some people get infected the marker will become green, to eventually become red when more people are infected.
 The visible area of a map can be exported to an image file using \texttt{File -> Export to image}.
 
-% TODO continue
+When using the main Stride executable the mapviewer can be opened by passing the \texttt{-v} option.
+
+\section{Using the GuiLauncher}
+
+With the GuiLauncher component one can open a configuration file, change the parameters and then run the simulator.
+It's also possible to select which viewers to use (e.g.
+the MapViewer) and whether to use the GuiContrller (\ref{sec:guicontroller}).
+The changed configuration file can also be saved.
+
+From the workspace directory, the GuiLauncher can be started by using \mbox{``\texttt{./bin/mapviewer}''}. No additional command line options are available.
+The GuiLauncher should be straightforward to use.
+
+\section{Using the GuiController}
+\label{sec:guicontroller}
+
+The GuiController can be started when using the GuiLauncher. It makes it possible to control the simulation run.
+After clicking the ``Start`` button the simulation will start. The time between each simulated day can be changed by editing the value of the input field. The default is two seconds.
+It is also possible to advance the simulation multiple days, by choosing the amount of days and clicking the ``Multi-Step`` button.
+The ``Step`` button will always simulate one day.
+
+\section{Using the Calibrator}
+\label{sec:calibrator}
 

### 2018-06-19 doc/latex/04-Code-quality.tex
Extra file!

%%!TEX root = ./UserManual.tex
\chapter{Code quality}
\label{chap:code-quality}

To ensure good code quality all compiler warnings were fixed our in some rare cases suppressed. The following compilers should give no warnings:
\begin{compactitem}
    \item GCC 6.4.0 on Linux
    \item GCC 7.3.0 on Linux
    \item GCC 7.3.1 on Linux
    \item GCC 8.1.1 on Linux
    \item Clang 5.0.0 on Linux
    \item Clang 5.0.1 on Linux
    \item Clang 5.0.2 on Linux
    \item Clang 6.0.0 on Linux
    \item AppleClang 8.1.0 on Darwin-16.7.0
    \item AppleClang 9.0.0 on Darwin-16.7.0
    \item AppleClang 9.1.0 on Darwin-17.4.0
\end{compactitem}

Clang-format was used to ensure a consistent code-style throughout the project. The used clang-format is 5.0.1.

The GUI's were manually tested on a macOS High Sierra system. We noticed that on one system, out of our control, an extra titlebar appeared. We were unable to reproduce this.
The used Qt version is

### 2018-06-19 main/cpp/mapviewer/backend.cpp
Fix + better colors

@@ -183,7 +183,7 @@ void Backend::ClearSelectionAndRender()
 {
         for (std::pair<int, int> locIDs : m_selection) {
                 auto* marker = m_markers[locIDs];
-                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "purple"));
+                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "#5d00ff"));
         }
         for (const auto& locIDs : m_unselection) {
                 auto* marker = m_markers[locIDs];
@@ -288,7 +288,7 @@ void Backend::UpdateColorOfMarkers()
         m_unselection.clear();
         for (const auto& locID : m_selection) {
                 auto* marker = m_markers[locID];
-                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "purple"));
+                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "#5d00ff"));
                 // Show the commutes
                 auto loc = GetLocationInRegion(locID);
                 if (m_showCommutes) {
@@ -417,14 +417,14 @@ void Backend::OnMarkerHovered(int region, unsigned int idOfHover)
 
         if (m_selection.find({region, idOfHover}) == m_selection.end()) {
                 QObject* marker = m_markers[{region, loc->GetID()}];
-                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "blue"));
+                QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection, Q_ARG(QVariant, "#FFFFFF"));
 
                 // Change colors of submunicipalities
                 const std::set<std::shared_ptr<gengeopop::Location>> sub = loc->GetSubMunicipalities();
                 for (const auto& mun : sub) {
                         QObject* markerMun = m_markers[{region, mun->GetID()}];
                         QMetaObject::invokeMethod(markerMun, "setBorder", Qt::DirectConnection,
-                                                  Q_ARG(QVariant, "blue"));
+                                                  Q_ARG(QVariant, "#FFFFFF"));
                 }
         }
 }
@@ -447,7 +447,7 @@ void Backend::OnMarkerHoveredOff(int region, unsigned int idOfHover)
                         } else {
                                 // Back to selection color
                                 QMetaObject::invokeMethod(marker, "setBorder", Qt::DirectConnection,
[…]

### 2018-06-19 main/cpp/mapviewer/backend.h

@@ -116,6 +116,14 @@ public:
          */
         void SaveGeoGridToFile(const QString& fileLoc, QObject* errorDialog);
 
+        Q_INVOKABLE
+        /**
+         * Saves the CustomMarker QObject of a specific location so we can modify it later.
+         * @param region the region of the location
+         * @param id the id of the location
+         */
+        void SaveMarker(int region, int id, QObject* marker);
+
 signals:
         /// Emits the locations that are selected. Other components can connect to this to be notified.
         void LocationsSelected(std::set<std::shared_ptr<gengeopop::Location>> locations);
@@ -156,15 +164,6 @@ private:
          * Removes all locations from selection and unselection + re-render the map.
          */
         void ClearSelectionAndRender();
-
-        Q_INVOKABLE
-        /**
-         * Saves the CustomMarker QObject of a specific location so we can modify it later.
-         * @param region the region of the location
-         * @param id the id of the location
-         */
-        void SaveMarker(int region, int id, QObject* marker);
-
         /**
          * Update colors of Markers based on the value of m_selection and m_unselection.
          * Won't loop over every marker or location.

### 2018-06-19 doc/latex/03-Simulator.tex
Add Calibrator doc

@@
 
+The Calibrator is a tool designed to calibrate the scenario tests.
+It can also be used for running a simulation multiple times to gather statistical data.
+This data can then be written to a file or be used for generating boxplots.
+The following configuration options are available:
+
+\begin{description}
+    \item[\texttt{--config}] \ \\
+        Specifies the run configuration parameters to be used for the simulation.
+        If this is provided multiple times, the calibration is performed on all given simulations.
+        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
+        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
+    \item[\texttt{--testcases}] \ \\
+        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
+        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
+    \item[\texttt{--multiple}]\ \\
+        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
+    \item[\texttt{--single}]\ \\
+        Run the simulations with the fixed seeds to determine the exact values.
+    \item[\texttt{--output}]\ \\
+        Write the results of the calibration to a file with given filename. This resulting file contains ...
+    \item[\texttt{--write}]\ \\
+        Write boxplots to files in the current directory. This creates an image for each config or testcase.
+    \item[\texttt{--display}]\ \\
+        Display the boxplots for the last step.
+    \item[\texttt{--displayStep}]\ \\
+        Display the boxplots for a specified step.
+\end{description}
+
+Examples:\\
+To find the exact values for the testcases and write these to a file:\\
+
+\centerline{\texttt{calibration -s -o out.json}}
+
+To run a configuration file 10 times with a random seed and display the generated boxplot for the last step in the simulation:\\
+
+\centerline{\texttt{calibration -c run\_default.xml -m 10 -d}}
+
+To run the testcase \texttt{influenza\_a} 10 times, write the results to a file and for each step in the simulation write a boxplot to a file:\\
+
+\centerline{\texttt{calibration -t influenza\_a -m 10 -w -o out.json}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-06-19 doxygen/d0/d2f/a00259.js
Update doxygen for f62d9dfe153c8cac8678fd589b17a0af2114ae8c

@@ -1,4 +1,0 @@
-var a00259 =
-[
-    [ "ExcAssert", "d0/d2f/a00259.html#a53951f1917941ac25ba6508b1b72771f", null ]
-];

### 2018-06-19 doxygen/d0/d48/a00351.js

@@ -1,4 +1,4 @@
 var a00351 =
 [
-    [ "main", "d0/d48/a00351.html#a3c04138a5bfe5d72780bb7e82a18e627", null ]
+    [ "main", "d0/d48/a00351.html#a0ddf1224851353fc92bfbff6f499fa97", null ]
 ];

### 2018-06-19 doxygen/d0/d4a/a00147.js

@@ -1,8 +1,7 @@
 var a00147 =
 [
-    [ "TravellerProfileBuilder", "d0/d4a/a00147.html#a92a979fcc9126020bb317ea37d26296f", null ],
-    [ "Build", "d0/d4a/a00147.html#a054950caec73fe87d50736d61377d182", null ],
-    [ "m_configPt", "d0/d4a/a00147.html#a3f7685d5081a50a71241c36279c02858", null ],
-    [ "m_rnManager", "d0/d4a/a00147.html#aad912ff7f64511bae926e1eb87cfe946", null ],
-    [ "m_pop", "d0/d4a/a00147.html#ae183a7f7ec1e3f6a1ee8b1a9e1e41f49", null ]
+    [ "TransmissionProfile", "d0/d4a/a00147.html#a1645757a571f63d0583d54a6838ca1fb", null ],
+    [ "GetRate", "d0/d4a/a00147.html#a51ffe104253ffd5bcf12ab299fa6f2e2", null ],
+    [ "Initialize", "d0/d4a/a00147.html#a5e67e9eab813de18fff32722ee6f1437", null ],
+    [ "m_transmission_rate", "d0/d4a/a00147.html#afbb8227d4d8b61b291fa521f33dce3ce", null ]
 ];

### 2018-06-19 doxygen/d1/d0b/a00452.js

@@ -1,4 +1,0 @@
-var a00452 =
-[
-    [ "KdTree2DPoint", "dc/d87/a00032.html", "dc/d87/a00032" ]
-];

### 2018-06-19 doxygen/d1/d92/a00475.js

@@ -1,0 +1,4 @@
+var a00475 =
+[
+    [ "Subject", "de/d14/a00139.html", "de/d14/a00139" ]
+];

### 2018-06-19 doxygen/d1/db7/a00157.js

@@ -1,23 +1,20 @@
 var a00157 =
 [
-    [ "Info", "d6/db8/a00158.html", "d6/db8/a00158" ],
-    [ "RNManager", "d1/db7/a00157.html#a30121f0f47cf4c23bed8da7521b2b904", null ],
-    [ "RNManager", "d1/db7/a00157.html#a09c7ac5ae3b2ecffe9ee9b373d035e57", null ],
-    [ "RNManager", "d1/db7/a00157.html#a9bd2ac6bfbf177b216ce9cfff0626a0f", null ],
-    [ "operator=", "d1/db7/a00157.html#a546d57ebd3d79450abc641b3ebe5d23c", null ],
-    [ "operator=", "d1/db7/a00157.html#a6b35b013e3ee4263df703ee01745ea3f", null ],
-    [ "GetInfo", "d1/db7/a00157.html#a3faf18a9fdd2400012612a2cafde01a3", null ],
-    [ "GetGenerator", "d1/db7/a00157.html#a6508932485d419a6e7ab3cac60754ae6", null ],
-    [ "RandomShuffle", "d1/db7/a00157.html#a5a7dc58c76f112c8d808866cac5a272d", null ],
-    [ "Initialize", "d1/db7/a00157.html#a8c78f40f38b8a3fc25e2c21be2de505a", null ],
-    [ "Initialize", "d1/db7/a00157.html#a49618df845ec996f3a777263c7f376de", null ],
-    [ "m_seed", "d1/db7/a00157.html#af9b36fdeadaea938995a293c940b90a4", null ],
-    [ "m_stream_count", "d1/db7/a00157.html#a56d4de95212dccdd02652c477673297c", null ],
-    [ "m_type_id", "d1/db7/a00157.html#a74b3b62e58d9dc935287af1f403e3a88", null ],
-    [ "m_lcg64", "d1/db7/a00157.html#a138adbebf56ee6aff14f4a5d657eb582", null ],
-    [ "m_lcg64_shift", "d1/db7/a00157.html#a47e49d570a9cef2fee04ef084c93e09a", null ],
-    [ "m_mrg2", "d1/db7/a00157.html#aef24d7bf005b199b20bbc26111bac570", null ],
-    [ "m_mrg3", "d1/db7/a00157.html#a03cc6bedd665abb75073633f6bef0a73", null ],
[…]

### 2018-06-19 doxygen/d2/d9d/a00464.js

@@ -1,0 +1,10 @@
+var a00464 =
+[
+    [ "GeoGrid_Location_Coordinate", "da/d2a/a00086.html", "da/d2a/a00086" ],
+    [ "GeoGrid_Location_ContactCenter_ContactPool", "df/d13/a00085.html", "df/d13/a00085" ],
+    [ "GeoGrid_Location_ContactCenter", "df/d5d/a00084.html", "df/d5d/a00084" ],
+    [ "GeoGrid_Location_Commute", "d2/d1f/a00083.html", "d2/d1f/a00083" ],
+    [ "GeoGrid_Location", "d4/d63/a00082.html", "d4/d63/a00082" ],
+    [ "GeoGrid_Person", "d1/d1e/a00087.html", "d1/d1e/a00087" ],
+    [ "GeoGrid", "d8/d53/a00081.html", "d8/d53/a00081" ]
+];

### 2018-06-19 doxygen/d2/dc8/a00242.js

@@ -1,0 +1,12 @@
+var a00242 =
+[
+    [ "Id", "d2/dc8/a00242.html#a8f1467c1f622638893d3a1c12eead2ba", [
+      [ "None", "d2/dc8/a00242.html#a8f1467c1f622638893d3a1c12eead2baa6adf97f83acf6453d4a6a4b1070f3754", null ],
+      [ "Transmissions", "d2/dc8/a00242.html#a8f1467c1f622638893d3a1c12eead2baa6d688add062a0c9e2d77cbb1e7594ae5", null ],
+      [ "All", "d2/dc8/a00242.html#a8f1467c1f622638893d3a1c12eead2baab1c94ca2fbc3e78fc30069c8d0f01680", null ],
+      [ "Susceptibles", "d2/dc8/a00242.html#a8f1467c1f622638893d3a1c12eead2baa5006b319d87706ec01a6e59c64a1433c", null ]
+    ] ],
+    [ "ToString", "d2/dc8/a00242.html#a025f9ff3cf2df8c0c8b95e48724d9b7c", null ],
+    [ "IsMode", "d2/dc8/a00242.html#a3242678fd1548cd6dd420490dc06fcff", null ],
+    [ "ToMode", "d2/dc8/a00242.html#a12707c23b43baa1a0f5bed51db72756d", null ]
+];

### 2018-06-19 doxygen/d3/d45/a00382.js

@@ -1,6 +1,6 @@
 var a00382 =
 [
-    [ "IsType", "d3/d45/a00382.html#a0d22d904ddff0d21494405335e5fc744", null ],
-    [ "ToString", "d3/d45/a00382.html#a120e2ae5e703cd5a7e1859a1c83ddcec", null ],
-    [ "ToType", "d3/d45/a00382.html#a58e0a5f256c9b615c606f90dabec96b2", null ]
+    [ "RangeIndexer", "da/d82/a00091.html", "da/d82/a00091" ],
+    [ "RangeIndexer< T, std::size_t >", "de/d38/a00160.html", "de/d38/a00160" ],
+    [ "make_range_indexer", "d3/d45/a00382.html#a4f10665aadf9707b6524fa2b3e159004", null ]
 ];

### 2018-06-19 doxygen/d3/d4a/a00297.js

@@ -1,8 +1,0 @@
-var a00297 =
-[
-    [ "HBM", "db/d57/a00112.html", "db/d57/a00112" ],
-    [ "VariableState", "d3/d4a/a00297.html#a9d01e8d18496c1065ce04a29ec8b3470", [
-      [ "Low", "d3/d4a/a00297.html#a9d01e8d18496c1065ce04a29ec8b3470a28d0edd045e05cf5af64e35ae0c4c6ef", null ],
-      [ "High", "d3/d4a/a00297.html#a9d01e8d18496c1065ce04a29ec8b3470a655d20c1ca69519ca647684edbb2db35", null ]
-    ] ]
-];

### 2018-06-19 doxygen/d3/d93/a00341.js

@@ -1,5 +1,0 @@
-var a00341 =
-[
-    [ "Location", "d4/d6d/a00055.html", "d4/d6d/a00055" ],
-    [ "Coordinate", "d3/d93/a00341.html#a787d85bc4a485c85bc62824e3434b953", null ]
-];

### 2018-06-19 doxygen/d4/d08/a00237.js

@@ -1,5 +1,0 @@
-var a00237 =
-[
-    [ "ToString", "d4/d08/a00237.html#a025f9ff3cf2df8c0c8b95e48724d9b7c", null ],
-    [ "ToMode", "d4/d08/a00237.html#a12707c23b43baa1a0f5bed51db72756d", null ]
-];

### 2018-06-19 doxygen/d4/d4b/a00471.js

@@ -1,9 +1,0 @@
-var a00471 =
-[
-    [ "MapViewer", "d5/dcb/a00170.html", "d5/dcb/a00170" ],
-    [ "AdoptedViewer", "dc/de6/a00167.html", "dc/de6/a00167" ],
-    [ "CliViewer", "dd/da7/a00168.html", "dd/da7/a00168" ],
-    [ "InfectedViewer", "de/d53/a00169.html", "de/d53/a00169" ],
-    [ "PersonsViewer", "d1/d0d/a00171.html", "d1/d0d/a00171" ],
-    [ "SummaryViewer", "d6/dfb/a00172.html", "d6/dfb/a00172" ]
-];

### 2018-06-19 doxygen/d4/d81/a00110.js

@@ -1,4 +1,8 @@
 var a00110 =
 [
-    [ "Build", "d4/d81/a00110.html#a1a9f0c9424522454bc5f99419734993c", null ]
+    [ "DiseaseSeeder", "d4/d81/a00110.html#a47b0a54271fcce196ed8546690563c4c", null ],
+    [ "Seed", "d4/d81/a00110.html#adc5b1f152367382afe3dade9421357da", null ],
+    [ "Vaccinate", "d4/d81/a00110.html#accb4b7832c08a4cc98973caf5aebf7f5", null ],
+    [ "m_config_pt", "d4/d81/a00110.html#a564d8b1346c1160f4e68f3ab8ad0bf8a", null ],
+    [ "m_rn_manager", "d4/d81/a00110.html#afd5a1be8a601cb5f5d07ee0a12a10547", null ]
 ];

### 2018-06-19 doxygen/d4/db5/a00328.js

@@ -1,4 +1,0 @@
-var a00328 =
-[
-    [ "InfectorExec", "d4/db5/a00328.html#a635bb1de3d0d033b13e5ea468dfdd0bb", null ]
-];

### 2018-06-19 doxygen/d5/dcb/a00170.js

@@ -1,10 +1,5 @@
 var a00170 =
 [
-    [ "MapViewer", "d5/dcb/a00170.html#a354bb93b86fe6ab7d88188f3e66cc8e8", null ],
-    [ "~MapViewer", "d5/dcb/a00170.html#a347ee82efaa83090012fa331c855285a", null ],
-    [ "Update", "d5/dcb/a00170.html#a682fd168e97785d7342bc192baeac078", null ],
-    [ "m_logger", "d5/dcb/a00170.html#a7899a4938e50547e1b14e387255c290a", null ],
-    [ "m_first", "d5/dcb/a00170.html#ac76efad12d02ce9ee9f0b8487ff726ec", null ],
-    [ "m_vis", "d5/dcb/a00170.html#a611730b84751ab3a6fbf48ff64e7a8c5", null ],
-    [ "m_runner", "d5/dcb/a00170.html#a086e9f45a7652dbbb2f2b63a790f41d7", null ]
+    [ "PracticesSocialDistancing", "d5/dcb/a00170.html#a8dcb01be7e194bb29d6a379322781a14", null ],
+    [ "PracticesVaccination", "d5/dcb/a00170.html#a4db3031aaeba5b0de11bd821ece9adbe", null ]
 ];

### 2018-06-19 doxygen/d7/d06/a00131.js

@@ -1,4 +1,4 @@
 var a00131 =
 [
-    [ "Update", "d7/d06/a00131.html#a02b2e25dbfe3b1a6aa498c415029b81a", null ]
+    [ "Update", "d7/d06/a00131.html#ae8df514c2c3f876dc620c2423091967c", null ]
 ];

### 2018-06-19 doxygen/d7/d70/a00106.js

@@ -1,7 +1,6 @@
 var a00106 =
 [
-    [ "DaysOffSchool", "d7/d70/a00106.html#ab77c78d8d9b00fe50c8f845fe459a657", null ],
-    [ "IsWorkOff", "d7/d70/a00106.html#a633453bbe4892b56891c42a4f4ac72fd", null ],
-    [ "IsSchoolOff", "d7/d70/a00106.html#a709acf6d0cec5722e20760a797ae35bb", null ],
-    [ "m_calendar", "d7/d70/a00106.html#a5ac5b045ac4db6ae397d91d7dd663784", null ]
+    [ "DaysOffNone", "d7/d70/a00106.html#a14d76fd72838aa5d10c53b0115d1ff3a", null ],
+    [ "IsWorkOff", "d7/d70/a00106.html#a6287fa68ca109373fc9be31f3941079d", null ],
+    [ "IsSchoolOff", "d7/d70/a00106.html#a939df1a48d594f56ec3099d1edcfdca7", null ]
 ];

### 2018-06-19 doxygen/d7/d9a/a00152.js

@@ -1,4 +1,12 @@
 var a00152 =
 [
-    [ "Exception", "d7/d9a/a00152.html#afa3f2f4a87be564f7f77fbc8cb64bfe1", null ]
+    [ "Any", "d7/d9a/a00152.html#a78136d1eb13e5df0bd7f8043adff152a", null ],
+    [ "Any", "d7/d9a/a00152.html#aa37a30a7324377f7afe3b614d3c8f1eb", null ],
+    [ "operator=", "d7/d9a/a00152.html#ad1330eaf1df07a82065354e88a87a6fd", null ],
+    [ "operator=", "d7/d9a/a00152.html#aac5387b1910deeba0f0fb319c8a6e710", null ],
+    [ "emplace", "d7/d9a/a00152.html#a8aee74d02cb317ad6a8212f9a84c9254", null ],
+    [ "cast", "d7/d9a/a00152.html#a25363f8f215051caae46e3094da0bff8", null ],
+    [ "operator bool", "d7/d9a/a00152.html#a60543e81cc55aee3d0a2d8e02779825b", null ],
+    [ "m_ptr", "d7/d9a/a00152.html#a581dd8c8a98e7470e351687980a7f41d", null ],
+    [ "m_destroy", "d7/d9a/a00152.html#a43e14abfb952e01348cb11cb50649daf", null ]
 ];

### 2018-06-19 doxygen/d8/d17/a00114.js

@@ -1,11 +1,28 @@
 var a00114 =
 [
-    [ "HealthSeeder", "d8/d17/a00114.html#a7b4785c0728c9f154aa1426034d6e1b5", null ],
-    [ "Seed", "d8/d17/a00114.html#ad6a9061857cee5335745fe5501bcb73d", null ],
-    [ "GetDistribution", "d8/d17/a00114.html#a7b240a326b204767217481b3fcc46237", null ],
-    [ "Sample", "d8/d17/a00114.html#a562b022d2c7f2836b4400e7d19e1b040", null ],
-    [ "m_distrib_start_infectiousness", "d8/d17/a00114.html#a2933ce9d9b3e17d11edb4d50bc005a1a", null ],
-    [ "m_distrib_start_symptomatic", "d8/d17/a00114.html#a09f22ca66e79edf806a249517ec6ac35", null ],
-    [ "m_distrib_time_infectious", "d8/d17/a00114.html#a520743c093005b7ccda658475107f0c2", null ],
-    [ "m_distrib_time_symptomatic", "d8/d17/a00114.html#a6d190e53a3a83864d7a40cb78b2188e4", null ]
+    [ "Health", "d8/d17/a00114.html#a29ca39e47180884b3c7681636d1c550d", null ],
+    [ "GetEndInfectiousness", "d8/d17/a00114.html#a8e8b3c6fe823b70820f868bb597ade73", null ],
+    [ "GetEndSymptomatic", "d8/d17/a00114.html#aac2a22ae31603c4dbaea3f440974d0d5", null ],
+    [ "GetStartInfectiousness", "d8/d17/a00114.html#a9eab117bce0fe7009188aad7e534ca82", null ],
+    [ "GetStartSymptomatic", "d8/d17/a00114.html#adf2c4f06cd9ad0dac95c5a2ffdd39489", null ],
+    [ "IsImmune", "d8/d17/a00114.html#a7c9caae07db1dd15732f726cec514dc2", null ],
+    [ "IsInfected", "d8/d17/a00114.html#aa54f0be8ce25462aaf62847ded75a29d", null ],
+    [ "IsInfectious", "d8/d17/a00114.html#a84c0cb686c22ec8504942b84105eaed2", null ],
+    [ "IsRecovered", "d8/d17/a00114.html#a4dae2bfe69375adb5dd89819f6798090", null ],
[…]

### 2018-06-19 doxygen/db/d10/a00350.js

@@ -1,4 +1,0 @@
-var a00350 =
-[
-    [ "main", "db/d10/a00350.html#a81ce304348a420752ee080480d2b3095", null ]
-];

### 2018-06-19 doxygen/db/db1/a00460.js

@@ -1,0 +1,5 @@
+var a00460 =
+[
+    [ "BaseNode", "d7/d46/a00002.html", "d7/d46/a00002" ],
+    [ "Node", "dc/dee/a00053.html", "dc/dee/a00053" ]
+];

### 2018-06-19 doxygen/db/dd9/a00179.js

@@ -1,6 +1,0 @@
-var a00179 =
-[
-    [ "MaximumAge", "db/dd9/a00179.html#ae2682ff4058ec78d0809d073dcdea2d1", null ],
-    [ "MinAdultAge", "db/dd9/a00179.html#a2b354a18a7f6986d363385ff46c9a473", null ],
-    [ "EffectiveAge", "db/dd9/a00179.html#abe2f1ef509d97ae6c13bdcd187e495f2", null ]
-];

### 2018-06-19 doxygen/dc/dc9/a00389.js

@@ -1,0 +1,6 @@
+var a00389 =
+[
+    [ "para_info", "dc/dc9/a00389.html#a1437dc582cd8fb70c6873c692adde468", null ],
+    [ "para_seed", "dc/dc9/a00389.html#a0c42ba6e336bed67e5a0bdd053802c2a", null ],
+    [ "para_seed", "dc/dc9/a00389.html#a3457bcd24475b5a21953b08e7137736d", null ]
+];

### 2018-06-19 doxygen/dc/de6/a00167.js

@@ -1,8 +1,29 @@
 var a00167 =
 [
-    [ "AdoptedViewer", "dc/de6/a00167.html#ab738a150c36440e77462aa81e7c61542", null ],
-    [ "Update", "dc/de6/a00167.html#ac36ba5df119a6774611d57cbc47657f1", null ],
-    [ "m_adopted", "dc/de6/a00167.html#a174d3d560614d28923c90dfe9ce23d1b", null ],
-    [ "m_adopted_file", "dc/de6/a00167.html#a7de96aa3b18fbd439033e4ac4a51e806", null ],
-    [ "m_runner", "dc/de6/a00167.html#ae6a20e953d090b14fb0a093a3b04d408", null ]
+    [ "self_type", "dc/de6/a00167.html#acf4391226c3334af2ab02fdbfcbe81c8", null ],
+    [ "container_pointer_type", "dc/de6/a00167.html#a385306acf359ed5cfa28a7e2921d417d", null ],
+    [ "SVIterator", "dc/de6/a00167.html#a314396936e46da86a1da0cc811225e27", null ],
+    [ "SVIterator", "dc/de6/a00167.html#ab481d9aa2bf4f1dd132a36fe2554be28", null ],
+    [ "SVIterator", "dc/de6/a00167.html#ac34d8cbf117630096864be24e5f3bca0", null ],
+    [ "operator*", "dc/de6/a00167.html#a7e3d418c40d965c28ed4b8370a9967e9", null ],
+    [ "operator->", "dc/de6/a00167.html#aa10e3ead890dc5f0dda7bd7d53474927", null ],
+    [ "operator++", "dc/de6/a00167.html#a764a61e4157323eeca43fa49de3a9e1a", null ],
+    [ "operator++", "dc/de6/a00167.html#a0d723c151c2ea9c4366875ecf4a90cc9", null ],
+    [ "operator--", "dc/de6/a00167.html#aee9c16d0cf1e70f153e2e74cec5f4c13", null ],
+    [ "operator--", "dc/de6/a00167.html#ae03ac9839333631874a218227eeb6ec9", null ],
+    [ "operator==", "dc/de6/a00167.html#af73d0024aef3eeb58f338806fb46d4b1", null ],
+    [ "operator!=", "dc/de6/a00167.html#ad1105a1f1358d5e88868a49bf4c2e34b", null ],
[…]

### 2018-06-19 doxygen/dc/ded/a00252.js

@@ -1,0 +1,6 @@
+var a00252 =
+[
+    [ "CSVRow::GetValue< std::string >", "dc/ded/a00252.html#a9dce01f32b092253d815beac1cd52010", null ],
+    [ "CSVRow::GetValue< std::string >", "dc/ded/a00252.html#a7c45b2cf6c75aee55004e27edb10e745", null ],
+    [ "operator<<", "dc/ded/a00252.html#abecfc8507900bdeb7a71e664c111b0be", null ]
+];

### 2018-06-19 doxygen/dd/d56/a00274.js

@@ -1,0 +1,8 @@
+var a00274 =
+[
+    [ "GeoAggregator", "dc/d3c/a00028.html", null ],
+    [ "KdTree2DPoint", "dc/d87/a00032.html", "dc/d87/a00032" ],
+    [ "dimension_type", "d0/dc0/a00033.html", "d0/dc0/a00033" ],
+    [ "GeoGrid", "df/d61/a00031.html", "df/d61/a00031" ],
+    [ "BoostPoint", "dd/d56/a00274.html#a7a3cba9aa788599b9ff36152b6bca624", null ]
+];

### 2018-06-19 doxygen/dd/d86/a00271.js

@@ -1,52 +1,0 @@
-var a00271 =
-[
-    [ "TableStruct", "db/ddf/a00088.html", "db/ddf/a00088" ],
-    [ "GeoGrid_Location_Coordinate", "da/d2a/a00086.html", "da/d2a/a00086" ],
-    [ "GeoGrid_Location_ContactCenter_ContactPool", "df/d13/a00085.html", "df/d13/a00085" ],
-    [ "GeoGrid_Location_ContactCenter", "df/d5d/a00084.html", "df/d5d/a00084" ],
-    [ "GeoGrid_Location_Commute", "d2/d1f/a00083.html", "d2/d1f/a00083" ],
-    [ "GeoGrid_Location", "d4/d63/a00082.html", "d4/d63/a00082" ],
-    [ "GeoGrid_Person", "d1/d1e/a00087.html", "d1/d1e/a00087" ],
-    [ "GeoGrid", "d8/d53/a00081.html", "d8/d53/a00081" ],
-    [ "is_proto_enum< ::proto::GeoGrid_Location_ContactCenter_Type >", "db/db6/a00074.html", null ],
-    [ "GeoGrid_Location_ContactCenter_Type", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8b", [
-      [ "GeoGrid_Location_ContactCenter_Type_K12School", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8baad3ada6021a90153f0fe7d23c4961b8c", null ],
-      [ "GeoGrid_Location_ContactCenter_Type_Community", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8baad239fb07a61835e8b6f34eaf04913de", null ],
-      [ "GeoGrid_Location_ContactCenter_Type_PrimaryCommunity", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8baca568431921aa96c039bfcb4f6787b4c", null ],
-      [ "GeoGrid_Location_ContactCenter_Type_SecondaryCommunity", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8bad068b29dc49070b52a4123c4afed3f73", null ],
-      [ "GeoGrid_Location_ContactCenter_Type_College", "dd/d86/a00271.html#a87e31302cbdcd5134821ad9ae876ed8ba515eed7ba2015e006e9543976a0f1bfa", null ],
[…]

### 2018-06-19 doxygen/dd/db3/a00313.js

@@ -1,15 +1,0 @@
-var a00313 =
-[
-    [ "Id", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836", [
-      [ "AtStart", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836afcf908843999113ed917adfa7d3582fe", null ],
-      [ "Stepped", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836a5ea38ba255e963326e6dbe47d8be6568", null ],
-      [ "Finished", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836a8f3d10eb21bd36347c258679eba9e92b", null ],
-      [ "SetupBegin", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836ac5be476a42d4abe754e94797ccc012ac", null ],
-      [ "SetupEnd", "dd/db3/a00313.html#ab046b05654e26ef19fd5e4e46c16e836a6e3d315343f8cb5b914a65acb273e7fe", null ]
-    ] ],
-    [ "NumOfTypes", "dd/db3/a00313.html#afd464f4ca1769b7880cb27383a3cafd2", null ],
-    [ "IsType", "dd/db3/a00313.html#a43c0310b3eef6024b540ffaa5c4c39b2", null ],
-    [ "ToSizeT", "dd/db3/a00313.html#acdde1acea1c3f4536af74bb4b126a739", null ],
-    [ "ToString", "dd/db3/a00313.html#aaa54357f0c5b3af4e7905ed503167ede", null ],
-    [ "ToType", "dd/db3/a00313.html#ac81b85da174b73232cac26f53bd6d3a0", null ]
-];

### 2018-06-19 doxygen/dd/dd7/a00248.js

@@ -1,6 +1,6 @@
 var a00248 =
 [
-    [ "CSVRow::GetValue< std::string >", "dd/dd7/a00248.html#a9dce01f32b092253d815beac1cd52010", null ],
-    [ "CSVRow::GetValue< std::string >", "dd/dd7/a00248.html#a7c45b2cf6c75aee55004e27edb10e745", null ],
-    [ "operator<<", "dd/dd7/a00248.html#abecfc8507900bdeb7a71e664c111b0be", null ]
+    [ "IsType", "dd/dd7/a00248.html#a1269217f56908f0da981dbe4e43bb73d", null ],
+    [ "ToString", "dd/dd7/a00248.html#a0cf9d3425b406cd76acdc02ef9c0286d", null ],
+    [ "ToType", "dd/dd7/a00248.html#af529300a78547c29c95b81ad8ac62afe", null ]
 ];

### 2018-06-19 doxygen/de/d14/a00139.js

@@ -1,25 +1,10 @@
 var a00139 =
 [
-    [ "Sim", "de/d14/a00139.html#a8fe8e4385431342099c66352104c5595", null ],
-    [ "Create", "de/d14/a00139.html#a5631d8dd270e27d496028cede8e799b9", null ],
-    [ "Create", "de/d14/a00139.html#a4e34f4dd075411598c9cb45d250e6e73", null ],
-    [ "GetCalendar", "de/d14/a00139.html#afea0f1297e849966883bcc1d8e3d8e86", null ],
-    [ "GetTransmissionProfile", "de/d14/a00139.html#a59f0ea739583f91283738089112a08dc", null ],
-    [ "GetPopulation", "de/d14/a00139.html#ae0d62bc95008a4974dd9227b5084e161", null ],
-    [ "GetRNManager", "de/d14/a00139.html#a678c64e042d050ed6bf8e1a7cc0effa7", null ],
-    [ "TimeStep", "de/d14/a00139.html#a032911d7270c91e0a6a9c55f68800096", null ],
-    [ "SimBuilder", "de/d14/a00139.html#a9a439036c5f4a413765b48764c0b1741", null ],
-    [ "m_config_pt", "de/d14/a00139.html#ac0f1837c346b11b4cea734b6769b8d1d", null ],
-    [ "m_contact_log_mode", "de/d14/a00139.html#af58f9eda3c97affca6acbfde33bc68c0", null ],
-    [ "m_num_threads", "de/d14/a00139.html#a6ea31f057cd8b04a29439301a786790f", null ],
-    [ "m_track_index_case", "de/d14/a00139.html#a4d51a48a2354c6c138552edbfaf57870", null ],
-    [ "m_local_info_policy", "de/d14/a00139.html#a553cd031e42186d3ddca16001871c8da", null ],
-    [ "m_calendar", "de/d14/a00139.html#af238badc880ea1db8dba6be4272f957c", null ],
-    [ "m_contact_profiles", "de/d14/a00139.html#a9fd4ab1a0802a5b855efa4bf2b5a8e08", null ],
-    [ "m_handlers", "de/d14/a00139.html#aa32eb53f04209e58c93b25d8c6c24a40", null ],
-    [ "m_infector", "de/d14/a00139.html#a36d96f3112de535bd8a48b8694545212", null ],
[…]

### 2018-06-19 doxygen/de/d53/a00169.js

@@ -1,9 +1,8 @@
 var a00169 =
 [
-    [ "InfectedViewer", "de/d53/a00169.html#aae44b0fd20d9193b61d065d08e57e8f3", null ],
-    [ "GetInfectionCounts", "de/d53/a00169.html#a0a02401197ff8238052068ecaa10c505", null ],
-    [ "Update", "de/d53/a00169.html#ac539c7549cc8c19530813f0bdb35a14d", null ],
-    [ "m_infected", "de/d53/a00169.html#a613860070a4a0778c61631fc4f343028", null ],
-    [ "m_infected_file", "de/d53/a00169.html#abf3638fe4dad03b5adb58b56ebd8a926", null ],
-    [ "m_runner", "de/d53/a00169.html#a13b27fd1d407a15fe3b542952168ba33", null ]
+    [ "ToColonString", "de/d53/a00169.html#ad6dcc9ca1dfee4746a739175240585ce", null ],
+    [ "ToColonString", "de/d53/a00169.html#a4289b5e11499452e2d8257c7c4bf1393", null ],
+    [ "ToColonString", "de/d53/a00169.html#a75cf053eac30cd061369b1b3bc8320e2", null ],
+    [ "ToColonString", "de/d53/a00169.html#a3257445eaf8975e71bd08d8ed6d8dad8", null ],
+    [ "ToColonString", "de/d53/a00169.html#a7bc634d3b69e570aa22d04aab7c94823", null ]
 ];

### 2018-06-19 doxygen/de/dc2/a00228.js

@@ -1,5 +1,0 @@
-var a00228 =
-[
-    [ "STRINGIFY", "de/dc2/a00228.html#a6df1d22fb5f09eccc23b9f399670cfd7", null ],
-    [ "TOSTRING", "de/dc2/a00228.html#a9063e80f8777300c93afde6e6f4c9cea", null ]
-];

### 2018-06-19 doxygen/de/df7/a00418.js

@@ -1,7 +1,0 @@
-var a00418 =
-[
-    [ "SegmentedVector", "d1/dc1/a00092.html", "d1/dc1/a00092" ],
-    [ "SVIterator", "dd/dae/a00163.html", "dd/dae/a00163" ],
-    [ "operator+", "de/df7/a00418.html#a88962f88931891b1cc3666c0fba4ffc0", null ],
-    [ "operator-", "de/df7/a00418.html#ace4ba6ea45982ec0ac63c0ad55b4f3fd", null ]
-];

### 2018-06-19 doxygen/df/d95/a00299.js

@@ -1,13 +1,0 @@
-var a00299 =
-[
-    [ "Health", "d3/d00/a00113.html", "d3/d00/a00113" ],
-    [ "HealthStatus", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070", [
-      [ "Susceptible", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a494bf3eaa390dc405dd04ed1c8c99311", null ],
-      [ "Exposed", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070aa54eecd5041d37f5c8443e0ee91e241a", null ],
-      [ "Infectious", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a313760d5227147d14dfed36005286215", null ],
-      [ "Symptomatic", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a89e0873bf9fe03198540a2a9c1d9c76f", null ],
-      [ "InfectiousAndSymptomatic", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a5f022e9ca4876084c0ef540485a5fa1a", null ],
-      [ "Recovered", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a5c4c4cf7bbab0d76fe61420aee14a5ca", null ],
-      [ "Immune", "df/d95/a00299.html#a738f5251821f53315d2aebf214fbd070a9ef69f48f751342bb563666bdbc224fb", null ]
-    ] ]
-];

### 2018-06-19 doxygen/df/da9/a00263.js

@@ -1,0 +1,4 @@
+var a00263 =
+[
+    [ "ExcAssert", "df/da9/a00263.html#a53951f1917941ac25ba6508b1b72771f", null ]
+];

### 2018-06-19 doxygen/df/dc8/a00122.js

@@ -1,5 +1,4 @@
 var a00122 =
 [
-    [ "InfectorMap", "df/dc8/a00122.html#a389bcbbddf547f27cb2e60feadca12af", null ],
-    [ "Add", "df/dc8/a00122.html#a2abaaf56ff495aa37bfead7eea5405de", null ]
+    [ "Exec", "df/dc8/a00122.html#a3e10dc57119090c30ba818420bbd7b94", null ]
 ];

### 2018-06-19 doxygen/df/dcd/a00127.js

@@ -1,5 +1,5 @@
 var a00127 =
 [
-    [ "Contact", "df/dcd/a00127.html#a4029fe93d6d5a913497231f343f686ab", null ],
-    [ "Trans", "df/dcd/a00127.html#a52603e3ed1e5a67a20110c339ce25872", null ]
+    [ "Contact", "df/dcd/a00127.html#a027a20be44f26ed2efddc2198158cc04", null ],
+    [ "Trans", "df/dcd/a00127.html#a2407907ef49e05cf7c170a87aef55680", null ]
 ];

### 2018-06-19 doxygen/navtreeindex8.js

@@ -1,37 +1,140 @@
 var NAVTREEINDEX8 =
 {
-"dc/d0c/a00430.html":[3,0,257],
-"dc/d0c/a00430_source.html":[3,0,257],
-"dc/d0f/a00303.html":[3,0,130],
-"dc/d0f/a00303_source.html":[3,0,130],
-"dc/d28/a00223.html":[3,0,50],
-"dc/d28/a00223_source.html":[3,0,50],
-"dc/d28/a00276.html":[3,0,103],
-"dc/d28/a00276_source.html":[3,0,103],
-"dc/d2f/a00425.html":[3,0,252],
-"dc/d2f/a00425_source.html":[3,0,252],
-"dc/d31/a00208.html":[3,0,35],
-"dc/d31/a00208_source.html":[3,0,35],
+"db/d57/a00112.html#a717f87bbb0a74caf3c65e8b1039a4dc5":[2,0,6,39,1],
+"db/d57/a00112.html#ac9549db2c1d92fbfd650d031f64fa42e":[2,0,6,39,3],
+"db/d57/a00112.html#af8ee2c666be0831c8593b7d1229f8c11":[2,0,6,39,6],
+"db/d57/a00112.html#af99fbfe3cc3bcb48d94aafa00c2cb164":[2,0,6,39,4],
+"db/d7b/a00296.html":[3,0,119],
+"db/d7b/a00296_source.html":[3,0,119],
+"db/d7e/a00372.html":[3,0,195],
+"db/d7e/a00372_source.html":[3,0,195],
+"db/d95/a00391.html":[3,0,214],
+"db/d95/a00391_source.html":[3,0,214],
+"db/da2/a00300.html":[3,0,123],
+"db/da2/a00300_source.html":[3,0,123],
+"db/dab/a00089.html":[2,0,18],
+"db/db1/a00460.html":[1,0,1,1],
+"db/db1/a00460.html":[2,0,1,1],
+"db/db2/a00020.html":[2,0,1,5],
+"db/db2/a00020.html#a3ea831d2b6fbbb1187086e4b985daf07":[2,0,1,5,0],
+"db/db6/a00074.html":[2,0,3,0,0],
+"db/db9/a00387.html":[3,0,210],
+"db/db9/a00387.html#a0d22d904ddff0d21494405335e5fc744":[3,0,210,0],
[…]

### 2018-06-19 doxygen/search/all_13.js

@@ -1,40 +1,40 @@
 var searchData=
 [
-  ['contactlogmode',['ContactLogMode',['../d2/d9d/a00464.html',1,'stride']]],
-  ['contactpooltype',['ContactPoolType',['../db/de0/a00465.html',1,'stride']]],
+  ['contactlogmode',['ContactLogMode',['../d7/db5/a00472.html',1,'stride']]],
+  ['contactpooltype',['ContactPoolType',['../dc/d8e/a00473.html',1,'stride']]],
   ['stride_3a_20simulation_20of_20transmission_20of_20infectious_20diseases_2e',['Stride: Simulation of TRansmission of Infectious DisEases.',['../index.html',1,'']]],
-  ['main_2ecpp',['main.cpp',['../d0/d48/a00351.html',1,'']]],
-  ['output',['output',['../db/d2c/a00466.html',1,'stride']]],
-  ['python',['python',['../d7/d5e/a00467.html',1,'stride']]],
-  ['rnenginetype',['RNEngineType',['../df/d38/a00468.html',1,'stride']]],
-  ['safe_5fcast',['safe_cast',['../d0/d29/a00470.html#ab6efe1a2dbf4a57479e8c7faa00e3359',1,'stride::util']]],
-  ['sample',['Sample',['../d8/d17/a00114.html#a562b022d2c7f2836b4400e7d19e1b040',1,'stride::HealthSeeder']]],
+  ['main_2ecpp',['main.cpp',['../d3/dc9/a00355.html',1,'']]],
+  ['output',['output',['../d5/d26/a00474.html',1,'stride']]],
+  ['python',['python',['../d1/d92/a00475.html',1,'stride']]],
+  ['rnenginetype',['RNEngineType',['../d9/d34/a00476.html',1,'stride']]],
+  ['safe_5fcast',['safe_cast',['../d9/dea/a00478.html#ab6efe1a2dbf4a57479e8c7faa00e3359',1,'stride::util']]],
+  ['sample',['Sample',['../d2/da3/a00115.html#a562b022d2c7f2836b4400e7d19e1b040',1,'stride::HealthSeeder']]],
   ['saveconfig',['SaveConfig',['../d9/da4/a00078.html#a4568f237cc4481a8e89141cf302c3361',1,'Launcher']]],
[…]

### 2018-06-19 doxygen/search/all_4.js

@@ -10,39 +10,39 @@ var searchData=
   ['calculateworkplacesincity',['CalculateWorkplacesInCity',['../d6/d2c/a00072.html#ae813a532362b485b1f15cf400f54ff5d',1,'gengeopop::WorkplacePopulator']]],
   ['calendar',['Calendar',['../d1/d44/a00098.html',1,'stride']]],
   ['calendar',['Calendar',['../d1/d44/a00098.html#a2f1b3543ea350957ea793e6b2d3ae851',1,'stride::Calendar']]],
-  ['calendar_2ecpp',['Calendar.cpp',['../d7/ded/a00196.html',1,'']]],
-  ['calendar_2eh',['Calendar.h',['../de/db1/a00197.html',1,'']]],
-  ['calibration',['calibration',['../d9/d10/a00449.html',1,'']]],
+  ['calendar_2ecpp',['Calendar.cpp',['../d3/db1/a00200.html',1,'']]],
+  ['calendar_2eh',['Calendar.h',['../dd/de3/a00201.html',1,'']]],
+  ['calibration',['calibration',['../de/d87/a00456.html',1,'']]],
   ['calibrationrunner',['CalibrationRunner',['../de/d21/a00006.html',1,'calibration']]],
   ['calibrationrunner',['CalibrationRunner',['../de/d21/a00006.html#a62a7912b727492f5ef378caadcffc58c',1,'calibration::CalibrationRunner']]],
-  ['calibrationrunner_2ecpp',['CalibrationRunner.cpp',['../d7/da0/a00198.html',1,'']]],
-  ['calibrationrunner_2eh',['CalibrationRunner.h',['../d8/d72/a00199.html',1,'']]],
+  ['calibrationrunner_2ecpp',['CalibrationRunner.cpp',['../db/d53/a00202.html',1,'']]],
+  ['calibrationrunner_2eh',['CalibrationRunner.h',['../de/d79/a00203.html',1,'']]],
   ['calibrator',['Calibrator',['../de/d5e/a00007.html',1,'calibration']]],
[…]

### 2018-06-19 doxygen/search/all_6.js

@@ -1,19 +1,20 @@
 var searchData=
 [
-  ['effectiveage',['EffectiveAge',['../d3/d5d/a00463.html#abe2f1ef509d97ae6c13bdcd187e495f2',1,'stride']]],
+  ['effectiveage',['EffectiveAge',['../d0/d29/a00470.html#abe2f1ef509d97ae6c13bdcd187e495f2',1,'stride']]],
   ['emitlocations',['EmitLocations',['../d8/d84/a00001.html#a613fb0cc751f55a428c18156fae84d15',1,'Backend']]],
-  ['emplace',['emplace',['../db/d48/a00148.html#a8aee74d02cb317ad6a8212f9a84c9254',1,'stride::util::Any::emplace()'],['../d1/dc1/a00092.html#aadda0fa9cba3c25598d83fc335dab5e4',1,'stride::util::SegmentedVector::emplace()']]],
+  ['emplace',['emplace',['../d7/d9a/a00152.html#a8aee74d02cb317ad6a8212f9a84c9254',1,'stride::util::Any::emplace()'],['../d1/dc1/a00092.html#aadda0fa9cba3c25598d83fc335dab5e4',1,'stride::util::SegmentedVector::emplace()']]],
   ['emplace_5fback',['emplace_back',['../d1/dc1/a00092.html#a2cd11f9b95b20b69378fc9268c380096',1,'stride::util::SegmentedVector']]],
   ['empty',['empty',['../d1/dc1/a00092.html#a66676df2d3b52bf0eb5896f2d48837af',1,'stride::util::SegmentedVector::empty()'],['../d1/dea/a00054.html#afad11c4405af9e2000dd75f751f4996d',1,'gengeopop::KdTree::Empty()']]],
[…]

### 2018-06-19 doxygen/search/classes_0.js

@@ -2,8 +2,8 @@ var searchData=
 [
   ['aabb',['AABB',['../d2/de7/a00014.html',1,'gengeopop']]],
   ['abstractpopbuilder',['AbstractPopBuilder',['../d4/d7d/a00093.html',1,'stride']]],
-  ['adoptedfile',['AdoptedFile',['../d5/deb/a00132.html',1,'stride::output']]],
-  ['adoptedviewer',['AdoptedViewer',['../dc/de6/a00167.html',1,'stride::viewers']]],
+  ['adoptedfile',['AdoptedFile',['../d0/de8/a00133.html',1,'stride::output']]],
+  ['adoptedviewer',['AdoptedViewer',['../d1/d0d/a00171.html',1,'stride::viewers']]],
   ['agecontactprofile',['AgeContactProfile',['../dc/d54/a00094.html',1,'stride']]],
-  ['any',['Any',['../db/d48/a00148.html',1,'stride::util']]]
+  ['any',['Any',['../d7/d9a/a00152.html',1,'stride::util']]]
 ];

### 2018-06-19 doxygen/search/classes_10.js

@@ -6,19 +6,19 @@ var searchData=
   ['segmentedvector_3c_20person_20_3e',['SegmentedVector&lt; Person &gt;',['../d1/dc1/a00092.html',1,'stride::util']]],
   ['segmentedvector_3c_20stride_3a_3acontactpool_20_3e',['SegmentedVector&lt; stride::ContactPool &gt;',['../d1/dc1/a00092.html',1,'stride::util']]],
   ['segmentedvector_3c_20stride_3a_3aperson_20_3e',['SegmentedVector&lt; stride::Person &gt;',['../d1/dc1/a00092.html',1,'stride::util']]],
-  ['sim',['Sim',['../de/d14/a00139.html',1,'stride']]],
-  ['simbuilder',['SimBuilder',['../d5/db1/a00140.html',1,'stride']]],
-  ['simrunner',['SimRunner',['../d5/d4e/a00141.html',1,'stride']]],
-  ['simworker',['SimWorker',['../d2/d82/a00142.html',1,'stride']]],
-  ['sliceindexer',['SliceIndexer',['../de/d38/a00160.html',1,'stride::util']]],
-  ['stopwatch',['Stopwatch',['../d6/d7d/a00161.html',1,'stride::util']]],
-  ['subject',['Subject',['../db/d44/a00162.html',1,'stride::util']]],
-  ['subject',['Subject',['../d4/ddd/a00138.html',1,'stride::python']]],
-  ['subject_3c_20stride_3a_3asim_5fevent_3a_3aid_20_3e',['Subject&lt; stride::sim_event::Id &gt;',['../db/d44/a00162.html',1,'stride::util']]],
+  ['sim',['Sim',['../d5/d4e/a00141.html',1,'stride']]],
+  ['simbuilder',['SimBuilder',['../d2/d82/a00142.html',1,'stride']]],
+  ['simrunner',['SimRunner',['../d7/dce/a00143.html',1,'stride']]],
+  ['simworker',['SimWorker',['../d5/da7/a00144.html',1,'stride']]],
+  ['sliceindexer',['SliceIndexer',['../db/ddf/a00164.html',1,'stride::util']]],
+  ['stopwatch',['Stopwatch',['../d0/d48/a00165.html',1,'stride::util']]],
+  ['subject',['Subject',['../d9/d38/a00166.html',1,'stride::util']]],
+  ['subject',['Subject',['../de/d14/a00139.html',1,'stride::python']]],
[…]

### 2018-06-19 doxygen/search/classes_11.js

@@ -3,11 +3,13 @@ var searchData=
   ['tablestruct',['TableStruct',['../db/ddf/a00088.html',1,'protobuf_geogrid_2eproto']]],
   ['testcalibrationrunner',['TestCalibrationRunner',['../da/da0/a00009.html',1,'calibration']]],
   ['threadexception',['ThreadException',['../dc/ddf/a00067.html',1,'gengeopop']]],
-  ['threshold',['Threshold',['../d5/da7/a00144.html',1,'stride']]],
-  ['timestamp',['TimeStamp',['../db/ddf/a00164.html',1,'stride::util']]],
-  ['timetostring',['TimeToString',['../d0/d48/a00165.html',1,'stride::util']]],
-  ['transmissionprofile',['TransmissionProfile',['../da/ddb/a00145.html',1,'stride']]],
-  ['travellerprofile',['TravellerProfile',['../d9/db6/a00146.html',1,'stride']]],
-  ['travellerprofilebuilder',['TravellerProfileBuilder',['../d0/d4a/a00147.html',1,'stride']]],
+  ['threshold',['Threshold',['../d9/db6/a00146.html',1,'stride']]],
+  ['timestamp',['TimeStamp',['../dd/da7/a00168.html',1,'stride::util']]],
+  ['timetostring',['TimeToString',['../de/d53/a00169.html',1,'stride::util']]],
+  ['transmissionprofile',['TransmissionProfile',['../d0/d4a/a00147.html',1,'stride']]],
+  ['travellerindex',['TravellerIndex',['../db/d48/a00148.html',1,'stride']]],
+  ['travellerinfo',['TravellerInfo',['../da/d1e/a00149.html',1,'stride::TravellerIndex']]],
+  ['travellerprofile',['TravellerProfile',['../d9/d7d/a00150.html',1,'stride']]],
+  ['travellerprofilebuilder',['TravellerProfileBuilder',['../dd/db2/a00151.html',1,'stride']]],
   ['true_5ftype',['true_type',['../d1/d6e/a00073.html',1,'']]]
 ];

### 2018-06-19 doxygen/search/classes_6.js

@@ -1,7 +1,7 @@
 var searchData=
 [
   ['gengeopopcontroller',['GenGeoPopController',['../d0/d33/a00027.html',1,'gengeopop']]],
-  ['genpopbuilder',['GenPopBuilder',['../d4/d81/a00110.html',1,'stride']]],
+  ['genpopbuilder',['GenPopBuilder',['../dd/d6d/a00111.html',1,'stride']]],
   ['geoaggregator',['GeoAggregator',['../dc/d3c/a00028.html',1,'gengeopop']]],
   ['geoaggregator_3c_20policy_20_3e',['GeoAggregator&lt; Policy &gt;',['../d5/d16/a00029.html',1,'gengeopop']]],
   ['geoaggregator_3c_20policy_2c_20f_20_3e',['GeoAggregator&lt; Policy, F &gt;',['../d5/d79/a00030.html',1,'gengeopop']]],
@@ -24,6 +24,6 @@ var searchData=
   ['geogridreaderfactory',['GeoGridReaderFactory',['../d5/db6/a00042.html',1,'gengeopop']]],
   ['geogridwriter',['GeoGridWriter',['../d6/d42/a00043.html',1,'gengeopop']]],
   ['geogridwriterfactory',['GeoGridWriterFactory',['../d5/df9/a00044.html',1,'gengeopop']]],
-  ['guicontroller',['GuiController',['../dd/d6d/a00111.html',1,'stride']]],
+  ['guicontroller',['GuiController',['../db/d57/a00112.html',1,'stride']]],
   ['guicontrollerbackend',['GuiControllerBackend',['../db/df8/a00076.html',1,'']]]
 ];

### 2018-06-19 doxygen/search/classes_7.js

@@ -1,8 +1,8 @@
 var searchData=
 [
-  ['hbm',['HBM',['../db/d57/a00112.html',1,'stride']]],
-  ['health',['Health',['../d3/d00/a00113.html',1,'stride']]],
-  ['healthseeder',['HealthSeeder',['../d8/d17/a00114.html',1,'stride']]],
+  ['hbm',['HBM',['../d3/d00/a00113.html',1,'stride']]],
+  ['health',['Health',['../d8/d17/a00114.html',1,'stride']]],
+  ['healthseeder',['HealthSeeder',['../d2/da3/a00115.html',1,'stride']]],
   ['household',['Household',['../d6/d97/a00045.html',1,'gengeopop']]],
   ['householdcsvreader',['HouseholdCSVReader',['../d3/dea/a00046.html',1,'gengeopop']]],
   ['householdgenerator',['HouseholdGenerator',['../d6/d2d/a00047.html',1,'gengeopop']]],

### 2018-06-19 doxygen/search/classes_f.js

@@ -2,11 +2,12 @@ var searchData=
 [
   ['radiuspolicy',['RadiusPolicy',['../d4/de8/a00061.html',1,'gengeopop']]],
   ['rangeindexer',['RangeIndexer',['../da/d82/a00091.html',1,'stride::util']]],
-  ['rangeindexer_3c_20t_2c_20std_3a_3asize_5ft_20_3e',['RangeIndexer&lt; T, std::size_t &gt;',['../d2/d34/a00156.html',1,'stride::util']]],
+  ['rangeindexer_3c_20t_2c_20std_3a_3asize_5ft_20_3e',['RangeIndexer&lt; T, std::size_t &gt;',['../de/d38/a00160.html',1,'stride::util']]],
   ['rangeindexer_3c_20util_3a_3astride_3a_3autil_3a_3asegmentedvector_3c_20stride_3a_3aperson_20_3e_2c_20std_3a_3asize_5ft_20_3e',['RangeIndexer&lt; util::stride::util::SegmentedVector&lt; stride::Person &gt;, std::size_t &gt;',['../da/d82/a00091.html',1,'stride::util']]],
   ['readerfactory',['ReaderFactory',['../df/d03/a00062.html',1,'gengeopop']]],
-  ['rnmanager',['RNManager',['../d1/db7/a00157.html',1,'stride::util']]],
-  ['runconfigmanager',['RunConfigManager',['../de/db9/a00159.html',1,'stride::util']]],
+  ['regionslicer',['RegionSlicer',['../d5/db1/a00140.html',1,'stride']]],
+  ['rnmanager',['RNManager',['../d6/d7d/a00161.html',1,'stride::util']]],
+  ['runconfigmanager',['RunConfigManager',['../dd/dae/a00163.html',1,'stride::util']]],
   ['runtype',['RunType',['../da/d24/a00068.html',1,'gengeopop::ThreadException']]],
   ['runtype_3c_20void_20_3e',['RunType&lt; void &gt;',['../d4/d31/a00069.html',1,'gengeopop::ThreadException']]]
 ];

### 2018-06-19 doxygen/search/defines_0.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['stringify',['STRINGIFY',['../de/dc2/a00228.html#a6df1d22fb5f09eccc23b9f399670cfd7',1,'ConfigInfo.cpp']]]
+  ['stringify',['STRINGIFY',['../d0/d53/a00232.html#a6df1d22fb5f09eccc23b9f399670cfd7',1,'ConfigInfo.cpp']]]
 ];

### 2018-06-19 doxygen/search/enums_4.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['variablestate',['VariableState',['../d3/d5d/a00463.html#a9d01e8d18496c1065ce04a29ec8b3470',1,'stride']]]
+  ['variablestate',['VariableState',['../d0/d29/a00470.html#a9d01e8d18496c1065ce04a29ec8b3470',1,'stride']]]
 ];

### 2018-06-19 doxygen/search/enumvalues_1.js

@@ -1,6 +1,6 @@
 var searchData=
 [
   ['capacity',['Capacity',['../d7/dd4/a00013.html#a92c3ad424613962b9a2f9de72970dc70a7217d4e9454d965e507f275edd4eecc4',1,'ContactPoolListModel']]],
-  ['cocoon',['Cocoon',['../d3/d5d/a00463.html#add8b5ebb9e886c003bf194783b4dd7fea4a15b408bd69263798be7e433d449dae',1,'stride']]],
-  ['college',['College',['../db/de0/a00465.html#aaa214aee675050e781497b0dd15449aba2806259c227f694c678ec9444aec2042',1,'stride::ContactPoolType']]]
+  ['cocoon',['Cocoon',['../d0/d29/a00470.html#add8b5ebb9e886c003bf194783b4dd7fea4a15b408bd69263798be7e433d449dae',1,'stride']]],
+  ['college',['College',['../dc/d8e/a00473.html#aaa214aee675050e781497b0dd15449aba2806259c227f694c678ec9444aec2042',1,'stride::ContactPoolType']]]
 ];

### 2018-06-19 doxygen/search/enumvalues_12.js

@@ -1,5 +1,5 @@
 var searchData=
 [
-  ['yarn2',['yarn2',['../df/d38/a00468.html#a4dad7ad4a2f8f59eb0e51b89ba0c192bacd05faf08e35df974d2c98f26230bff1',1,'stride::RNEngineType']]],
-  ['yarn3',['yarn3',['../df/d38/a00468.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba325f9198cb6d6f356ff4dae2598dfbc7',1,'stride::RNEngineType']]]
+  ['yarn2',['yarn2',['../d9/d34/a00476.html#a4dad7ad4a2f8f59eb0e51b89ba0c192bacd05faf08e35df974d2c98f26230bff1',1,'stride::RNEngineType']]],
+  ['yarn3',['yarn3',['../d9/d34/a00476.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba325f9198cb6d6f356ff4dae2598dfbc7',1,'stride::RNEngineType']]]
 ];

### 2018-06-19 doxygen/search/enumvalues_a.js

@@ -1,6 +1,6 @@
 var searchData=
 [
   ['maxpools',['MaxPools',['../da/d45/a00011.html#a05e0faa6f1216772876b0a2d4f3e1cf0a1de39e94b91aea3de37b3f229fe3df1a',1,'ContactCenterListModel']]],
-  ['mrg2',['mrg2',['../df/d38/a00468.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba73ab14a245ef684f30a4aa9264aa6fb5',1,'stride::RNEngineType']]],
-  ['mrg3',['mrg3',['../df/d38/a00468.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba6a2923899d3ebb06023aa5298c8bbbd3',1,'stride::RNEngineType']]]
+  ['mrg2',['mrg2',['../d9/d34/a00476.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba73ab14a245ef684f30a4aa9264aa6fb5',1,'stride::RNEngineType']]],
+  ['mrg3',['mrg3',['../d9/d34/a00476.html#a4dad7ad4a2f8f59eb0e51b89ba0c192ba6a2923899d3ebb06023aa5298c8bbbd3',1,'stride::RNEngineType']]]
 ];

### 2018-06-19 doxygen/search/enumvalues_f.js

@@ -1,5 +1,5 @@
 var searchData=
 [
-  ['transmissions',['Transmissions',['../d2/d9d/a00464.html#a8f1467c1f622638893d3a1c12eead2baa6d688add062a0c9e2d77cbb1e7594ae5',1,'stride::ContactLogMode']]],
+  ['transmissions',['Transmissions',['../d7/db5/a00472.html#a8f1467c1f622638893d3a1c12eead2baa6d688add062a0c9e2d77cbb1e7594ae5',1,'stride::ContactLogMode']]],
   ['typerole',['TypeRole',['../da/d45/a00011.html#a05e0faa6f1216772876b0a2d4f3e1cf0a82e4dea123d4d816eeeddc24769c1c57',1,'ContactCenterListModel']]]
 ];

### 2018-06-19 doxygen/search/functions_2.js

@@ -12,17 +12,17 @@ var searchData=
   ['calibrator',['Calibrator',['../de/d5e/a00007.html#af054625deb216f50191b155cfe1be657',1,'calibration::Calibrator']]],
   ['capacity',['capacity',['../d1/dc1/a00092.html#ae6e77c3d0e64d983ee26e44336291604',1,'stride::util::SegmentedVector']]],
   ['captureexception',['CaptureException',['../dc/ddf/a00067.html#ac1132fb1b2f34a8ac2ae91eb0ba64732',1,'gengeopop::ThreadException']]],
-  ['cast',['cast',['../db/d48/a00148.html#a25363f8f215051caae46e3094da0bff8',1,'stride::util::Any']]],
+  ['cast',['cast',['../d7/d9a/a00152.html#a25363f8f215051caae46e3094da0bff8',1,'stride::util::Any']]],
   ['cbegin',['cbegin',['../df/d61/a00031.html#ae83a8504901d3b4244fb740d065a9cd8',1,'gengeopop::GeoGrid::cbegin()'],['../d4/d3a/a00101.html#abfa15d23d1997d6ea4619b74c76f01bc',1,'stride::ContactPool::cbegin()'],['../d1/dc1/a00092.html#ace914c758677123e4a8d391cd711a5f8',1,'stride::util::SegmentedVector::cbegin()']]],
   ['cend',['cend',['../df/d61/a00031.html#ae3d4eb8515a5b75cd33d6c32e3e8c48d',1,'gengeopop::GeoGrid::cend()'],['../d4/d3a/a00101.html#a48eee55ad46ff147171898861eba8bda',1,'stride::ContactPool::cend()'],['../d1/dc1/a00092.html#a661e877760bdf6cd246e4038b677434a',1,'stride::util::SegmentedVector::cend()']]],
   ['checkenv',['CheckEnv',['../d9/d77/a00095.html#ab018c0bad76fb740e98203ca2d432a26',1,'stride::BaseController']]],
   ['checkfinalized',['CheckFinalized',['../df/d61/a00031.html#aa4c75377c4a4c0376997e0851b68e886',1,'gengeopop::GeoGrid']]],
-  ['checkinstallenv',['CheckInstallEnv',['../da/d01/a00153.html#a9dde9db2fbf4a2f6fa9e3116b5fe2949',1,'stride::util::FileSys']]],
[…]

### 2018-06-19 doxygen/search/functions_a.js

@@ -3,7 +3,7 @@ var searchData=
   ['latitude',['latitude',['../da/d2a/a00086.html#a6bc5976b2e0d0f05f1a134544844b6bc',1,'proto::GeoGrid_Location_Coordinate']]],
   ['launch',['Launch',['../d9/da4/a00078.html#a69589d1327149e595d3242dab0805035',1,'Launcher']]],
   ['launcher',['Launcher',['../d9/da4/a00078.html#a7be10dda45e4e1704c05b6284b60f9c5',1,'Launcher::Launcher()'],['../d9/da4/a00078.html#a1fd8b38599f6cd9fdc9a1f850cd74760',1,'Launcher::Launcher(const Launcher &amp;b)=delete']]],
-  ['launchgui',['LaunchGui',['../d7/dfc/a00349.html#ae0509bb7817eee297e8f3c9dbd675b00',1,'main.cpp']]],
+  ['launchgui',['LaunchGui',['../db/ddc/a00353.html#ae0509bb7817eee297e8f3c9dbd675b00',1,'main.cpp']]],
   ['loadcombobox',['LoadComboBox',['../d9/da4/a00078.html#a764a1803d2df7509dba617e753f483fb',1,'Launcher']]],
   ['loadgeogridfromcommandline',['LoadGeoGridFromCommandLine',['../d8/d84/a00001.html#a4c68caab686f34853c326b801fbadf4b',1,'Backend']]],
   ['loadgeogridfromfile',['LoadGeoGridFromFile',['../d8/d84/a00001.html#a76b9d9ea83aa45c28655644598ce1b27',1,'Backend']]],

### 2018-06-19 doxygen/search/functions_e.js

@@ -1,7 +1,7 @@
 var searchData=
 [
-  ['para_5finfo',['para_info',['../d0/d29/a00470.html#a1437dc582cd8fb70c6873c692adde468',1,'stride::util']]],
-  ['para_5fseed',['para_seed',['../d0/d29/a00470.html#a0c42ba6e336bed67e5a0bdd053802c2a',1,'stride::util::para_seed(vector&lt; T &gt; &amp;engines, unsigned int stream_count, unsigned long seed)'],['../d0/d29/a00470.html#a3457bcd24475b5a21953b08e7137736d',1,'stride::util::para_seed(vector&lt; T &gt; &amp;engines, unsigned int stream_count, const string &amp;state)']]],
+  ['para_5finfo',['para_info',['../d9/dea/a00478.html#a1437dc582cd8fb70c6873c692adde468',1,'stride::util']]],
+  ['para_5fseed',['para_seed',['../d9/dea/a00478.html#a0c42ba6e336bed67e5a0bdd053802c2a',1,'stride::util::para_seed(vector&lt; T &gt; &amp;engines, unsigned int stream_count, unsigned long seed)'],['../d9/dea/a00478.html#a3457bcd24475b5a21953b08e7137736d',1,'stride::util::para_seed(vector&lt; T &gt; &amp;engines, unsigned int stream_count, const string &amp;state)']]],
   ['parsecontactcenter',['ParseContactCenter',['../de/d8c/a00036.html#afb3033a81be83438278779ea66f0ac7d',1,'gengeopop::GeoGridJSONReader::ParseContactCenter()'],['../d3/de7/a00039.html#a351fab1f7eb8f7035fa432b2a3d7c104',1,'gengeopop::GeoGridProtoReader::ParseContactCenter()']]],
   ['parsecontactpool',['ParseContactPool',['../de/d8c/a00036.html#a5672d9dab3a04cd5663b67b8dadae157',1,'gengeopop::GeoGridJSONReader::ParseContactPool()'],['../d3/de7/a00039.html#a19e0ff14a2aef228d926d53132fa767b',1,'gengeopop::GeoGridProtoReader::ParseContactPool()']]],
[…]

### 2018-06-19 doxygen/search/namespaces_0.js

@@ -1,4 +1,4 @@
 var searchData=
 [
-  ['calibration',['calibration',['../d9/d10/a00449.html',1,'']]]
+  ['calibration',['calibration',['../de/d87/a00456.html',1,'']]]
 ];

### 2018-06-19 doxygen/search/typedefs_7.js

@@ -1,5 +1,7 @@
 var searchData=
 [
-  ['range_5ftype',['range_type',['../da/d82/a00091.html#ac9137dbaf6b528cdbf45fa1dd40e5b34',1,'stride::util::RangeIndexer::range_type()'],['../d2/d34/a00156.html#aa40c399685b42d5a3d8d870b5f63512f',1,'stride::util::RangeIndexer&lt; T, std::size_t &gt;::range_type()'],['../de/d38/a00160.html#ae2f8f5fde77de1bb59c21d3b75fb3698',1,'stride::util::SliceIndexer::range_type()']]],
+  ['range_5ftype',['range_type',['../da/d82/a00091.html#ac9137dbaf6b528cdbf45fa1dd40e5b34',1,'stride::util::RangeIndexer::range_type()'],['../de/d38/a00160.html#aa40c399685b42d5a3d8d870b5f63512f',1,'stride::util::RangeIndexer&lt; T, std::size_t &gt;::range_type()'],['../db/ddf/a00164.html#ae2f8f5fde77de1bb59c21d3b75fb3698',1,'stride::util::SliceIndexer::range_type()']]],
+  ['ranges',['Ranges',['../d5/db1/a00140.html#a37c412934f16bbd51637a30cfcca8412',1,'stride::RegionSlicer']]],
+  ['result',['Result',['../d5/db1/a00140.html#aa5b6ef8977de9fc1d73f0b0f319b8220',1,'stride::RegionSlicer']]],
   ['runtype_5ft',['RunType_t',['../dc/ddf/a00067.html#af366ae4c7b0d7f6d5679b68f6600a118',1,'gengeopop::ThreadException']]]
 ];

### 2018-06-19 doxygen/search/typedefs_8.js

@@ -1,5 +1,5 @@
 var searchData=
 [
-  ['self_5ftype',['self_type',['../d1/dc1/a00092.html#a9e8d6a6fb6adf407e479f954ad70ffb3',1,'stride::util::SegmentedVector::self_type()'],['../dd/dae/a00163.html#acf4391226c3334af2ab02fdbfcbe81c8',1,'stride::util::SVIterator::self_type()']]],
+  ['self_5ftype',['self_type',['../d1/dc1/a00092.html#a9e8d6a6fb6adf407e479f954ad70ffb3',1,'stride::util::SegmentedVector::self_type()'],['../dc/de6/a00167.html#acf4391226c3334af2ab02fdbfcbe81c8',1,'stride::util::SVIterator::self_type()']]],
   ['size_5ftype',['size_type',['../d1/dc1/a00092.html#a4344636a6d7dea3aff481c178b5ff008',1,'stride::util::SegmentedVector']]]
 ];

### 2018-06-19 doxygen/search/variables_3.js

@@ -3,11 +3,12 @@ var searchData=
   ['calculated',['calculated',['../db/df3/a00034.html#af9610682c3d25a6c5cf4dc0164988a54',1,'gengeopop::GeoGridConfig']]],
   ['calibrator',['calibrator',['../de/d21/a00006.html#a3b6f548b4810c4f7936b259b884d65a7',1,'calibration::CalibrationRunner']]],
   ['college',['College',['../df/d5d/a00084.html#a5a97534718d0231be73b42854038f937',1,'proto::GeoGrid_Location_ContactCenter']]],
-  ['columncount',['columnCount',['../d9/d7d/a00150.html#a598821720121beeaed01a7a7216e5601',1,'stride::util::CSV']]],
+  ['columncount',['columnCount',['../d3/d65/a00154.html#a598821720121beeaed01a7a7216e5601',1,'stride::util::CSV']]],
   ['community',['Community',['../df/d5d/a00084.html#aaa150e1e77bd7b4add7dde6e5aacc5d0',1,'proto::GeoGrid_Location_ContactCenter']]],
   ['commutes_5f',['commutes_',['../d4/d63/a00082.html#a894569fd4ed53ed226da26767b5196f3',1,'proto::GeoGrid_Location']]],
   ['compulsorypupils',['compulsoryPupils',['../db/df3/a00034.html#a6f6aa2c75003ae4952a3ad7ce5afe880',1,'gengeopop::GeoGridConfig']]],
   ['configs',['configs',['../de/d21/a00006.html#a419082164b3f4f27abc7ddc4f65663e9',1,'calibration::CalibrationRunner']]],
+  ['constants',['constants',['../db/df3/a00034.html#a2ef783a0eb04a2a0dfc164b72f2c4503',1,'gengeopop::GeoGridConfig']]],
   ['contactcenters',['contactCenters',['../db/df3/a00034.html#a737d7b1ed78c73a8628b1a938a47475f',1,'gengeopop::GeoGridConfig']]],
   ['contactcenters_5f',['contactcenters_',['../d4/d63/a00082.html#a6d5ee56896c3552cabccecd44252f143',1,'proto::GeoGrid_Location']]],
   ['contactloglevel',['contactLogLevel',['../d9/da4/a00078.html#a91bcad505e74e0ba02ac28ca804fa5b6',1,'Launcher']]],

### 2018-06-19 doxygen/search/variables_6.js

@@ -4,5 +4,6 @@ var searchData=
   ['fraction_5f1826_5fyears_5fwhicharestudents',['fraction_1826_years_WhichAreStudents',['../db/df3/a00034.html#a9a3f4f357cef24a66d3c9dcdc58f7b5b',1,'gengeopop::GeoGridConfig']]],
   ['fraction_5f1865_5fyears_5factive',['fraction_1865_years_active',['../db/df3/a00034.html#a34a5fe86ba4e60ef668c1bc60222634d',1,'gengeopop::GeoGridConfig']]],
   ['fraction_5factive_5fcommutingpeople',['fraction_active_commutingPeople',['../db/df3/a00034.html#abc57c86996194cd95c586896e8918a20',1,'gengeopop::GeoGridConfig']]],
-  ['fraction_5fstudent_5fcommutingpeople',['fraction_student_commutingPeople',['../db/df3/a00034.html#a78e9f4c58c365259d7d080dabc329f96',1,'gengeopop::GeoGridConfig']]]
+  ['fraction_5fstudent_5fcommutingpeople',['fraction_student_commutingPeople',['../db/df3/a00034.html#a78e9f4c58c365259d7d080dabc329f96',1,'gengeopop::GeoGridConfig']]],
+  ['from',['from',['../da/d1e/a00149.html#ada53be3bcc1ac0af2b2b0b1d8f3e6bee',1,'stride::TravellerIndex::TravellerInfo']]]
 ];

### 2018-06-19 doxygen/search/variables_b.js

@@ -1,7 +1,8 @@
 var searchData=
 [
-  ['labels',['labels',['../d9/d7d/a00150.html#a4298638a8f9c9871d800338bdf77bd50',1,'stride::util::CSV']]],
+  ['labels',['labels',['../d3/d65/a00154.html#a4298638a8f9c9871d800338bdf77bd50',1,'stride::util::CSV']]],
   ['latitude_5f',['latitude_',['../da/d2a/a00086.html#ac6fb61398d83024973e7b1db2763a81a',1,'proto::GeoGrid_Location_Coordinate']]],
+  ['leaveday',['leaveDay',['../da/d1e/a00149.html#abeb5f8930b5bd8f4940f9e939314651f',1,'stride::TravellerIndex::TravellerInfo']]],
   ['localinformationpolicy',['localInformationPolicy',['../d9/da4/a00078.html#a83e6b13a9a926487a1a2c7983031eafa',1,'Launcher']]],
   ['locations_5f',['locations_',['../d8/d53/a00081.html#aef45db26c3ceb9df2afcc1195be76b9f',1,'proto::GeoGrid']]],
   ['lock',['Lock',['../dc/ddf/a00067.html#a2eaf8c9a458243ef883acf6ded668642',1,'gengeopop::ThreadException']]],

### 2018-06-19 doxygen/search/variables_f.js

@@ -1,6 +1,7 @@
 var searchData=
 [
   ['people_5f',['people_',['../df/d13/a00085.html#a44843691e11c3cde291f62049fe43fc6',1,'proto::GeoGrid_Location_ContactCenter_ContactPool']]],
+  ['person',['person',['../da/d1e/a00149.html#af4ef8d5e213175ec088d18219d7c9479',1,'stride::TravellerIndex::TravellerInfo']]],
   ['persons_5f',['persons_',['../d8/d53/a00081.html#a3b59a92801fa6e3205c99df850f08dd1',1,'proto::GeoGrid']]],
   ['pools_5f',['pools_',['../df/d5d/a00084.html#ac39969a64388bd2631672f1363db74d0',1,'proto::GeoGrid_Location_ContactCenter']]],
   ['population_5f',['population_',['../d4/d63/a00082.html#a6547521bb7e4140e082542aae89d718f',1,'proto::GeoGrid_Location']]],

### 2018-06-19 doc/latex/03-Simulator.tex
Add info about calibrator file
Fix commutes doc

@@
 Ctrl+ A can be used to select all cities, while Ctrl + F can be used to fit the viewport of the map so all cities are visible.
-To show commutes of a city, first enable the \texttt{View -> Show Commutes} option and then select a city.
+To show commutes of a city, first enable the \texttt{View -> Show Commutes} option. The commutes between the selected cities will be shown.
 While simulating a blue marker indicates that no one is infected at that location.
@@
     \item[\texttt{--output}]\ \\
-        Write the results of the calibration to a file with given filename. This resulting file contains ...
+        Write the results of the calibration to a file with given filename.
+        This resulting file contains for each configuration and each step in the simulation the mean, standard deviation, exact value using the default seed and the values found with other seeds.
+        These values depend on the selected options, specifically \texttt{--multiple} and \texttt{--single}.
     \item[\texttt{--write}]\ \\

### 2018-06-19 doc/latex/02-Software.tex
Fix <
Fixes

@@
 Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
-To use the visualization tools Qt is needed (at least version 5.9), besides that the following tools needs to be installed:
+The following tools needs to be installed:
 \begin{compactitem}
@@
     \item make
-    \item CMake (>= v3.10)
+    \item CMake (\textgreater = v3.10)
     \item Boost
+    \item Qt (\textgreater = 5.9, optional, for visualization)
     \item Python (optional, for automatization)
@@
 
-To install the project, first obtain the source code by cloning the repository to a directory or download a zip file with all project
-material from the GitHub website and de-compress the archive. 
+To install the project, first obtain the source code by cloning the repository to a directory .
 The build system for Stride uses the CMake tool. This is used to build and install the software at a high level of abstraction and almost platform independent (see \url{http://www.cmake.org/}). 

### 2018-06-19 doc/latex/03-Simulator.tex
Fixes

@@
 
-        \item $DE\_cities.csv$: German cities, fetched from \footnote{\url{}}.
-        \item $FR\_cities.csv$: French cities, fetched from \footnote{\url{}}.
-        \item $NL\_cities.csv$: Dutch cities, fetched from \footnote{\url{}}.
-        \item $wallonia\_cities.csv$: Wallonia cities, fetched from \footnote{\url{}}.
-        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{}}.
+        \item $DE\_cities.csv$: German cities, fetched from \footnote{\url{https://en.wikipedia.org/wiki/List\_of\_cities\_and\_towns\_in\_Germany}}.
+        \item $FR\_cities.csv$: French cities, fetched from \footnote{\url{https://en.wikipedia.org/wiki/List\_of\_arrondissements\_of\_France}}.
+        \item $NL\_cities.csv$: Dutch cities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Tabel\_van\_Nederlandse\_gemeenten}}.
+        \item $wallonia\_cities.csv$: Walloon cities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Waals\_Gewest}}.
+        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Vlaams\_Gewest}}.
         \end{itemize}
@@
         If this is provided multiple times, the calibration is performed on all given simulations.
-        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
-        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
+        It may be either \texttt{-c file=<file>} \texttt{or -c name=<name>}.
+        The first option can be shortened to \texttt{-c <file>}, the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \texttt{<name}.
     \item[\texttt{--testcases}] \ \\

### 2018-06-19 doc/latex/01-Introduction.tex
Latest fixes

  %%!TEX root = ./UserManual.tex
\chapter{Introduction}
\label{chap:Introduction}

This manual provides a brief description of the Stride software and its
features. 
Stride stands for \textbf{S}imulation of \textbf{tr}ansmission 
 of \textbf{i}nfectious \textbf{d}is\textbf{e}ases and is an agent-based modeling 
system for close-contact disease transmission developed by researchers at the
University of Antwerp and Hasselt University, Belgium.
The simulator uses census-based synthetic populations
that capture the demographic and geographic distributions, as well as detailed social networks.
Stride is an open source software. The authors hope to make large-scale
agent-based epidemic models more useful to the community.
More info on the project and results obtained with the software
can be found in: 
\textit{``Willem L, Stijven S, Tijskens E, Beutels P, Hens N \& Broeckhove J. (2015) Optimizing agent-based transmission models for infectious diseases, BMC Bioinformatics, 16:183''} \cite{willem2015}.

The model population consists of households, schools, workplaces and
communities, which represent a group of people we define as a ``ContactPool''.
Social contacts can only happen within a ContactPool. 
When school or work is off, people stay at home and in their primary
community and can have social contacts with the other members.
During other days, people are present in their household, secondary community
and a possible workplace or school.

We use a $Simulator$ class to organize the activities from the people in the population.
The ContactPools in a population are grouped into ContactCenters (e.g. the different classes of a school are grouped into one K12School ContactCenter}
These ContactCenters are geographically grouped into a geographical grid (sometimes called GeoGrid)

The $Contact Handler$ performs Bernoulli trials to decide whether a contact
between an infectious and susceptible person leads to disease transmission. 
People transit through Susceptible-Exposed-Infected-Recovered states,
similar to an influenza-like disease.
Each $ContactPool$ contains a link to its members and the $Population$ stores all personal
data, with $Person$ objects.
The implementation is based on the open source model from Grefenstette et al. \cite{grefenstette2013}. 
The household, workplace and school clusters are handled separately from the
community clusters, which are used to model general community contacts. The
$Population$ is a collection of $Person$ objects.

### 2018-06-19 doc/latex/02-Software.tex
Latest fixes

@@
 
-Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
+Stride is written in C++ and portable over all platforms that have a sufficiently recent version of the GNU C++ compiler. 
 The following tools needs to be installed:
@@
     \item CMake (\textgreater = v3.10)
-    \item Boost
+    \item Boost (\textgreater = 1.66 is known to work)
     \item Qt (\textgreater = 5.9, optional, for visualization)
@@
 The Application Programmer Interface (API) documentation is generated automatically 
-using the Doxygen tool ((see \url{www.doxygen.org}) from documentation instructions 
+using the Doxygen tool (see \url{www.doxygen.org}) from documentation instructions 
 embedded in the code .
@@
 The project directory structure is very systematic.
-Everything used to build the software is stored in the directory \texttt{./src}:
+Everything used to build the software is stored in the root directory:
 \begin{compactitem}
-    \item \texttt{src/main}: Code related files (sources, third party libraries and headers, ...)
+    \item \texttt{main}: Code related files (sources, third party libraries and headers, ...)
       	\begin{itemize}
-        		\item \texttt{src/main/<language>}: source code, per coding language: cpp (for C++), python, R,   
-        		\item \texttt{src/main/resources}: third party resources included in the project: 
+        		\item \texttt{main/<language>}: source code, per coding language: cpp (for C++), python, R,   
+        		\item \texttt{main/resources}: third party resources included in the project: 
         \end{itemize}
-    \item \texttt{src/doc}: documentation files (API, manual, ...)
+    \item \texttt{doc}: documentation files (API, manual, ...)
       	\begin{itemize}
-        		\item \texttt{src/doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
-        		\item \texttt{src/doc/latex\_man}: files needed to generate the user manual with Latex
+        		\item \texttt{doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
+        		\item \texttt{doc/latex\_man}: files needed to generate the user manual with Latex
         \end{itemize}
-    \item \texttt{src/test}: test related files (scripts, regression files, ...)
+    \item \texttt{test}: test related files (scripts, regression files, ...)
 \end{compactitem}

### 2018-06-19 doc/latex/01-Introduction.tex

@@
 We use a $Simulator$ class to organize the activities from the people in the population.
-The ContactPools in a population are grouped into ContactCenters (e.g. the different classes of a school are grouped into one K12School ContactCenter}
+The ContactPools in a population are grouped into ContactCenters (e.g. the different classes of a school are grouped into one K12School ContactCenter).
 These ContactCenters are geographically grouped into a geographical grid (sometimes called GeoGrid)

### 2018-08-22 doc/latex/03-Simulator.tex
Latest fixes
Add background information for gengeopop + template for other sections that have to be added to the manual

@@
 
-\item \texttt{-r} or \texttt{{-}-r0}: To obtain the basic reproduction number, no tertiary infections.
+\item \texttt{-v} or \texttt{{-}-mapviewer}: Shows the MapViewer during simulation (only useful when using a GeoGrid).
 
@@
         The state to be used for initializing the random engine. This can be used to continue with the same state when generating multiple regions.
-    \item[\texttt{--rng\_type}] \ \\
-        The type of random engine to use by default \texttt{mrg2} is used.
-Available options are: \texttt{mrg2}, \texttt{mrg3}, \texttt{yarn2}, \texttt{yarn3}, \texttt{lgc64} and \texttt{lgc64\_shift}.
     \item[\texttt{--seed}] \ \\

### 2018-08-22 doc/latex/04-Code.tex
Add background information for gengeopop + template for other sections that have to be added to the manual

%%!TEX root = ./UserManual.tex
\chapter{Code}
\label{chap:code}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GenGeoPop
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{GenGeoPop}
\label{section:gengeopop}

\subsection{Background}
\label{subsection:background}

To explain the algorithms used for generating the geography of the countries and their respective population, we have to introduce some background concepts:

\begin{description}
    \item[ContactPool]:
        A pool of persons that potentially come in contact with each other.
        If they actually do and if a transmission of an infection occurs depends on the algorithms in the simulator.
        We distinguish different types of ContactPools associated with work, school, community and households.
        Note that there is a difference between the size of a school (for example 500 students) and the size of the ContactPools inside the school (20 students).
    \item[ContactCenter]:
        A group of one or more ContactPools of the same type.
        This allows for a single College to contain multiple classes for example.
        It is also used to contain a single ContactPool, for example in the case of a Household.
    \item[K-12 student]: Part of the population from 3 until 18 years of age that are obligated (at least in Belgium) to attend a school. Students that skip or repeat years are not accounted for.
    \item[College student]:
        Persons older than 18 and younger than 26 years of age that attend a higher education. For simplicity we will group all forms of higher eduction into the same type of ContactCenter, a College. A fraction of college students will attend a college ``close to home'' and the others will attend a college ``far from home''.
        Most educations don't last for 8 years, but using this number we compensate for changes in the field of study, doctoral studies, advanced masters and repeating a failed year of study.
    \item[Employable]:
        We consider people of ages 18 to 65 as employable. A fraction of people between 18 and 26 will attend a college, and the complementary fraction will be employable.
    \item[Active population]:
        The fraction of the employable part of the population that is actually working. A fraction of these workers will work ``close to home'' and the complementary fraction will commute to a workplace further away.
    \item[Household profile]:
        The composition of households in terms of the number of members and their age is an important factor in the simulation. In this case the profile is not defined by the age of its members or fractions, but through a set of reference households. This set contains a sample of households which are representative of the whole population in their composition.
    \item[GeoGrid locations]:
        Our data only allows for a very limited geographical resolution. We have the longitude and latitude of cities and municipalities (a distinction we will not make), which we shall use to create GeoGrid locations for the domicile of the households.
        All households in the same location are mapped to the coordinates of the location's center. These locations with corresponding coordinates will form a grid that will contain the complete simulation area.
\end{description}

\subsection{Generating the geography}
\label{subsection:gengeo}
TODO

\subsection{Generating the population}
\label{subsection:genpop}
TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Travel
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Travel}
\label{section:travel}
TODO

### 2018-08-23 doc/latex/02-Software.tex
Add background information for gengeopop + template for other sections that have to be added to the manual
Add gengeo to manual

@@
       	\begin{itemize}
-        		\item \texttt{doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
-        		\item \texttt{doc/latex\_man}: files needed to generate the user manual with Latex
+        		\item \texttt{doc/doxygen}: files needed to generate the reference documentation with Doxygen
+        		\item \texttt{doc/latex}: files needed to generate the user manual with Latex
         \end{itemize}
@@
 \end{description}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Protobuf
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Protocol Buffers}
+\label{section:protobuf}
+TODO

### 2018-08-23 doc/latex/03-Simulator.tex
Add gengeo to manual

@@
 		\item $belgium\_population$: Relative Belgian population per city. Details are provided for all cities and for 13 major cities.
+        \item $flanders\_cities$: Cities and municipalities in Flanders with coordinates and population figures based on samples.
+These relative population figures are used for assigning residencies and domiciles based on a discrete probability distribution.
+        \item $flanders\_commuting$: Relative commuting information between cities and communities.
+Since this data is relative, the total number of commuters is a derived parameter, based on the fraction of the total population that is commuting.
 		\item $contact\_matrix\_average$: Social contact rates, given the cluster type. Community clusters have average (week/weekend) rates.

### 2018-08-23 doc/latex/04-Code.tex
Add gengeo to manual

@@
 \label{subsection:gengeo}
-TODO
+We start by generating the geographical component, we call this a GeoGrid.
+This contains locations with an id, name, province, coordinates and nominative population figures.
+These locations contain multiple ContactCenters, like Schools and Households, which in turn contain ContactPools.
+This structure is internally generated by several ``Generators" and will afterwards be used by ``Populators" to fill the ContactPools.
+We construct the following types of ContactCenter:
+
+\begin{description}
+    \item[K-12 Schools]:
+        These schools contain on average 500 students, with an average of 20 students per class, which corresponds to 25 ContactPools.
+        The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
+        These generated schools are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
+    \item[Colleges]:
+        These contain an average of 3000 students and 150 students per ContactPool.
+        They are exclusively assigned to the 10 biggest locations in terms of population size.
+        Within those 10 locations we again use a discrete distribution based on the relative population of the city compared to the total population in these top 10 cities.
+    \item[Workplaces]:
+        The assignment of workplaces is analogous to that of K-12 schools, but now we account for commuting information to determine the actual number of workers in a location.
+        We find this amount by the working people who live there plus the people that commute to this location minus the ones that live there but commute away.
+        A workplace contains on average 20 people.
+    \item[Communities]:
+        We create both primary and secondary communities, each containing 2000 persons from all ages and occupations.
+        The assignement is analogous to that of K-12 schools.
+    \item[Households]:
+        The number of households is determined by the average size of a household in the reference profile and the total population size.
+        The assignement is again analogous to that of K-12 schools.
+\end{description}
 

### 2018-08-23 doc/latex/04-Code.tex
Add documentation for GenPop in manual

@@
 This structure is internally generated by several ``Generators" and will afterwards be used by ``Populators" to fill the ContactPools.
-We construct the following types of ContactCenter:
+The different types of ContactCenters are created by a different partial generator for each type and added separately to the GeoGrid.
+We construct the following types of ContactCenters:
 
 \begin{description}
+    \item[Households]:
+        The number of households is determined by the average size of a household in the reference profile and the total population size.
+        These generated households are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
     \item[K-12 Schools]:
@@
         The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
-        These generated schools are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
+        The assignment is analogous to that of households.
     \item[Colleges]:
@@
     \item[Workplaces]:
-        The assignment of workplaces is analogous to that of K-12 schools, but now we account for commuting information to determine the actual number of workers in a location.
+        The assignment of workplaces is analogous to that of households, but now we account for commuting information to determine the actual number of workers in a location.
         We find this amount by the working people who live there plus the people that commute to this location minus the ones that live there but commute away.
@@
         We create both primary and secondary communities, each containing 2000 persons from all ages and occupations.
-        The assignement is analogous to that of K-12 schools.
-    \item[Households]:
-        The number of households is determined by the average size of a household in the reference profile and the total population size.
-        The assignement is again analogous to that of K-12 schools.
+        The assignment is again analogous to that of households.
 \end{description}
@@
 \label{subsection:genpop}
-TODO
+After creating the structures that will allow people to come in contact with each other and spread possible infections, we have create the population itself and determine the different ContactPools they will be in.
+The persons are created based on the Household profiles in the HouseholdPopulator.
+Analogous to the creation of the ContactCenters, we have a partial populator that will populate its own type of ContactPool:
+
+\begin{description}
+    \item[Households]:
+        To create the actual persons, we draw a random household from the list of sample households and use that as a template for the number of members and their ages.
+        We simply do this for each household in the GeoGrid, since we already determined the locations and amount of households while generating the geography.
+    \item[K-12 Schools]:
+        We start by finding all schools within a 10km radius of the household location. If this list is empty, we double this searching radius until it's no longer empty.
+        We then choose a random ContactPool from the combined list of ContactPools in the found schools, even if this ContactPool now has more students than average (20).
+    \item[Colleges]:
+        The students who study ``close to home" are assigned to a college in a way analogous to the assignment to K-12 schools.
+        For the ones that study further from home we first determine the list of locations where people from this locations commute to and choose one of these locations by use of a discrete distribution based on the relative commuting information.
+        After we have chosen a location, we randomly choose a ContactPool at a college this location and assign it to the commuting student.
+    \item[Workplaces]:
+        We first decide if the person actually has a job based on the unemployment parameter.
+        We assign a workplace to an active worker that works ``close to home" in an analogous way as the assignment of K-12 schools to students.
+        For the commuting workers we use a technique analogous to that of the commuting college students.
+    \item[Communities]:
+        The communities we can choose from at a location is determined in an analogous way to the K-12 schools.
+        In primary communities we simply choose a random ContactPool from the list of Communities for each person in a household.
+        In secondary communities however, we assign complete households to the ContactPools instead of each person in the household separately to a ContactPool.
+
+\end{description}
 

### 2018-08-23 doc/latex/02-Software.tex
Add section about protobuf

@@
 \label{section:protobuf}
-TODO
+
+Protocol Buffers\footnote{\url{https://developers.google.com/protocol-buffers/}} is a library used for serializing structured data.
+We use it to read and write the population generated by GenGeoPop (see \ref{section:gengeopop}).
+It uses an interface description language that describes the structure of the data we want to store, in this case the GeoGrid.
+The file that describes how the GeoGrid is structured inside the generated binary file is located at:
+\texttt{main/cpp/gengeopop/io/proto/geogrid.proto}
+This file is then used to generate the C++ code necessary to read and write our GeoGrid in the structure we provided.
+We include this generated code in the project so it's not necessary to install the \texttt{protobuf-c} package\footnote{\url{https://github.com/protobuf-c/protobuf-c}} in order to compile Stride.
+These generated source files can be found in the same folder.
+If you want to change the structure, for example due to changes in the way the population is generated, you will need to install the previously mentioned package and generate the necessary code again.
+To make it easier to do this, we provided a CMake parameter and target that will generate the code and copy it to the source directory respectively.
+For this to work, Stride needs to be compiled using the ``\texttt{STRIDE\_GEN\_PROTO=true}" argument.
+This will generate the code based on the \texttt{geogrid.proto} file and use that instead of the version included in the source directory.
+If you then want to copy this code to the correct location in the source, you can use ``\texttt{make proto}".
+If the version of \texttt{protobuf-c} you're using is significantly newer than the one included in this repository, you might also need to update the files stored \texttt{main/resources/lib/protobuf}.
+
+The classes that are responsible for reading and writing a GeoGrid to an \texttt{istream} containing the serialized data are the \texttt{GeoGridProtoReader} and \texttt{GeoGridProtoWriter} respectively.

### 2018-08-26 doc/latex/04-Code.tex
Fix some typos in manual

@@
 A fraction of college students will attend a college ``close to home'' and the others will attend a college ``far from home''.
-        Most educations don't last for 8 years, but using this number we compensate for changes in the field of study, doctoral studies, advanced masters and repeating a failed year of study.
+        Most higher educations don't last for 8 years, but using this number we compensate for changes in the field of study, doctoral studies, advanced masters and repeating a failed year of study.
     \item[Employable]:
-        We consider people of ages 18 to 65 as employable. A fraction of people between 18 and 26 will attend a college, and the complementary fraction will be employable.
+        We consider people of ages 18 to 65 to be employable. A fraction of people between 18 and 26 will attend a college, and the complementary fraction will be employable.
     \item[Active population]:
@@
 \label{subsection:gengeo}
-We start by generating the geographical component, we call this a GeoGrid.
+We start by generating the geographical component, a GeoGrid.
 This contains locations with an id, name, province, coordinates and nominative population figures.
@@
         The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
-        The assignment is analogous to that of households.
+        The assignment of the schools to the locations is analogous to that of households.
     \item[Colleges]:
@@
         For the ones that study further from home we first determine the list of locations where people from this locations commute to and choose one of these locations by use of a discrete distribution based on the relative commuting information.
-        After we have chosen a location, we randomly choose a ContactPool at a college this location and assign it to the commuting student.
+        After we have chosen a location, we randomly choose a ContactPool at a college in this location and assign it to the commuting student.
     \item[Workplaces]:

### 2018-09-02 doc/latex/03-Simulator.tex
Add documentation for GenPop in manual
Remove support for Sub-municipalities

@@
         \item $wallonia\_cities.csv$: Walloon cities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Waals\_Gewest}}.
-        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Vlaams\_Gewest}}.
         \end{itemize}
@@
         The file to read the cities from.
-    \item[\texttt{--subMinicipalities}] \ \\
-        The file to read the sub-municipalities from.
     \item[\texttt{--output}] \ \\
@@
     \item[\texttt{--seed}] \ \\
-        The seed to be used for the random engine. The default is \texttt{0}.
+        The seed to be used for the random engine. The default is \texttt{"1,2,3,4"}.
     \item[\texttt{--loglevel}] \ \\
@@
 To open a GeoGrid use the menu option \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
-The circular markers indicate a city or sub-municipality. The square markers indicate the ``parent'' city of sub-municipalities, they don't have a population.
-By clicking on the square marker, all the sub-municipalities will be selected.
+The circular markers indicate a city.
 When one ore more cities is selected the details are shown in the right sidebar.

### 2018-09-02 main/cpp/gengeopop/GenGeoPopController.cpp

@@ -20,12 +20,11 @@ namespace gengeopop {
 GenGeoPopController::GenGeoPopController(std::shared_ptr<spdlog::logger> logger, GeoGridConfig& geoGridConfig,
                                          stride::util::RnMan& rnManager, std::string citiesFileName,
                                          std::string commutingFileName, std::string householdFileName,
-                                         std::string subMunicipalitiesFileName, std::string regionName)
+                                         std::string regionName)
     : m_geoGridConfig(geoGridConfig), m_rnManager(rnManager), m_geoGrid(nullptr), m_population(nullptr),
-      m_citiesReader(nullptr), m_commutesReader(nullptr), m_householdsReader(nullptr),
-      m_subMunicipalitiesReader(nullptr), m_logger(std::move(logger)), m_citiesFileName(std::move(citiesFileName)),
-      m_commutingFileName(std::move(commutingFileName)), m_householdsFileName(std::move(householdFileName)),
-      m_subMunicipalitiesFileName(std::move(subMunicipalitiesFileName)), m_regionId(0), m_regionName(regionName)
+      m_citiesReader(nullptr), m_commutesReader(nullptr), m_householdsReader(nullptr), m_logger(std::move(logger)),
+      m_citiesFileName(std::move(citiesFileName)), m_commutingFileName(std::move(commutingFileName)),
+      m_householdsFileName(std::move(householdFileName)), m_regionId(0), m_regionName(regionName)
 {
 }
 
@@ -60,10 +59,6 @@ void GenGeoPopController::ReadDataFiles()
                 }
         }
 
-        if (m_subMunicipalitiesFileName != "") {
-                m_subMunicipalitiesReader = readerFactory.CreateSubMunicipalitiesReader(m_subMunicipalitiesFileName);
-                m_subMunicipalitiesReader->FillGeoGrid(m_geoGrid);
-        }
         if (m_commutingFileName != "") {
                 m_commutesReader->FillGeoGrid(m_geoGrid);
         }

### 2018-09-02 main/cpp/gengeopop/GenGeoPopController.h

@@ -2,7 +2,6 @@
 
 #include "GeoGridConfig.h"
 #include <gengeopop/io/CommutesReader.h>
-#include <gengeopop/io/SubMunicipalitiesReader.h>
 #include <spdlog/logger.h>
 #include <util/RnMan.h>
 
@@ -17,8 +16,7 @@ public:
         /// Create a GenGeoPopController
         GenGeoPopController(std::shared_ptr<spdlog::logger> logger, GeoGridConfig& geoGridConfig,
                             stride::util::RnMan& rnManager, std::string citiesFileName, std::string commutingFileName,
-                            std::string householdFileName, std::string subMunicipalitiesFileName,
-                            std::string regionName);
+                            std::string householdFileName, std::string regionName);
 
         /// Reads the data files
         void ReadDataFiles();
@@ -44,19 +42,16 @@ private:
 
         std::shared_ptr<stride::Population> m_population; ///< The generated GeoGrid
 
-        std::shared_ptr<CitiesReader>            m_citiesReader;            ///< The CitiesReader
-        std::shared_ptr<CommutesReader>          m_commutesReader;          ///< The CommutesReader
-        std::shared_ptr<HouseholdReader>         m_householdsReader;        ///< The HouseholdsReader
-        std::shared_ptr<SubMunicipalitiesReader> m_subMunicipalitiesReader; ///< The SubMunicipalitiesReader
-        std::shared_ptr<spdlog::logger>          m_logger;                  ///< The logger used
+        std::shared_ptr<CitiesReader>    m_citiesReader;     ///< The CitiesReader
+        std::shared_ptr<CommutesReader>  m_commutesReader;   ///< The CommutesReader
+        std::shared_ptr<HouseholdReader> m_householdsReader; ///< The HouseholdsReader
+        std::shared_ptr<spdlog::logger>  m_logger;           ///< The logger used
 
         std::string m_citiesFileName;     ///< Filename of the file which stores information about the cities
         std::string m_commutingFileName;  ///< Filename of the file which stores information about the commutes
         std::string m_householdsFileName; ///< Filename of the file which stores information about the households
-        std::string
-                    m_subMunicipalitiesFileName; ///< Filename of the file which stores information about the submunicipalities
-        std::size_t m_regionId;                  ///< RegionId, used to create persons
-        std::string m_regionName;                ///< RegionName
+        std::size_t m_regionId;           ///< RegionId, used to create persons
+        std::string m_regionName;         ///< RegionName
 };
 
 } // namespace gengeopop

### 2018-09-02 main/cpp/gengeopop/Location.cpp

@@ -7,7 +7,7 @@ namespace gengeopop {
 Location::Location(unsigned int id, unsigned int province, Coordinate coordinate, std::string name)
     : m_id(id), m_name(std::move(name)), m_province(province), m_population(0), m_relativePopulation(0.0),
       m_coordinate(coordinate), m_contactCenters(), m_incomingCommutingLocations(), m_outgoingCommutingLocations(),
-      m_subMunicipalities(), m_parent(nullptr), m_contactCenterByType()
+      m_contactCenterByType()
 {
 }
 
@@ -70,25 +70,6 @@ unsigned int Location::GetSimulationPopulation() const
         return population;
 }
 
-double Location::GetInfectedRatioOfSubmunicipalities() const
-{
-        unsigned int infected   = 0;
-        unsigned int population = 0;
-        for (auto loc : m_subMunicipalities) {
-                for (const std::shared_ptr<gengeopop::ContactCenter>& cc : loc->GetContactCenters()) {
-                        auto r = cc->GetPopulationAndInfectedCount();
-                        population += r.first;
-                        infected += r.second;
-                }
-        }
-
-        if (population == 0) {
-                return 0;
-        }
-
-        return static_cast<double>(infected) / static_cast<double>(population);
-}
-
 const std::vector<std::shared_ptr<ContactCenter>>& Location::GetContactCenters() const { return m_contactCenters; }
 
 const Coordinate& Location::GetCoordinate() const { return m_coordinate; }
@@ -143,8 +124,6 @@ int Location::OutGoingCommutingPeople(double fractionOfPopulationCommuting) cons
 
 bool Location::operator==(const Location& other) const
 {
-        auto        sub1 = GetSubMunicipalities();
-        const auto& sub2 = other.GetSubMunicipalities();
 
         using boost::geometry::get;
         return GetID() == other.GetID() && get<0>(GetCoordinate()) == get<0>(other.GetCoordinate()) &&
@@ -152,14 +131,7 @@ bool Location::operator==(const Location& other) const
                GetProvince() == other.GetProvince() && GetPopulation() == other.GetPopulation() &&
                GetContactCenters() == other.GetContactCenters() &&
                GetIncomingCommuningCities() == other.GetIncomingCommuningCities() &&
-               GetOutgoingCommuningCities() == other.GetOutgoingCommuningCities() &&
-               ((!GetParent() && !other.GetParent()) ||
[…]

### 2018-09-02 main/cpp/gengeopop/Location.h

@@ -67,9 +67,6 @@ public:
         /// Gets the amount of people infected in the contactpools of this location
         double GetInfectedCount() const;
 
-        /// Gets the ratio of infected persons in all contactPools of this location's subMunicipalities
-        double GetInfectedRatioOfSubmunicipalities() const;
-
         /// Given the total population calculates this location's population using the relative population of this
         /// location
         void CalculatePopulation(unsigned int totalPopulation);
@@ -79,9 +76,6 @@ public:
 
         /// Gets the relative population
         double GetRelativePopulationSize() const;
-
-        //// Gets the sum of the population of all sub municipalities
-        unsigned int GetPopulationOfSubmunicipalities() const;
 
         /// Gets a vector with the outgoing cities which people are commuting to + the proportion
         const std::vector<std::pair<std::shared_ptr<Location>, double>>& GetIncomingCommuningCities() const;
@@ -106,18 +100,6 @@ public:
 
         /// Gets the absolute amount of people going to this location
         int IncomingCommutingPeople(double fractionOfPopulationCommuting) const;
-
-        /// Add a sub-municipality to this location
-        void AddSubMunicipality(std::shared_ptr<Location> location);
-
-        /// Gets the sub-municipalities of this location
-        const std::set<std::shared_ptr<Location>>& GetSubMunicipalities() const;
-
-        /// Sets the parent of this sub-municipality, requires that this location doesn't have any sub-municipality
-        void SetParent(const std::shared_ptr<Location>& location);
-
-        /// Gets the parent of this sub-municipality
-        std::shared_ptr<Location> GetParent() const;
 
         /// Gets the Coordinate of this location
         const Coordinate& GetCoordinate() const;
@@ -147,10 +129,6 @@ private:
         std::vector<std::pair<std::shared_ptr<Location>, double>> m_incomingCommutingLocations;
         ///< Outgoing commutes stored as pair of location and proportion relative to the this location
         std::vector<std::pair<std::shared_ptr<Location>, double>> m_outgoingCommutingLocations;
-        std::set<std::shared_ptr<Location>>
-            m_subMunicipalities; ///< Set of sub-municipalties, must be empty when m_parent is set
-        std::shared_ptr<Location>
-            m_parent; ///< Parent of this sub-municipality, must be nullptr when m_subMunicipalities is et
         std::unordered_map<std::type_index, std::vector<std::shared_ptr<ContactCenter>>>
             m_contactCenterByType; ///< Stores the contact centers indexed by their type
 };

### 2018-09-02 main/cpp/gengeopop/io/CommutesCSVReader.cpp

@@ -10,52 +10,6 @@ CommutesCSVReader::CommutesCSVReader(std::unique_ptr<std::istream> inputStream)
 {
 }
 
-double CommutesCSVReader::MunicipalityTotal(std::shared_ptr<Location> loc) const
-{
-        double total = 0;
-        for (const auto& sub : loc->GetSubMunicipalities()) {
-                total += sub->GetRelativePopulationSize();
-        }
-        return total;
-}
-
-void CommutesCSVReader::AddCommute(std::shared_ptr<Location> from, std::shared_ptr<Location> to,
-                                   double proportion) const
-{
-        from->AddOutgoingCommutingLocation(to, proportion);
-        to->AddIncomingCommutingLocation(from, proportion);
-}
-
-void CommutesCSVReader::AddCommuteFrom(std::shared_ptr<Location> from, std::shared_ptr<Location> to,
-                                       double proportion) const
-{
-        if (from->GetSubMunicipalities().size()) {
-                for (auto& subMunicipalityFrom : from->GetSubMunicipalities()) {
-                        AddCommuteTo(subMunicipalityFrom, to, proportion);
-                }
-        } else {
-                AddCommuteTo(from, to, proportion);
-        }
-}
-void CommutesCSVReader::AddCommuteTo(std::shared_ptr<Location> from, std::shared_ptr<Location> to,
-                                     double proportion) const
-{
-        double total_population = MunicipalityTotal(to);
-        if (to->GetSubMunicipalities().size()) {
-                if (total_population > 0) {
-                        double total_added = 0;
-                        for (auto& subMunicipalityTo : to->GetSubMunicipalities()) {
-                                double prop =
-                                    proportion * (subMunicipalityTo->GetRelativePopulationSize() / total_population);
-                                total_added += prop;
-                                AddCommute(from, subMunicipalityTo, prop);
-                        }
-                        assert(std::abs(total_added - proportion) < 0.01);
-                }
-        } else {
-                AddCommute(from, to, proportion);
-        }
-}
 void CommutesCSVReader::FillGeoGrid(std::shared_ptr<GeoGrid> geoGrid) const
 {
         // cols:
@@ -99,7 +53,8 @@ void CommutesCSVReader::FillGeoGrid(std::shared_ptr<GeoGrid> geoGrid) const
                                             "Proportion of commutes from " + std::to_string(locFrom->GetID()) + " to " +
                                             std::to_string(locTo->GetID()) + " is invalid (0 <= proportion <= 1)");
[…]

### 2018-09-02 main/cpp/gengeopop/io/CommutesCSVReader.h

@@ -21,18 +21,8 @@ public:
         void FillGeoGrid(std::shared_ptr<GeoGrid> geoGrid) const override;
 
 private:
-        /// Find the relative total populution in the submunicipalities. If it doesn't have any, it will return 0.
-        double MunicipalityTotal(std::shared_ptr<Location> loc) const;
-
         /// Add the provided commute symmetrically to the locations
         void AddCommute(std::shared_ptr<Location> from, std::shared_ptr<Location> to, double proportion) const;
-
-        /// Add commutes by splitting the 'from' into submunicipalities if necessary.
-        // This will call AddCommuteTo with the submunicipality and the provided 'to'.
-        void AddCommuteFrom(std::shared_ptr<Location> from, std::shared_ptr<Location> to, double proportion) const;
-
-        /// Add commutes by splitting the 'to' into submunicipalities if necessary.
-        void AddCommuteTo(std::shared_ptr<Location> from, std::shared_ptr<Location> to, double proportion) const;
 
         stride::util::CSV m_reader; ///< The pure CSV reader
 };

### 2018-09-02 main/cpp/gengeopop/io/GeoGridJSONReader.cpp

@@ -67,11 +67,9 @@ std::shared_ptr<GeoGrid> GeoGridJSONReader::Read()
 #pragma omp taskwait
         }
         e->Rethrow();
-        AddSubMunicipalities(m_geoGrid);
         AddCommutes(m_geoGrid);
         m_commutes.clear();
         m_people.clear();
-        m_subMunicipalities.clear();
         return m_geoGrid;
 } // namespace gengeopop
 
@@ -104,12 +102,6 @@ std::shared_ptr<Location> GeoGridJSONReader::ParseLocation(boost::property_tree:
 #pragma omp taskwait
         }
         e->Rethrow();
-
-        for (const auto& subMun : location.get_child("submunicipalities")) {
-#pragma omp critical
-                m_subMunicipalities.emplace_back(id,
-                                                 boost::lexical_cast<unsigned int>(subMun.second.get_child("").data()));
-        }
 
         if (location.count("commutes")) {
                 boost::property_tree::ptree commutes = location.get_child("commutes");

### 2018-09-02 main/cpp/gengeopop/io/GeoGridJSONWriter.cpp

@@ -86,14 +86,6 @@ boost::property_tree::ptree GeoGridJSONWriter::WriteLocation(std::shared_ptr<Loc
         }
         location_root.add_child("contactCenters", contactCenters);
 
-        boost::property_tree::ptree subMunicipalities;
-        for (const auto& subMunicipality : location->GetSubMunicipalities()) {
-                boost::property_tree::ptree person_root;
-                person_root.put("", subMunicipality->GetID());
-                subMunicipalities.push_back(std::make_pair("", person_root));
-        }
-        location_root.add_child("submunicipalities", subMunicipalities);
-
         return location_root;
 }
 

### 2018-09-02 main/cpp/gengeopop/io/GeoGridProtoReader.cpp

@@ -66,10 +66,8 @@ std::shared_ptr<GeoGrid> GeoGridProtoReader::Read()
         }
         e->Rethrow();
         AddCommutes(m_geoGrid);
-        AddSubMunicipalities(m_geoGrid);
         m_people.clear();
         m_commutes.clear();
-        m_subMunicipalities.clear();
         return m_geoGrid;
 } // namespace gengeopop
 
@@ -108,10 +106,6 @@ std::shared_ptr<Location> GeoGridProtoReader::ParseLocation(const proto::GeoGrid
                 m_commutes.emplace_back(std::make_tuple(id, commute.to(), commute.proportion()));
         }
 
-        for (int idx = 0; idx < protoLocation.submunicipalities_size(); idx++) {
-#pragma omp critical
-                m_subMunicipalities.emplace_back(std::make_pair(result->GetID(), protoLocation.submunicipalities(idx)));
-        }
         return result;
 } // namespace gengeopop
 

### 2018-09-02 main/cpp/gengeopop/io/GeoGridProtoWriter.cpp

@@ -49,9 +49,6 @@ void GeoGridProtoWriter::WriteLocation(std::shared_ptr<Location> location, proto
         for (const auto& contactCenter : *location) {
                 WriteContactCenter(contactCenter, protoLocation->add_contactcenters());
         }
-        for (const auto& subMunicipality : location->GetSubMunicipalities()) {
-                protoLocation->add_submunicipalities(subMunicipality->GetID());
-        }
 }
 
 void GeoGridProtoWriter::WriteCoordinate(const Coordinate&                   coordinate,

### 2018-09-02 main/cpp/gengeopop/io/GeoGridReader.cpp

@@ -3,16 +3,8 @@
 namespace gengeopop {
 
 GeoGridReader::GeoGridReader(std::unique_ptr<std::istream> inputStream)
-    : m_people(), m_commutes(), m_subMunicipalities(), m_regionId(0), m_regionName("Default"),
-      m_inputStream(std::move(inputStream))
+    : m_people(), m_commutes(), m_regionId(0), m_regionName("Default"), m_inputStream(std::move(inputStream))
 {
-}
-
-void GeoGridReader::AddSubMunicipalities(std::shared_ptr<GeoGrid> geoGrid)
-{
-        for (const auto& subMunTuple : m_subMunicipalities) {
-                geoGrid->GetById(subMunTuple.first)->AddSubMunicipality(geoGrid->GetById(subMunTuple.second));
-        }
 }
 void GeoGridReader::AddCommutes(std::shared_ptr<GeoGrid> geoGrid)
 {

### 2018-09-02 main/cpp/gengeopop/io/GeoGridReader.h

@@ -27,16 +27,12 @@ public:
                            std::string regionName);
 
 protected:
-        /// Add the SubMunicipalities that were found while looping of the Locations to their parent municipality
-        void AddSubMunicipalities(std::shared_ptr<GeoGrid> geoGrid);
-
         /// Add the commutes that were found to their respective Locations symmetrically
         void AddCommutes(std::shared_ptr<GeoGrid> geoGrid);
 
         std::map<unsigned int, stride::Person*>
                                                                     m_people; ///< Store the persons (id->person) that were found while loping over the ContactPools
-        std::vector<std::tuple<unsigned int, unsigned int, double>> m_commutes;          ///< from, to, amount
-        std::vector<std::pair<unsigned int, unsigned int>>          m_subMunicipalities; //// first has submun second
+        std::vector<std::tuple<unsigned int, unsigned int, double>> m_commutes; ///< from, to, amount
         std::size_t                                                 m_regionId; ///< RegionId, used to create persons
         std::string m_regionName; ///< RegionName, region name passed to GeoGrid
 

### 2018-09-02 main/cpp/gengeopop/io/ReaderFactory.cpp

@@ -2,7 +2,6 @@
 #include "CitiesCSVReader.h"
 #include "CommutesCSVReader.h"
 #include "HouseholdCSVReader.h"
-#include "SubMunicipalitiesCSVReader.h"
 #include <iostream>
 #include <util/Exception.h>
 #include <util/FileSys.h>
@@ -37,16 +36,6 @@ std::shared_ptr<HouseholdReader> ReaderFactory::CreateHouseholdReader(const std:
 std::shared_ptr<HouseholdReader> ReaderFactory::CreateHouseholdReader(const std::filesystem::path& path)
 {
         return std::make_shared<HouseholdCSVReader>(OpenFile(path));
-}
-
-std::shared_ptr<SubMunicipalitiesReader> ReaderFactory::CreateSubMunicipalitiesReader(const std::string& filename)
-{
-        return CreateSubMunicipalitiesReader(stride::util::FileSys::GetDataDir() / std::filesystem::path(filename));
-}
-
-std::shared_ptr<SubMunicipalitiesReader> ReaderFactory::CreateSubMunicipalitiesReader(const std::filesystem::path& path)
-{
-        return std::make_shared<SubMunicipalitiesCSVReader>(OpenFile(path));
 }
 
 std::unique_ptr<std::istream> ReaderFactory::OpenFile(const std::filesystem::path& path) const

### 2018-09-02 main/cpp/gengeopop/io/ReaderFactory.h

@@ -2,7 +2,6 @@
 #include "CitiesReader.h"
 #include "CommutesReader.h"
 #include "HouseholdReader.h"
-#include "SubMunicipalitiesReader.h"
 
 #if __has_include(<filesystem>)
 #include <filesystem>
@@ -42,12 +41,6 @@ public:
 
         /// Create a HouseholdReader based on an absolute Boost Filesystem Path pointing to the input file
         std::shared_ptr<HouseholdReader> CreateHouseholdReader(const std::filesystem::path& path);
-
-        /// Create a SubMunicipalitiesReader based on the filename of the input file, relative to the data directory
-        std::shared_ptr<SubMunicipalitiesReader> CreateSubMunicipalitiesReader(const std::string& filename);
-
-        /// Create a SubMunicipalitiesReader based on an absolute Boost Filesystem Path pointing to the input file
-        std::shared_ptr<SubMunicipalitiesReader> CreateSubMunicipalitiesReader(const std::filesystem::path& path);
 
 private:
         /// Create an istream based on the provided Boost Filesystem Path

### 2018-09-02 main/cpp/gengeopop/io/SubMunicipalitiesCSVReader.cpp

@@ -1,43 +1,0 @@
-#include "SubMunicipalitiesCSVReader.h"
-#include "../../util/CSV.h"
-#include "../../util/CSVRow.h"
-#include <iostream>
-
-namespace gengeopop {
-
-SubMunicipalitiesCSVReader::SubMunicipalitiesCSVReader(std::unique_ptr<std::istream> inputStream)
-    : SubMunicipalitiesReader(std::move(inputStream)), m_reader(*(m_inputStream.get()))
-{
-}
-
-void SubMunicipalitiesCSVReader::FillGeoGrid(std::shared_ptr<GeoGrid> geoGrid) const
-{
-        // columns: parent_id,id,parent_is_sub,population_rel_to_parent,latitude,longitude,name
-
-        // first build a list of relative population sizes of each Location
-        std::map<unsigned int, double> populationSizesMapping;
-
-        for (const auto& loc : *geoGrid) {
-                populationSizesMapping[loc->GetID()] = loc->GetRelativePopulationSize();
-        }
-
-        for (const stride::util::CSVRow& row : m_reader) {
-                auto parentId = row.GetValue<unsigned int>(0);
-                auto id       = row.GetValue<unsigned int>(1);
-                auto parent   = geoGrid->GetById(parentId);
-
-                parent->SetRelativePopulation(0);
-                auto location = std::make_shared<Location>(id,                                           // id
-                                                           parent->GetProvince(),                        // province
-                                                           Coordinate(row.GetValue<double>("longitude"), // longtitude
-                                                                      row.GetValue<double>("latitude")   // latitude
-                                                                      ),
-                                                           row.GetValue(5));
-                location->SetRelativePopulation(row.GetValue<double>("population_rel_to_parent") *
-                                                populationSizesMapping[parentId]);
-                parent->AddSubMunicipality(location);
-                location->SetParent(parent);
-                geoGrid->AddLocation(location);
-        }
-}
-} // namespace gengeopop

### 2018-09-02 main/cpp/gengeopop/io/SubMunicipalitiesCSVReader.h

@@ -1,23 +1,0 @@
-#pragma once
-
-#include "SubMunicipalitiesReader.h"
-#include <util/CSV.h>
-
-namespace gengeopop {
-
-/**
- * Create a Reader which fills a GeoGrid with the SubMunicipalities found in a given CSV file
- */
-class SubMunicipalitiesCSVReader : public SubMunicipalitiesReader
-{
-public:
-        /// Construct the SubMunicipalitiesCSVReader with an istream containing the CSV data
-        explicit SubMunicipalitiesCSVReader(std::unique_ptr<std::istream> inputStream);
-
-        /// Add the found SubMunicipalities to the provided GeoGrid
-        void FillGeoGrid(std::shared_ptr<GeoGrid> geoGrid) const override;
-
-private:
-        stride::util::CSV m_reader; ///< The pure CSV reader
-};
-} // namespace gengeopop

### 2018-09-02 main/cpp/gengeopop/io/SubMunicipalitiesReader.cpp

@@ -1,10 +1,0 @@
-#include "SubMunicipalitiesReader.h"
-
-namespace gengeopop {
-
-SubMunicipalitiesReader::SubMunicipalitiesReader(std::unique_ptr<std::istream> inputStream)
-    : m_inputStream(std::move(inputStream))
-{
-}
-
-} // namespace gengeopop

### 2018-09-02 main/cpp/gengeopop/io/SubMunicipalitiesReader.h

@@ -1,28 +1,0 @@
-#pragma once
-
-#include <gengeopop/GeoGrid.h>
-#include <gengeopop/Location.h>
-#include <map>
-#include <string>
-
-namespace gengeopop {
-/**
- * Create an abstract Reader which fills a GeoGrid with the SubMunicipalities found in a given file.
- * This can be implemented using different input file types. Currently CSV is implemented.
- */
-class SubMunicipalitiesReader
-{
-public:
-        /// Construct the SubMunicipalitiesReader with an istream containing the file content
-        explicit SubMunicipalitiesReader(std::unique_ptr<std::istream> inputStream);
-
-        /// Add the found SubMunicipalities to the provided GeoGrid
-        virtual void FillGeoGrid(std::shared_ptr<GeoGrid>) const = 0;
-
-        /// Default constructor
-        virtual ~SubMunicipalitiesReader() = default;
-
-protected:
-        std::unique_ptr<std::istream> m_inputStream; ///< The istream containing the file content
-};
-} // namespace gengeopop

### 2018-09-02 main/cpp/gengeopop/io/proto/geogrid.pb.cc

@@ -7,7 +7,6 @@
 
 #include <google/protobuf/stubs/common.h>
 #include <google/protobuf/stubs/port.h>
-#include <google/protobuf/stubs/once.h>
 #include <google/protobuf/io/coded_stream.h>
 #include <google/protobuf/wire_format_lite_inl.h>
 #include <google/protobuf/descriptor.h>
@@ -19,6 +18,15 @@
 #include "third_party/protobuf/version.h"
 #endif
 // @@protoc_insertion_point(includes)
+
+namespace protobuf_geogrid_2eproto {
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<0> scc_info_GeoGrid_Location_Commute;
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<0> scc_info_GeoGrid_Location_ContactCenter_ContactPool;
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<0> scc_info_GeoGrid_Location_Coordinate;
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<0> scc_info_GeoGrid_Person;
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<1> scc_info_GeoGrid_Location_ContactCenter;
+extern PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto ::google::protobuf::internal::SCCInfo<3> scc_info_GeoGrid_Location;
+}  // namespace protobuf_geogrid_2eproto
 namespace proto {
 class GeoGrid_Location_CoordinateDefaultTypeInternal {
  public:
@@ -57,14 +65,9 @@ class GeoGridDefaultTypeInternal {
 } _GeoGrid_default_instance_;
 }  // namespace proto
 namespace protobuf_geogrid_2eproto {
-void InitDefaultsGeoGrid_Location_CoordinateImpl() {
+static void InitDefaultsGeoGrid_Location_Coordinate() {
   GOOGLE_PROTOBUF_VERIFY_VERSION;
 
[…]

### 2018-09-02 main/cpp/gengeopop/io/proto/geogrid.pb.h

@@ -1,19 +1,19 @@
 // Generated by the protocol buffer compiler.  DO NOT EDIT!
 // source: geogrid.proto
 
-#ifndef PROTOBUF_geogrid_2eproto__INCLUDED
-#define PROTOBUF_geogrid_2eproto__INCLUDED
+#ifndef PROTOBUF_INCLUDED_geogrid_2eproto
+#define PROTOBUF_INCLUDED_geogrid_2eproto
 
 #include <string>
 
 #include <google/protobuf/stubs/common.h>
 
-#if GOOGLE_PROTOBUF_VERSION < 3005000
+#if GOOGLE_PROTOBUF_VERSION < 3006001
 #error This file was generated by a newer version of protoc which is
 #error incompatible with your Protocol Buffer headers.  Please update
 #error your headers.
 #endif
-#if 3005001 < GOOGLE_PROTOBUF_MIN_PROTOC_VERSION
+#if 3006001 < GOOGLE_PROTOBUF_MIN_PROTOC_VERSION
 #error This file was generated by an older version of protoc which is
 #error incompatible with your Protocol Buffer headers.  Please
 #error regenerate this file with a newer version of protoc.
@@ -24,6 +24,7 @@
 #include <google/protobuf/arenastring.h>
 #include <google/protobuf/generated_message_table_driven.h>
 #include <google/protobuf/generated_message_util.h>
+#include <google/protobuf/inlined_string_field.h>
 #include <google/protobuf/metadata.h>
 #include <google/protobuf/message.h>
 #include <google/protobuf/repeated_field.h>  // IWYU pragma: export
@@ -31,6 +32,7 @@
 #include <google/protobuf/generated_enum_reflection.h>
 #include <google/protobuf/unknown_field_set.h>
 // @@protoc_insertion_point(includes)
+#define PROTOBUF_INTERNAL_EXPORT_protobuf_geogrid_2eproto 
 
 namespace protobuf_geogrid_2eproto {
 // Internal implementation detail -- do not use these members.
@@ -43,29 +45,6 @@ struct TableStruct {
   static const ::google::protobuf::uint32 offsets[];
 };
 void AddDescriptors();
-void InitDefaultsGeoGrid_Location_CoordinateImpl();
-void InitDefaultsGeoGrid_Location_Coordinate();
-void InitDefaultsGeoGrid_Location_ContactCenter_ContactPoolImpl();
-void InitDefaultsGeoGrid_Location_ContactCenter_ContactPool();
[…]

### 2018-09-02 main/cpp/gengeopop/main.cpp

@@ -71,9 +71,6 @@ int main(int argc, char* argv[])
                 ValueArg<unsigned int> populationSize("p", "populationSize", "Population size", false, 6000000,
                                                       "POPULATION SIZE", cmd);
 
-                ValueArg<std::string> subMunicipalitiesFile("x", "subMinicipalities", "subMinicipalitiesFile", false,
-                                                            "submunicipalities.csv", "OUTPUT FILE", cmd);
-
                 ValueArg<std::string> rng_seed("", "seed", "The seed to be used for the random engine", false,
                                                "1,2,3,4", "SEED", cmd);
 
@@ -110,8 +107,7 @@ int main(int argc, char* argv[])
                 stride::util::RnMan       rnManager(info);
 
                 GenGeoPopController genGeoPopController(logger, geoGridConfig, rnManager, citiesFile.getValue(),
-                                                        commutingFile.getValue(), houseHoldFile.getValue(),
-                                                        subMunicipalitiesFile.getValue(), "Default");
+                                                        commutingFile.getValue(), houseHoldFile.getValue(), "Default");
 
                 // --------------------------------------------------------------
                 // Read input files.

### 2018-09-02 main/cpp/guilauncher/Launcher.cpp

@@ -191,8 +191,6 @@ void Launcher::UpdateConfigForm()
                     "text", m_configPt.get<std::string>("run.geopop_gen.commuting_file").c_str());
                 m_configEditor.geopopHousehold->setProperty(
                     "text", m_configPt.get<std::string>("run.geopop_gen.household_file").c_str());
-                m_configEditor.geopopSubmunicipalities->setProperty(
-                    "text", m_configPt.get<std::string>("run.geopop_gen.submunicipalities_file").c_str());
         }
 }
 
@@ -314,8 +312,6 @@ void Launcher::UpdatePtree()
                                m_configEditor.geopopCommuting->property("text").toString().toStdString());
                 m_configPt.put("run.geopop_gen.household_file",
                                m_configEditor.geopopHousehold->property("text").toString().toStdString());
-                m_configPt.put("run.geopop_gen.submunicipalities_file",
-                               m_configEditor.geopopSubmunicipalities->property("text").toString().toStdString());
         }
 }
 
@@ -365,7 +361,6 @@ void Launcher::SetRootObject(QObject* rootObject)
         m_configEditor.geopopCities                  = rootObject->findChild<QObject*>("gengeopopCitiesFile");
         m_configEditor.geopopCommuting               = rootObject->findChild<QObject*>("gengeopopCommutingFile");
         m_configEditor.geopopHousehold               = rootObject->findChild<QObject*>("gengeopopHouseholdFile");
-        m_configEditor.geopopSubmunicipalities = rootObject->findChild<QObject*>("gengeopopSubmunicipalitiesFile");
 }
 
 void Launcher::LoadComboBox(QObject* comboBox, const char* value)

### 2018-09-02 main/cpp/guilauncher/Launcher.h

@@ -144,6 +144,5 @@ private:
                 QObject* geopopCities                  = nullptr;
                 QObject* geopopCommuting               = nullptr;
                 QObject* geopopHousehold               = nullptr;
-                QObject* geopopSubmunicipalities       = nullptr;
         } m_configEditor; ///< The form objects in the QML that store the config
 };

### 2018-09-02 main/cpp/mapviewer/backend.cpp

@@ -118,11 +118,9 @@ void Backend::PlaceMarkers()
         int i = 0;
         for (auto grid : m_grids) {
                 for (const std::shared_ptr<gengeopop::Location>& loc : *grid) {
-                        bool         selected = m_selection.find({i, loc->GetID()}) != m_selection.end();
-                        bool         special  = !loc->GetSubMunicipalities().empty();
-                        unsigned int population =
-                            special ? loc->GetPopulationOfSubmunicipalities() : loc->GetPopulation();
-                        PlaceMarker(loc->GetCoordinate(), i, loc->GetID(), population, selected, special);
+                        bool         selected   = m_selection.find({i, loc->GetID()}) != m_selection.end();
+                        unsigned int population = loc->GetPopulation();
+                        PlaceMarker(loc->GetCoordinate(), i, loc->GetID(), population, selected);
                 }
                 i++;
         }
@@ -149,15 +147,14 @@ void Backend::SetObjects(QObject* map)
         PlaceMarkers();
 }
 
-void Backend::PlaceMarker(gengeopop::Coordinate coordinate, int region, int id, unsigned int population, bool selected,
-                          bool specialmarker)
+void Backend::PlaceMarker(gengeopop::Coordinate coordinate, int region, int id, unsigned int population, bool selected)
 {
         using boost::geometry::get;
         QVariant returnVal;
         double   size = std::min(50.0, 10 + population * 0.0015);
         QMetaObject::invokeMethod(m_map, "addMarker", Qt::QueuedConnection, Q_ARG(QVariant, get<1>(coordinate)),
                                   Q_ARG(QVariant, get<0>(coordinate)), Q_ARG(QVariant, region), Q_ARG(QVariant, id),
-                                  Q_ARG(QVariant, size), Q_ARG(QVariant, selected), Q_ARG(QVariant, specialmarker));
+                                  Q_ARG(QVariant, size), Q_ARG(QVariant, selected));
         // Save the marker so we can edit it's color etc later
         SaveMarker(region, id, qvariant_cast<QObject*>(returnVal));
 }
@@ -237,21 +234,11 @@ void Backend::OnExtraMarkerClicked(int region, unsigned int idOfClicked)
 
 void Backend::ToggleSelectionOfLocation(int region, std::shared_ptr<gengeopop::Location> loc)
 {
-        const auto& subMun = loc->GetSubMunicipalities();
[…]

### 2018-09-02 main/cpp/mapviewer/backend.h

@@ -151,10 +151,8 @@ private:
 
         /**
          * Places a marker at the given coordinate
-         * @Param specialmarker Whether or not to display a special marker
          */
-        void PlaceMarker(gengeopop::Coordinate coordinate, int region, int id, unsigned int population, bool selected,
-                         bool specialmarker);
+        void PlaceMarker(gengeopop::Coordinate coordinate, int region, int id, unsigned int population, bool selected);
 
         /**
          * Places the markers on the map, according to the current checked boxes.

### 2018-09-02 main/cpp/pop/GenPopBuilder.cpp

@@ -67,15 +67,9 @@ shared_ptr<Population> GenPopBuilder::Build(std::shared_ptr<Population> pop, std
                 commutesFile = m_region_pt.get<std::string>("geopop_gen.commuting_file");
         }
 
-        std::string submunicipalitiesFile;
-        // Check if given
-        if (geopop_gen.count("submunicipalities_file") > 0) {
-                submunicipalitiesFile = m_region_pt.get<std::string>("geopop_gen.submunicipalities_file");
-        }
-
-        GenGeoPopController genGeoPopController(
-            stride_logger, geoGridConfig, m_rn_manager, m_region_pt.get<std::string>("geopop_gen.cities_file"),
-            commutesFile, m_region_pt.get<std::string>("geopop_gen.household_file"), submunicipalitiesFile, regionName);
+        GenGeoPopController genGeoPopController(stride_logger, geoGridConfig, m_rn_manager,
+                                                m_region_pt.get<std::string>("geopop_gen.cities_file"), commutesFile,
+                                                m_region_pt.get<std::string>("geopop_gen.household_file"), regionName);
 
         genGeoPopController.UsePopulation(pop, regionId);
 

### 2018-09-02 main/resources/submunicipality/city_spider.py

@@ -1,56 +1,0 @@
-import scrapy
-
-class CitySpider(scrapy.Spider):
-    name = "city"
-
-    start_urls = [
-        'https://nl.wikipedia.org/wiki/Lijst_van_gemeenten_in_het_Vlaams_Gewest',
-    ]
-
-    def parse_nis(self, response):
-        nis = response.xpath('//td/a[contains(text(),"NIS")]/../following-sibling::td[1]/text()').extract_first()
-        yield {'nis': nis,
-              'name': response.meta['parent_name'],
-              "coordinates": response.xpath('//td/a[contains(text(),"rdinaten")]/../following-sibling::td[1]//a/text()').extract_first()}
-
-    def parse(self, response):
-        for city in response.css('.wikitable > tbody > tr'):
-            item = {"parent_name": city.css('td:nth-child(1) > a::text').extract_first(),
-                    "parent_area": city.css('td:nth-child(4)::text').extract_first(),
-                    "parent_population": city.css('td:nth-child(5)::text').extract_first(),
-            }
-
-            nisUrl = city.css('td:nth-child(1) > a::attr(href)').extract_first()
-            if nisUrl is not None:
-                yield scrapy.Request(response.urljoin(nisUrl), callback=self.parse_nis, meta=item)
-
-            main = city.css('td:nth-child(6)::text').extract_first()
-
-            for deel in city.css('td:nth-child(6) > a::attr(href)').extract():
-                request = scrapy.Request(response.urljoin(deel), callback=self.parse_submunicipality)
-                request.meta['item'] = item
-                yield request
-
-            if main is not None:
-                name = main.replace(',', '').strip()
-                if name != "":
-
-                    mainItem = {
-                        "name": name,
-                        "main": True
-                    }
-
-                    yield mainItem
-
-    def parse_submunicipality(self, response):
-        item = response.meta['item']
-
-        item['child'] = {
-            "name": response.css('#firstHeading::text').extract_first(),
-            "area": response.xpath('//td/a[contains(text(),"Oppervlakte")]/../following-sibling::td[1]/text()').extract_first(),
-            "population": response.xpath('//td/a[contains(text(),"Inwoners")]/../following-sibling::td[1]/text()').extract_first(),
-            "coordinates": response.xpath('//td/a[contains(text(),"rdinaten")]/../following-sibling::td[1]//a/text()').extract_first(),
[…]

### 2018-09-02 main/resources/submunicipality/postprocess.py

@@ -1,152 +1,0 @@
-# coding=utf-8
-import csv
-import json
-import re
-import math
-from pprint import pprint
-
-input_data = json.load(open('output.json'))
-
-data = {}
-
-def parseCoordinate(coord):
-    lat_degree, lat_minute = coord.strip().split(' ')
-    lat_degree = lat_degree.strip()
-    lat_minute = lat_minute.strip()
-    return str(int(lat_degree) + int(lat_minute) / 60.0)
-
-
-# parse the scarped data
-for submunicipality in input_data:
-
-    if 'nis' in submunicipality:
-        continue
-
-    if 'main' in submunicipality and submunicipality['main']:
-        try:
-            data[submunicipality['name']]['has_main'] = True
-        except:
-            data[submunicipality['name']] = {'has_main': True, 'children': [], 'population': None}
-        continue
-
-    if submunicipality['child']['name'] == submunicipality['parent_name']:
-        try:
-            data[submunicipality['child']['name']]['has_main'] = True
-        except:
-            data[submunicipality['child']['name']] = {'has_main': True, 'children': [], 'population': None}
-        continue
-
-    child = submunicipality['child']
-    if child['name'] == 'Antwerpen': continue
-
-    if child['area']:
-        child['area'] = child['area'].replace('km²', '').strip()
-    if child['coordinates']:
-        lat, lon = child['coordinates'].replace('°', '').replace("′", '').replace("NB", '').replace("OL", '').strip().split(',')
-        child['lat'] = parseCoordinate(lat)
-        child['lon'] = parseCoordinate(lon)
-        del child['coordinates']
-
-    if child['name']:
-        child['name'] = re.sub('\(.*\)', '', child['name']).strip().replace('\r', '')
-
-    if child['population']:
-        child['population'] = re.sub('\(.*\)*', '', child['population'])
-        child['population'] = re.sub('[a-zA-Z]*', '', child['population'])
-        child['population'] = int(child['population'].replace('.', '').replace(' ', ''))
-
-    if submunicipality['parent_population']:
-        submunicipality['parent_population'] = re.sub('\(.*\)*', '', submunicipality['parent_population'])
-        submunicipality['parent_population'] = re.sub('[a-zA-Z]*', '', submunicipality['parent_population'])
-        submunicipality['parent_population'] = int(submunicipality['parent_population'].replace('.', '').replace(' ', ''))
-
-    try:
[…]

### 2018-09-02 test/cpp/gtester/gengeopop/io/GeoGridIOUtils.cpp

@@ -89,13 +89,6 @@ void CompareLocation(std::shared_ptr<Location> location, const proto::GeoGrid_Lo
                 EXPECT_EQ(protoCommute.to(), commute_pair.first->GetID());
                 EXPECT_EQ(protoCommute.proportion(), commute_pair.second);
         }
-        ASSERT_EQ(protoLocation.submunicipalities_size(), location->GetSubMunicipalities().size());
-        int idx = 0;
-        for (auto& submunicipality : location->GetSubMunicipalities()) {
-                auto protoSubmunicipalityId = protoLocation.submunicipalities(idx);
-                EXPECT_EQ(submunicipality->GetID(), protoSubmunicipalityId);
-                idx++;
-        }
 }
 void ComparePerson(const proto::GeoGrid_Person& protoPerson)
 {

### 2018-09-02 test/cpp/gtester/gengeopop/io/GeoGridProtoReaderTest.cpp

@@ -67,16 +67,6 @@ TEST(GeoGridProtoReaderTest, contactCentersTest)
 
         CompareGeoGrid(geoGrid);
 }
-TEST(GeoGridProtoReaderTest, submunicipalityTest)
-{
-        proto::GeoGrid geoGrid;
-        auto           location        = geoGrid.add_locations();
-        auto           submunicipality = geoGrid.add_locations();
-        fillLocation(1, 4, 2500, Coordinate(0, 0), "Bavikhove", location);
-        fillLocation(2, 4, 2500, Coordinate(0, 0), "Gent", submunicipality);
-        location->add_submunicipalities(submunicipality->id());
-        CompareGeoGrid(geoGrid);
-}
 TEST(GeoGridProtoReaderTest, peopleTest)
 {
         proto::GeoGrid geoGrid;

### 2018-09-02 test/cpp/gtester/gengeopop/io/GeoGridProtoWriterTest.cpp

@@ -48,17 +48,6 @@ TEST(GeoGridProtoWriterTest, contactCentersTest)
 
         CompareGeoGrid(geoGrid);
 }
-TEST(GeoGridProtoWriterTest, submunicipalityTest)
-{
-        auto geoGrid         = GetGeoGrid();
-        auto location        = std::make_shared<Location>(1, 4, 2500, Coordinate(0, 0), "Bavikhove");
-        auto submunicipality = std::make_shared<Location>(2, 4, 2500, Coordinate(0, 0), "Gent");
-        submunicipality->AddContactCenter(std::make_shared<K12School>(0));
-        location->AddSubMunicipality(submunicipality);
-        geoGrid->AddLocation(location);
-
-        CompareGeoGrid(geoGrid);
-}
 TEST(GeoGridProtoWriterTest, peopleTest) { CompareGeoGrid(GetPopulatedGeoGrid()); }
 TEST(GeoGridProtoWriterTest, commutesTest) { CompareGeoGrid(GetCommutesGeoGrid()); }
 } // namespace

### 2018-09-02 test/cpp/gtester/gengeopop/io/ReaderFactoryTest.cpp

@@ -70,17 +70,4 @@ TEST(ReaderFactoryTest, TestHouseHolds)
             std::runtime_error);
 }
 
-TEST(ReaderFactoryTest, TestSubMuns)
-{
-        ReaderFactory readerFactory;
-
-        const std::shared_ptr<SubMunicipalitiesReader>& res1 =
-            readerFactory.CreateSubMunicipalitiesReader(std::string("flanders_cities.csv"));
-
-        EXPECT_NE(std::dynamic_pointer_cast<SubMunicipalitiesReader>(res1), nullptr);
-
-        EXPECT_THROW(
-            readerFactory.CreateSubMunicipalitiesReader(stride::util::FileSys::GetTestsDir() / "testdata/io/empty.txt"),
-            std::runtime_error);
-}
 } // namespace

### 2018-09-02 test/cpp/gtester/gengeopop/io/SubMunicipalitiesCSVReaderTest.cpp

@@ -1,133 +1,0 @@
-#include <gengeopop/io/CitiesCSVReader.h>
-#include <gengeopop/io/SubMunicipalitiesCSVReader.h>
-#include <gtest/gtest.h>
-
-using namespace gengeopop;
-
-namespace {
-
-std::shared_ptr<GeoGrid> getExpectedGeoGrid()
-{
-        std::shared_ptr<GeoGrid> geoGrid = std::make_shared<GeoGrid>();
-        auto                     loc1    = std::make_shared<Location>(11057, 1, 9042, Coordinate(), "MALLE");
-        auto                     loc2    = std::make_shared<Location>(11009, 1, 16227, Coordinate(), "BRECHT");
-        auto                     loc3    = std::make_shared<Location>(46003, 4, 28654, Coordinate(), "BEVEREN");
-
-        loc1->CalculatePopulation(10000);
-        loc2->CalculatePopulation(10000);
-        loc3->CalculatePopulation(10000);
-
-        auto loc4 = std::make_shared<Location>(110571, 1, 0.5, Coordinate(4.733333333333333, 51.3), "OOSTMALLE");
-        loc1->AddSubMunicipality(loc4);
-        loc4->SetParent(loc1);
-        auto loc5 = std::make_shared<Location>(110572, 1, Coordinate(4.683333333333334, 51.3), "WESTMALLE");
-        loc1->AddSubMunicipality(loc5);
-        loc5->SetParent(loc1);
-
-        auto loc6 = std::make_shared<Location>(110091, 1, Coordinate(4.683333333333334, 51.35), "SINT-LENAARTS");
-        loc2->AddSubMunicipality(loc6);
-        loc6->SetParent(loc2);
-        auto loc7 = std::make_shared<Location>(110092, 1, Coordinate(4.583333333333333, 51.3), "SINT-JOB-IN-'T-GOOR");
-        loc2->AddSubMunicipality(loc7);
-        loc7->SetParent(loc2);
-
-        auto loc8 = std::make_shared<Location>(460031, 4, Coordinate(4.183333333333334, 51.25), "VERREBROEK");
-        loc3->AddSubMunicipality(loc8);
-        loc8->SetParent(loc3);
-        auto loc9 =
-            std::make_shared<Location>(460032, 4, Coordinate(4.166666666666667, 51.28333333333333), "KIELDRECHT");
-        loc3->AddSubMunicipality(loc9);
-        loc9->SetParent(loc3);
[…]

### 2018-09-14 doc/latex/04-Code.tex
Add documentation about travel

@@
 \label{section:travel}
-TODO
+The persons in the simulation also travel within different regions of the simulation for work or recreation.
+This can also be within the same region.
+You perform a simulation with multiple regions by using a config file based on ``run\_regions\_default.xml" or ``run\_regions\_import.xml", where currently the regions Flanders, Wallonia, The Netherlands, France and Germany are defined.
+Please note that the population sizes and fractions provided are not representative of the actual values.
+By using the option ``traveller\_amount" we can set the proportion of the population that is travelling at any given time.
+Likewise, the option ``traveller\_max\_duration" indicates the maximal duration of travel. The actual duration will be chosen using a uniform distribution between 1 day and the maximal duration.
+Finally, the option ``traveller\_fraction\_work\_travel" indicates the fraction of people that are travelling for work as opposed to recreationally.
+We also need to set the probability of travelling to a specific destination country from a given origin country, which can be different for work and recreational travel.
+We do this in the CSV files provided in the options ``traveller\_data\_work" and ``traveller\_data\_recreation" respectively, which can be found in the ``data" folder.
+
+After every day in the simulation, a person decides if it will start travelling based on a TravellerProfile, which contains all information provided by the aforementioned options.
+In this TravellerProfile it is also decided how long the stay will be, if it is a work or recreation related trip and where the person is travelling to, based on a discrete distribution of possible regions provided in the aforementioned CSV files.
+Within this chosen region, we select a random ContactPool based on the type of travel and add the traveller to this pool for the duration, removing him/her temporarily from the original ContactPools.
+In case of work related travel, the temporary ContactPool will be of the type ``Work" and for recreational travel it will be of the type ``PrimaryCommunity".
+All the information of this trip and the original ContactPools, which have to be restored after the trip ends, will then be stored in a TravellerIndex.
+This TravellerIndex is also responsible for returning travellers to their original state.
+At the end of each day, it will use a priority queue to efficiently determine if this is the end date for some travels.
+
+To support this functionality, we create a Population that consists of one GeoGrid for each region in the simulation.
+This allows us to easily loop over the complete population, spanning over multiple regions, and for example retrieve the total amount of infected persons.
+Multi-region support is only provided when using GenGeoPop to generate the population, since we use different GeoGrids to represent the different regions.

### 2018-09-14 doc/latex/02-Software.tex
Add guide on how to update the included protobuf library

@@
 If you then want to copy this code to the correct location in the source, you can use ``\texttt{make proto}".
-If the version of \texttt{protobuf-c} you're using is significantly newer than the one included in this repository, you might also need to update the files stored \texttt{main/resources/lib/protobuf}.
+If the version of \texttt{protobuf-c} you're using is significantly newer than the \texttt{protobuf} included in this repository, you might also need to update the files stored \texttt{main/resources/lib/protobuf}.
+At the time of writing, this is done in the following way, although this may be subject to change:
+\begin{itemize}
+    \item Copy all files from \url{https://github.com/protocolbuffers/protobuf/tree/master/src/google/protobuf} to \texttt{main/resources/lib/protobuf/google/protobuf}.
+    \item Copy the \texttt{libprotobuf\_files} and \texttt{libprotobuf\_includes} from \url{https://github.com/protocolbuffers/protobuf/blob/master/cmake/libprotobuf.cmake} and \url{https://github.com/protocolbuffers/protobuf/blob/master/cmake/libprotobuf-lite.cmake}
+    \item Remove the prefix \texttt{\${protobuf\_source\_dir}/src/} from these listings.\\
+        For example \texttt{\${protobuf\_source\_dir}/src/google/protobuf/any.cc} becomes \texttt{google/protobuf/any.cc}.
+    \item Edit the \texttt{CMakeLists.text} at \texttt{main/resources/lib/protobuf} and replace the current values of \texttt{libprotobuf\_files} and \texttt{libprotobuf\_includes} with the ones we just obtained.
+\end{itemize}
 
